### 2018-03-02 paper.tex
First outline

\documentclass[10pt, conference, compsocconf]{IEEEtran}

% packages
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsfonts} % for R symbol (the set of real numbers)
\usepackage{color}
\usepackage[pdftex]{graphicx}
\usepackage[bookmarks=false]{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,filecolor=black,urlcolor=blue}
\usepackage{mathtools}
\usepackage{multirow}
\usepackage{stmaryrd} % for llbracket and rrbracket
\usepackage{subcaption}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}

% new commands
\newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}:
      #1}}}

\newcommand{\note}[1]{
  \color{blue}\emph{[Note: #1]}
  \color{black}
}

\begin{document}

\title{Predicting computational reproducibility of scientific pipelines using collaborative filtering}

\author{Soudabeh Barghi, Lalet Scaria, Tristan Glatard\\
  Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada\\
  {first.last}@concordia.ca\\
  $^*$ These authors have contributed equally
}

\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}

% Computational reproducibility is an issue, for instance among
% different operating systems (refer to Glatard FINF 2015,
% Gronenschild 2012).

% Scientific data analysis pipeline executions are long (give examples
% from neuroimaging).

% Define subjects.

% Problem: predict the reproducibility of pipeline files from other
% subjects and the first files produced by a pipeline. Restrict the
% study to binary classification.

\section{Method}

\subsection{Collaborative filtering using ALS}

% Summarize Koren, Bell and Volinsky: https://dl.acm.org/citation.cfm?id=1608614
% Explain that you have binary classes (rounding)
% Biases

\subsection{Sampling the Training Set}

% Explain all sampling techniques (maybe rename 4, 5, and 6)
% 1. random unreal (baseline)
% 2. columns
% 3. rows
% 4. random real
% 5. random diagonal
% 6. random triangular
% For every method, show a training matrix to illustrate for a given ratio.

\section{Dataset}

% Describe your dataset: pipeline(s) used, input data, operating systems (CentOS5, 6, 7), matrix.

% 1. Prefreesurfer (what you have)
% 2. Freesurfer, with the same subjects as in Prefreesurfer.
% 3. PostFreesurfer
% 4. fmriVolume

\section{Results}

% Present your results: accuracy, ROC curves, transparency matrix.

\section{Discussion}

% Which sampling method is best

% How can this be used in practice

% What are the limitations

\section{Conclusion}

% Summary of the results and discussion. The take-home message.

\section*{Acknowledgment}

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,biblio.bib}

\end{document}

### 2018-03-08 paper.tex
First outline
More notes
test

@@
 
+Computational reproducibility, the property through which
+computational results can be recomputed over time and
+space~\cite{stodden}, has become a critical component of scientific
+methodology with the rise of the reproducibility crisis in several
+domains~\cite{xxx}. Among the factors hampering computational
+reproducibility, infrastructural characteristics such as the operating
+system play an important role. In neurosciences, our primary field of
+interest, several studies have shown the effect of the operating
+system on computational results. However, conducting such
+reproducibility studies at scale is cumbersome due to the execution
+time of data analysis pipelines, which easily exceeds a few hours.
+
+In this paper we investigate approximate methods to predict the
+reproducibility of a computational analysis from the first files that
+it produces. Our main intuition is that reproducibility errors are
+caused by a reduced number of factors that originate in the analysis
+pipeline and input data.
+
 % Computational reproducibility is an issue, for instance among
@@
 % from neuroimaging).
+
+% Refer to Germain et al 2008.
 
@@
 
+what is specific to our problem compared to regular collaborative filtering:
+%+ subjects are equivalent to users. Not all subjects have the same input data. Anatomical variability, acquisition variability (e.g., 1 subject may have multiple T1s).
+%+ files are produced in a specific order (movies aren't),
+% which add constraints on the training set (cannot sample late files and not early ones).
+%+ utility matrix is not sparse: we can potentially populate it completely.
+Which means that we can decide precisely which samples we need (active sampling).
+Therefore we can take the first row and first column to avoid cold start issues.
+
 \subsection{Collaborative filtering using ALS}
@@
 % Summarize Koren, Bell and Volinsky: https://dl.acm.org/citation.cfm?id=1608614
+
 % Explain that you have binary classes (rounding)
+
 % Biases
@@
 
-% Present your results: accuracy, ROC curves, transparency matrix.
+% Present your results: accuracy, ROC curves, transparency matrix, factors.
+
+% Try with different numbers of factors.
 
@@
 
+% Not all subjects behave the same, which motivates the Big Data approach.
+
 % Which sampling method is best
+
+% Interpreting the factors? Factors reflect the pipeline definition.
 

### 2018-03-08 paper.tex
First paragraphs in dataset

@@
 
-% Define subjects.
+% Define subjects, pipelines.
 
@@
 
-what is specific to our problem compared to regular collaborative filtering:
+% What is specific to our problem compared to regular collaborative filtering:
 %+ subjects are equivalent to users. Not all subjects have the same input data. Anatomical variability, acquisition variability (e.g., 1 subject may have multiple T1s).
@@
 \section{Dataset}
+
+We acquired data about the computational reproducibility of analysis
+pipelines of the Human Connectome Project~\cite{general-hcp}. We
+processed a set S of 94 subjects randomly selected in the S500 HCP
+release~\todo{URL} in three execution conditions with different
+versions of the CentOS operating system (5.?, 6.? and 7.?), using the
+PreFreesurfer, Freesurfer, PostFreesurfer and fMRIVolume pipelines
+described in~\cite{hcp-pipelines} and available at \todo{URL}. For
+each pipeline, we identified the set F of files produced for all
+subjects in all conditions. For each condition pair and each pipeline,
+we computed a binary difference matrix D of size $|F|\times|S|$, where $D_{i,j}$ is true
+if file $i$ of subject $j$ was different in each condition. Rows of
+$M$ are ordered by ascending file modification time in the pipeline.
+
+Figure~\ref{fig:pre-freesurfer-5-7} shows the difference matrix
+obtained for the PreFreesurfer pipeline\todo{Remove title from figure,
+  remove color scale, add axes labels.}. The computational
+reproducibility of the PreFreesurfer pipeline varies across subjects,
+which motivates our study. Nevertheless, some files behave
+consistently across all subjects, leading to complete black or white
+lines. The ratio of positive elements in this matrix is
+\todo{x}\%. Similar matrices were obtained with this pipeline for
+CentOS~6 vs CentOS~7 and for CentOS~5 vs CentOS~6, see
+Figures~\ref{fig:pre-freesurfer-5-6} and~\ref{fig:pre-freesurfer-5-7}.
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{figures/original_matrix_CentOS5vsCentOS7.pdf}
+  \caption{Difference matrix, PreFreesurfer pipeline, CentOS~5 vs CentOS~7.}
+  \label{fig:pre-freesurfer-5-7}
+\end{figure}
 

### 2018-03-27 paper.tex

@@
 
-% What is specific to our problem compared to regular collaborative filtering:
+what is specific to our problem compared to regular collaborative filtering:
 %+ subjects are equivalent to users. Not all subjects have the same input data. Anatomical variability, acquisition variability (e.g., 1 subject may have multiple T1s).
@@
 % 1. random unreal (baseline)
+Training set, is fitted with no restriction and it is totally based on random selection of files regardless of their generation time.
+Although this method is not applicable in our study, it is used as a baseline for having a comparison on the performance of other methods.
 % 2. columns
+Training set defined by selecting random subject in turns and reading their files’ value in respect to the file generation in pipeline.
+This selection will continue till the training set reaches the user-defined training ratio.
 % 3. rows
+Training set defined from the first files produced by the processing of each subject.
+All subjects will be processed on to the specific point of the pipeline and according to the generated files until that point the prediction of the value of the rest files will occur.
 % 4. random real
+This approach will select its next training set element according to the next file turn in the next random selected subject.
 % 5. random diagonal
+For every subject, the number of files added to the training set is randomly picked from a uniform distribution.
 % 6. random triangular
+To acquire about those files which are generated almost at the end of pipeline processing with respect of the training ratio, we used triangular ratio to calculate the number of files for each subject and added them to the training set.
 % For every method, show a training matrix to illustrate for a given ratio.

### 2018-03-27 paper.tex
Fixes following meeting with @soudabeh19

--- 2018-03-08 paper.tex
@@
 
+We investigated the following sampling techniques for the training set.
+
 % Explain all sampling techniques (maybe rename 4, 5, and 6)
 % 1. random unreal (baseline)
+\paragraph{Random unreal}
+The training set is sampled randomly with no restriction, that is,
+regardless of their generation time.  This method will be used as a
+baseline for comparison with other methods, although it is not
+realistic.
+
 % 2. columns
+\paragraph{Complete columns}
+The training set is sampled by randomly selecting complete columns in
+the matrix, that is, complete subject executions. The last selected
+column might be incomplete to meet the exact training ratio. This
+method is realistic: it corresponds to a situation where the
+collaborative filtering method will predict the reproducibility in the
+remaining subjects from the subjects in the training set.
+
 % 3. rows
+\paragraph{Complete rows} The training set is sampled by randomly
+selecting complete rows in the matrix, that is, the first files in
+every execution. The last selected row might be incomplete to meet the
+exact training ratio. This method is realistic: it corresponds to a
+situation where the processing of all the subjects is launched and
+interrupted before the execution is complete. The collaborative
+filtering method will then predict the reproducibility of the
+remaining files.
+
 % 4. random real
+\paragraph{Random real}
+\todo{Explain this better} This approach will select its next training set element according to
+the next file turn in the next random selected subject.
+
 % 5. random diagonal
+\paragraph{Random diagonal}
+For every subject, the number of files added to the training set is randomly picked from a uniform distribution.
+
 % 6. random triangular
+\paragraph{Random triangular}
+To acquire about those files which are generated almost at the end of pipeline processing with respect of the training ratio, we used triangular ratio to calculate the number of files for each subject and added them to the training set.
 % For every method, show a training matrix to illustrate for a given ratio.
+
+\todo{Find better names: consistent with either the graphical patter or the distribution.}
+\todo{Add a summary figure of the sampling methods.}
 

### 2018-04-03 paper.tex
Added figures and more info

@@
 realistic.
+\begin{figure}
+  \includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_0.3_training_plot.png}
+  \caption{Sample training set of random Unreal method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
+  \label{fig:Sample Training set }
+\end{figure}
 
@@
 remaining subjects from the subjects in the training set.
-
+\begin{figure}
+  \includegraphics[width=\columnwidth]{figures/5vs7_columns_0.3_training_plot.png}
+  \caption{Sample training set of Columns method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
+  \label{fig:Sample Training set }
+\end{figure}
 % 3. rows
-\paragraph{Complete rows} The training set is sampled by randomly
-selecting complete rows in the matrix, that is, the first files in
+\paragraph{Complete rows} The training set is sampled by selecting complete 
+rows in the matrix, that is, the first files in
 every execution. The last selected row might be incomplete to meet the
@@
 remaining files.
+\begin{figure}
+  \includegraphics[width=\columnwidth]{figures/5vs7_rows_0.3_training_plot.png}
+  \caption{Sample training set of Rows method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
+  \label{fig:Sample Training set }
+\end{figure}
 
 % 4. random real
-\paragraph{Random real}
-\todo{Explain this better} This approach will select its next training set element according to
-the next file turn in the next random selected subject.
+\paragraph{Random real (Uniform-S)}
+\todo{Explain this better}The training set sampling in this method is quite simillar to rows method.
+The key difference lies in the way that the next subject is selected randomly. In this respect, subjects' files
+are selected by coming their turn which is defined according to their generation time in the pipeline.
+\begin{figure}
+  \includegraphics[width=\columnwidth]{figures/5vs7_random-real_0.3_training_plot.png}
+  \caption{Sample training set of random Real method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
+  \label{fig:Sample Training set }
+\end{figure}
 
 % 5. random diagonal
-\paragraph{Random diagonal}
-For every subject, the number of files added to the training set is randomly picked from a uniform distribution.
-
+\paragraph{Random diagonal (Uniform-SF)}
+The training set suffers from lacking the files which are almost generated towareds the end of pipeline.
+(Or: This method aims to sample some of the files which are almost generated at the end of the pipeline).
+In this regard, the number of sampling files' of each random subject is calculated according to a 
+uniform distribution which illustrates a diagonal pattern of sampled files from the utility matrix.
+\todo{random difference tagert ratio and the efficiant one could be more than 0.01 and less than 0.1}
+\begin{comment}
+random difference tagert ratio and the efficiant one could be more than 0.01 and less than 0.1
+\begin{comment}
+\end{comment}
 % 6. random triangular
 \paragraph{Random triangular}
-To acquire about those files which are generated almost at the end of pipeline processing with respect of the training ratio, we used triangular ratio to calculate the number of files for each subject and added them to the training set.
+\subparagraph{largest-a}
+The training set is sampled by randomly selecting subjects in the matrix.
+The number of their files to be sampled in training set is calculated according to triangular distribution.
+This ununiform distribution targeting to sample files which are generated 
+almost the end of pipeline by meeting the closest training ratio  to the requested one by user.
+In this approach at laest some of the first generated files of the pipelines are set in the training for each subject and there is no possibility of not having more than the first generated file for a subject.
+\subparagraph{smallest-a}
 % For every method, show a training matrix to illustrate for a given ratio. 
+This approach is almost the same as largest-a but the only difference is that there is probability of not having more than one file of a subject in the sample training set.
 

### 2018-04-03 paper.tex
Fixed error of figures

@@
 \usepackage[pdftex]{graphicx}
+\usepackage{graphicx}
 \usepackage[bookmarks=false]{hyperref}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_0.3_training_plot.png}
+\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_03_training_plot}
   \caption{Sample training set of random Unreal method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{figures/5vs7_columns_0.3_training_plot.png}
+  \includegraphics[width=\columnwidth]{figures/5vs7_columns_03_training_plot}
   \caption{Sample training set of Columns method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{figures/5vs7_rows_0.3_training_plot.png}
+  \includegraphics[width=\columnwidth]{figures/5vs7_rows_03_training_plot}
   \caption{Sample training set of Rows method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{figures/5vs7_random-real_0.3_training_plot.png}
+ \includegraphics[width=\columnwidth]{figures/5vs7_random-real_03_training_plot}
   \caption{Sample training set of random Real method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
@@
 \end{comment}
+
 % 6. random triangular

### 2018-04-04 paper.tex
Renamed the figures' names

@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_03_training_plot}
+\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_03_training}
   \caption{Sample training set of random Unreal method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{figures/5vs7_columns_03_training_plot}
+  \includegraphics[width=\columnwidth]{figures/5vs7_columns_03_training}
   \caption{Sample training set of Columns method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{figures/5vs7_rows_03_training_plot}
+  \includegraphics[width=\columnwidth]{figures/5vs7_rows_03_training}
   \caption{Sample training set of Rows method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
@@
 \begin{figure}
- \includegraphics[width=\columnwidth]{figures/5vs7_random-real_03_training_plot}
+ \includegraphics[width=\columnwidth]{figures/5vs7_random-real_03_training}
   \caption{Sample training set of random Real method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}

### 2018-04-04 paper.tex
Added more info into <Method> section

@@
 baseline for comparison with other methods, although it is not
-realistic.
+realistic.~\ref{fig:Random-Unreal-Sample-Training-set}
 \begin{figure}
@@
   \caption{Sample training set of random Unreal method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
-  \label{fig:Sample Training set }
+  \label{fig:Random-Unreal-Sample-Training-set}
 \end{figure}
+
+Note: In the following provided methods in order to overcome the cold start problem and ensure that there is 
+at least one sample from each subject and also from each file in the training set, the first generated file of each 
+subjects and the whole files of the first random subject are sampled into 
+the training set by default.
 
@@
 collaborative filtering method will predict the reproducibility in the
-remaining subjects from the subjects in the training set.
+remaining subjects from the subjects in the training set. ~\ref{fig:Columns-Sample-Training-set}
 \begin{figure}
@@
   \caption{Sample training set of Columns method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
-  \label{fig:Sample Training set }
+  \label{fig:Columns-Sample-Training-set}
 \end{figure}
@@
 filtering method will then predict the reproducibility of the
-remaining files.
+remaining files.~\ref{fig:Rows-Sample-Training-set}
 \begin{figure}
@@
   \caption{Sample training set of Rows method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
-  \label{fig:Sample Training set }
+  \label{fig:Rows-Sample-Training-set}
 \end{figure}
@@
 \paragraph{Random real (Uniform-S)}
-\todo{Explain this better}The training set sampling in this method is quite simillar to rows method.
+\todo{Explain this better}The training set sampling in this method is quite simillar to complete rows method.
 The key difference lies in the way that the next subject is selected randomly. In this respect, subjects' files
-are selected by coming their turn which is defined according to their generation time in the pipeline.
+are selected by coming their turn which is defined according to their generation time in the pipeline.~\ref{fig:Uniform-S-Sample-Training-set}
 \begin{figure}
@@
   \caption{Sample training set of random Real method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
-  \label{fig:Sample Training set }
+  \label{fig:Uniform-S-Sample-Training-set}
 \end{figure}
@@
 The training set suffers from lacking the files which are almost generated towareds the end of pipeline.
-(Or: This method aims to sample some of the files which are almost generated at the end of the pipeline).
 In this regard, the number of sampling files' of each random subject is calculated according to a 
@@
 \paragraph{Random triangular}
-\subparagraph{largest-a}
 The training set is sampled by randomly selecting subjects in the matrix.
 The number of their files to be sampled in training set is calculated according to triangular distribution.
-This ununiform distribution targeting to sample files which are generated 
-almost the end of pipeline by meeting the closest training ratio  to the requested one by user.
-In this approach at laest some of the first generated files of the pipelines are set in the training for each subject and there is no possibility of not having more than the first generated file for a subject.
+This ununiform distribution targeting to sample files which are generated almost the end of pipeline by 
+meeting the closest training ratio to the requested one by user.
+Two approches are tried to apply this method.
+
+\subparagraph{Largest-a}	
+In this approach there is a concern to eliminate the possibility of having less 
+than the two first generated files of any subjects in the sampled training set. 
+The possibility of missing some subjects in training set can happen to some of them due to 
+random selection of subjects or even meeting the determined training ratio before 
+having the chance of being selected.
+
 \subparagraph{smallest-a}
+In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
+that some subjects be reperesented in the training set just by their first generated file and no more files.
+
 % For every method, show a training matrix to illustrate for a given ratio.
-This approach is almost the same as largest-a but the only difference is that there is probability of not having more than one file of a subject in the sample training set.
 

### 2018-04-10 paper.tex

@@
 \section{Results}
+The experimental results have been obtained from four different approaches:
+1. Straightforward results by applying ALS technique
+2. Results achieved through employing Bias as well as ALS technique
+3. Results just got through Bias 
+4. Results stemmed from ommiting the impact of predicted value for canstant files 
+In all above approaches, dummy classifier which makes predictions using simple rules\cite{URL}has been used to indicate that how much predicted value would tend to be anticipate as the dominent value of the utility matrix.
+This classifier is considered as an accuracy evaluator since the binary utility matrix is consist of \{1,0\} which respectively represent whether a difference has been observed between the same files in two different conditions (by comapring their checksums) or not.
+With the knowledge of the fact that random-unreal method is not applicable to our case study we used its results as the comparision between the unrealistic method and realistics ones.
+In this regard, the aformentioned approaches are propossed and tried to lessen the gaps between the best results from random-unreal and the applied one.
+\subsection{Straightforward results by applying ALS technique}
+Results show that in all condition pairs Complete Column method has almost a constant accuracy even if the training ratio increased and it is almost two times less than dummy accuracy in more differentiated condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7).
+But in the best case which it means in similar conditions the Complete column accuracy is as much accurate as the Dummy accuracy is, \num{0.65} percent.
+In general the accuracy pattern of the two complete Rows and Uniform-s methods show similar decline and grow behavior over the training ratio axis however it can be subject to considerable fluctuations in differentiated condition pairs.
+Dispite of their seemingly irrational behaviour, they always perform a better accuracy for the training size with less than \num{0.3} in comparison to other methods.
+This better performance (around 75 percent)is almost three times higher than other methods in condition pairs with more differences but just 20 percent better when the conditions are more similar to each other (CentOS5 vs CentOS6) with accuracy of \num{90\%}.
+All the other random methods, Uniform-SF and both Triangular approaches are performing a continues groth.
+Although some considerable variation for both triangular approches have been observed (CentOS5 vs CentOS6) their constant rise leads us to the next phase of experiments which was adding up bias into the current ALS technique.
 

### 2018-04-10 paper.tex
Edits made during meeting with @soudabeh19

@@
 \newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}:
+      #1}}}
+\newcommand{\comment}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{blue}\textbf{Comment}:
       #1}}}
@@
 
+We consider the collaborative filtering method as implemented in Spark's MLlb.
 % Summarize Koren, Bell and Volinsky: https://dl.acm.org/citation.cfm?id=1608614
@@
 We investigated the following sampling techniques for the training set. 
+In each method, we included the first row of the matrix (first 
+generated file of each subject) and a random column (all files of a 
+random subject) to avoid cold start issues. \todo{Check why the first line is not in random unreal}
 
@@
 % 1. random unreal (baseline)
-\paragraph{Random unreal}
+\paragraph{Random Unreal}
 The training set is sampled randomly with no restriction, that is,
-regardless of their generation time.  This method will be used as a
+regardless of the file generation time. This method will be used as a
 baseline for comparison with other methods, although it is not
-realistic.~\ref{fig:Random-Unreal-Sample-Training-set}
+realistic. Figure~\ref{fig:Random-Unreal-Sample-Training-set} represents 
+a training set sampled using this method.
 \begin{figure}
 \includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_03_training}
-  \caption{Sample training set of random Unreal method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
+  \caption{Sample training set obtained with the Random Unreal method with a training ratio of 0.3.}
   \label{fig:Random-Unreal-Sample-Training-set}
@@
 
-Note: In the following provided methods in order to overcome the cold start problem and ensure that there is 
-at least one sample from each subject and also from each file in the training set, the first generated file of each 
-subjects and the whole files of the first random subject are sampled into 
-the training set by default.
-
 % 2. columns
-\paragraph{Complete columns}
+\paragraph{Complete Columns}
 The training set is sampled by randomly selecting complete columns in
@@
 collaborative filtering method will predict the reproducibility in the 
-remaining subjects from the subjects in the training set. ~\ref{fig:Columns-Sample-Training-set}
+remaining subjects from the subjects in the training set. 
+Figure~\ref{fig:Columns-Sample-Training-set} represents a training set 
+sampled using this method.
 \begin{figure}
   \includegraphics[width=\columnwidth]{figures/5vs7_columns_03_training}
-  \caption{Sample training set of Columns method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
+  \caption{Sample training set obtained with the Complete Columns method with a training ratio of 0.3.}
   \label{fig:Columns-Sample-Training-set}
 \end{figure}
+
 % 3. rows
-\paragraph{Complete rows} The training set is sampled by selecting complete 
-rows in the matrix, that is, the first files in
+\paragraph{Complete Rows} The training set is sampled by selecting complete 
+rows in the matrix, that is, the first files produced by
 every execution. The last selected row might be incomplete to meet the
@@
 interrupted before the execution is complete. The collaborative 
-filtering method will then predict the reproducibility of the
-remaining files.~\ref{fig:Rows-Sample-Training-set}
+filtering method will then predict the reproducibility of the remaining 
+files. Figure~\ref{fig:Rows-Sample-Training-set} represents a training 
+set sampled using this method.
 \begin{figure}
   \includegraphics[width=\columnwidth]{figures/5vs7_rows_03_training}
-  \caption{Sample training set of Rows method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
+  \caption{Sample training set obtained with the Complete Rows method with a training ratio of 0.3.}
   \label{fig:Rows-Sample-Training-set}
@@
 
-% 4. random real
-\paragraph{Random real (Uniform-S)}
-\todo{Explain this better}The training set sampling in this method is quite simillar to complete rows method.
-The key difference lies in the way that the next subject is selected randomly. In this respect, subjects' files
-are selected by coming their turn which is defined according to their generation time in the pipeline.~\ref{fig:Uniform-S-Sample-Training-set}
+\paragraph{Random Subjects} This method builds the 
+training set by selecting the next generated file of a random subject 
+until the training ratio is reached. The next generated file of a 
+subject is the file with the lowest index in this subject that has not 
+been already selected in the training set. This method is realistic as 
+files are sampled according to their production timestamps. 
+Figure~\ref{fig:Uniform-S-Sample-Training-set} represents a training 
+set sampled using this method.
 \begin{figure}
  \includegraphics[width=\columnwidth]{figures/5vs7_random-real_03_training}
-  \caption{Sample training set of random Real method with 0.3 training ratio in condition pair of CentOS~5 vs CentOS~7}
+  \caption{Sample training set obtained with the Random Subjects method with a training ratio of 0.3.}
   \label{fig:Uniform-S-Sample-Training-set}
@@
 
-% 5. random diagonal
-\paragraph{Random diagonal (Uniform-SF)}
-The training set suffers from lacking the files which are almost generated towareds the end of pipeline.
-In this regard, the number of sampling files' of each random subject is calculated according to a 
-uniform distribution which illustrates a diagonal pattern of sampled files from the utility matrix.
-\todo{random difference tagert ratio and the efficiant one could be more than 0.01 and less than 0.1}
-\begin{comment}
-random difference tagert ratio and the efficiant one could be more than 0.01 and less than 0.1
-\begin{comment}
-\end{comment}
+\paragraph{Random File Numbers (Uniform)}
+The 
+number of files selected in every subject is randomly selected in a 
+uniform distribution with parameters a and b where a and b are set as follows: \ldots{}
+This method is realistic as files are sampled according to their production timestamps.
+Due to sampling issues, it is possible that the actual training ratio obtained with this method
+does not match the target one. We check that the difference between the target and real training ratios
+was lower than 0.01.
 
-% 6. random triangular
-\paragraph{Random triangular}
-The training set is sampled by randomly selecting subjects in the matrix.
-The number of their files to be sampled in training set is calculated according to triangular distribution.
-This ununiform distribution targeting to sample files which are generated almost the end of pipeline by 
-meeting the closest training ratio to the requested one by user.
-Two approches are tried to apply this method.
-
-\subparagraph{Largest-a}	
-In this approach there is a concern to eliminate the possibility of having less 
+\paragraph{Random File Numbers (Triangular)}
+The number of files selected in every subject is randomly selected in a triangular distribution
+with parameters a, b and c where a, b and c are set as follows: \ldots{}
+This ununiform distribution aims at sampling files produced towards the end of the execution.
+Two approches are tried to apply this method:
+\begin{enumerate}
+\item Largest-a:  In this approach there is a concern to eliminate the possibility of having less \todo{Reformulate, this is unclear.}
 than the two first generated files of any subjects in the sampled training set. 
@@
 having the chance of being selected.
-
-\subparagraph{smallest-a}
-In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
-that some subjects be reperesented in the training set just by their first generated file and no more files.
-
-% For every method, show a training matrix to illustrate for a given ratio.
-
-\todo{Find better names: consistent with either the graphical patter or the distribution.}
-\todo{Add a summary figure of the sampling methods.}
+\todo{Add a Figure.}
+\item Smallest-a: In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
+that some subjects be reperesented in the training set just by their first generated file and no more files. \todo{Reformulate, this is unclear.}
+\todo{Add a Figure.}
+\end{enumerate}
 
@@
 
-We acquired data about the computational reproducibility of analysis
+We collected data to evaluate the computational reproducibility of analysis
 pipelines of the Human Connectome Project~\cite{general-hcp}. We
@@
 \section{Results}
+
+\todo{Revise intro to this section}
 The experimental results have been obtained from four different approaches:
@@
 In this regard, the aformentioned approaches are propossed and tried to lessen the gaps between the best results from random-unreal and the applied one.
-\subsection{Straightforward results by applying ALS technique}
-Results show that in all condition pairs Complete Column method has almost a constant accuracy even if the training ratio increased and it is almost two times less than dummy accuracy in more differentiated condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7).
-But in the best case which it means in similar conditions the Complete column accuracy is as much accurate as the Dummy accuracy is, \num{0.65} percent.
-In general the accuracy pattern of the two complete Rows and Uniform-s methods show similar decline and grow behavior over the training ratio axis however it can be subject to considerable fluctuations in differentiated condition pairs.
-Dispite of their seemingly irrational behaviour, they always perform a better accuracy for the training size with less than \num{0.3} in comparison to other methods.
-This better performance (around 75 percent)is almost three times higher than other methods in condition pairs with more differences but just 20 percent better when the conditions are more similar to each other (CentOS5 vs CentOS6) with accuracy of \num{90\%}.
-All the other random methods, Uniform-SF and both Triangular approaches are performing a continues groth.
-Although some considerable variation for both triangular approches have been observed (CentOS5 vs CentOS6) their constant rise leads us to the next phase of experiments which was adding up bias into the current ALS technique.
+
+\subsection{ALS without biases}
+Results show that in all condition pairs Complete Column method has 
+almost a constant accuracy even if the training ratio increased and it 
+is almost two times less than dummy accuracy in more differentiated 
+condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the 
+best case which it means in similar conditions the Complete column 
+accuracy is as much accurate as the Dummy accuracy is, $0.65$ 
+percent. In general the accuracy pattern of the two complete Rows and 
+Uniform-s methods show similar decline and grow behavior over the 
+training ratio axis however it can be subject to considerable 
+fluctuations in differentiated condition pairs. Dispite of their 
+seemingly irrational behaviour, they always perform a better accuracy 
+for the training size with less than $0.3$ in comparison to other 
+methods. This better performance (around 75 percent)is almost three 
+times higher than other methods in condition pairs with more 
+differences but just 20 percent better when the conditions are more 
+similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$. 
+All the other random methods, Uniform-SF and both Triangular approaches 
+are performing a continues groth. Although some considerable variation 
+for both triangular approches have been observed (CentOS5 vs CentOS6) 
+their constant rise leads us to the next phase of experiments which was 
+adding up bias into the current ALS technique.
+
+The training set suffers from lacking the files which are almost generated towareds the end of pipeline.
 

### 2018-04-18 paper.tex
Put two figures side by side

@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_03_training}
-  \caption{Sample training set obtained with the Random Unreal method with a training ratio of 0.3.}
+\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
+  \caption{Sample training set obtained with the Random Unreal method with a training ratio of 0.4.}
   \label{fig:Random-Unreal-Sample-Training-set}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{figures/5vs7_columns_03_training}
-  \caption{Sample training set obtained with the Complete Columns method with a training ratio of 0.3.}
+  \includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
+  \caption{Sample training set obtained with the Complete Columns method with a training ratio of 0.4.}
   \label{fig:Columns-Sample-Training-set}
@@
 set sampled using this method.
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figures/5vs7_rows_03_training}
-  \caption{Sample training set obtained with the Complete Rows method with a training ratio of 0.3.}
+\begin{figure}[h!]
+	\centering
+	\begin{subfigure}[b]{0.4\linewidth}
+  		\includegraphics[width=\columnwidth]{figures/5vs7_rows_04_training}
+  		\caption{Sample training set obtained with the Complete Rows method with a training ratio of 0.4.}
   		\label{fig:Rows-Sample-Training-set}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.4\linewidth}
+ 		\includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
+		\caption{Sample training set obtained with the Random Subjects method with a training ratio of 0.4.}
+  		\label{fig:Uniform-S-Sample-Training-set}
+	\end{subfigure}
 \end{figure}
@@
 \begin{figure}
- \includegraphics[width=\columnwidth]{figures/5vs7_random-real_03_training}
-  \caption{Sample training set obtained with the Random Subjects method with a training ratio of 0.3.}
+ \includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
+  \caption{Sample training set obtained with the Random Subjects method with a training ratio of 0.4.}
   \label{fig:Uniform-S-Sample-Training-set}
@@
 was lower than 0.01. 
+\begin{figure}
+  \includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
+  \caption{Sample training set obtained with the Random File Numbers (Uniform) method with a training ratio of 0.4.}
+  \label{fig:Diagonal-Sample-Training-set}
+\end{figure}
 
@@
 having the chance of being selected.
-\todo{Add a Figure.}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
+  \caption{Sample training set obtained with the Random File Numbers (Triangular-L) method with a training ratio of 0.4.}
+  \label{fig:triangular-L-Sample-Training-set}
+\end{figure}
 \item Smallest-a: In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
 that some subjects be reperesented in the training set just by their first generated file and no more files. \todo{Reformulate, this is unclear.}
-\todo{Add a Figure.}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
+  \caption{Sample training set obtained with the Random File Numbers (Triangular-S) method with a training ratio of 0.4.}
+  \label{fig:triangular-S-Sample-Training-set}
+\end{figure}
 \end{enumerate}

### 2018-04-19 paper.tex
Minor changes of methods' names

@@
 a training set sampled using this method.
-\begin{figure}
-\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
-  \caption{Sample training set obtained with the Random Unreal method with a training ratio of 0.4.}
-  \label{fig:Random-Unreal-Sample-Training-set}
-\end{figure}
 
@@
 sampled using this method.
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
-  \caption{Sample training set obtained with the Complete Columns method with a training ratio of 0.4.}
-  \label{fig:Columns-Sample-Training-set}
-\end{figure}
 
@@
 	\centering
+	\begin{subfigure}[b]{0.6\linewidth}
+		\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
+  		\caption{Random Unreal method}
+  		\label{fig:Random-Unreal-Sample-Training-set}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.4\linewidth}
+  		\includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
+  		\caption{Complete Columns method}
+  		\label{fig:Columns-Sample-Training-set}
+	\end{subfigure}
 	\begin{subfigure}[b]{0.4\linewidth}
   		\includegraphics[width=\columnwidth]{figures/5vs7_rows_04_training}
-  		\caption{Sample training set obtained with the Complete Rows method with a training ratio of 0.4.}
+  		\caption{Complete Rows method}
   		\label{fig:Rows-Sample-Training-set}
@@
  		\includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
-		\caption{Sample training set obtained with the Random Subjects method with a training ratio of 0.4.}
+		\caption{Random Subjects method}
   		\label{fig:Uniform-S-Sample-Training-set}
 	\end{subfigure}
+	\begin{subfigure}[b]{0.4\linewidth}
+  		\includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
+  		\caption{(Uniform) method }
+  		\label{fig:Diagonal-Sample-Training-set}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.4\linewidth}
+  		\includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
+  		\caption{(Triangular-L) method}
+  		\label{fig:triangular-L-Sample-Training-set}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.4\linewidth}
+  		\includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
+  		\caption{(Triangular-S) method}
+  		\label{fig:triangular-S-Sample-Training-set}
+	\end{subfigure}
+	\caption{Sample training set for different methods with a training ratio of 0.4.}		
 \end{figure}
 
-\paragraph{Random Subjects} This method builds the 
+\paragraph{Random Subjects- RS} This method builds the 
 training set by selecting the next generated file of a random subject 
@@
 set sampled using this method.
-\begin{figure}
- \includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
-  \caption{Sample training set obtained with the Random Subjects method with a training ratio of 0.4.}
-  \label{fig:Uniform-S-Sample-Training-set}
-\end{figure}
 
-\paragraph{Random File Numbers (Uniform)}
+\paragraph{Random File Numbers (Uniform)- RFNU}
 The 
@@
 was lower than 0.01.
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
-  \caption{Sample training set obtained with the Random File Numbers (Uniform) method with a training ratio of 0.4.}
-  \label{fig:Diagonal-Sample-Training-set}
-\end{figure}
 
-\paragraph{Random File Numbers (Triangular)}
+\paragraph{Random File Numbers (Triangular)- RFNT}
 The number of files selected in every subject is randomly selected in a triangular distribution
@@
 \begin{enumerate}
-\item Largest-a:  In this approach there is a concern to eliminate the possibility of having less \todo{Reformulate, this is unclear.}
+\item Largest-a (RFNT-L):  In this approach there is a concern to eliminate the possibility of having less \todo{Reformulate, this is unclear.}
 than the two first generated files of any subjects in the sampled training set. 
@@
 having the chance of being selected.
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
-  \caption{Sample training set obtained with the Random File Numbers (Triangular-L) method with a training ratio of 0.4.}
-  \label{fig:triangular-L-Sample-Training-set}
-\end{figure}
-\item Smallest-a: In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
+
+\item Smallest-a (RNFT-S): In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
 that some subjects be reperesented in the training set just by their first generated file and no more files. \todo{Reformulate, this is unclear.}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
-  \caption{Sample training set obtained with the Random File Numbers (Triangular-S) method with a training ratio of 0.4.}
-  \label{fig:triangular-S-Sample-Training-set}
-\end{figure}
+
 \end{enumerate}
@@
 The experimental results have been obtained from four different approaches:
-1. Straightforward results by applying ALS technique
-2. Results achieved through employing Bias as well as ALS technique
-3. Results just got through Bias 
-4. Results stemmed from ommiting the impact of predicted value for canstant files 
+1. Applying ALS technique
+2. Employing Bias as well as ALS technique
+3. Using just Bias 
+4. Results stemmed from ommiting the impact of predicted value of canstant files 
 In all above approaches, dummy classifier which makes predictions using simple rules\cite{URL}has been used to indicate that how much predicted value would tend to be anticipate as the dominent value of the utility matrix.
 This classifier is considered as an accuracy evaluator since the binary utility matrix is consist of \{1,0\} which respectively represent whether a difference has been observed between the same files in two different conditions (by comapring their checksums) or not.
-With the knowledge of the fact that random-unreal method is not applicable to our case study we used its results as the comparision between the unrealistic method and realistics ones.
+With the knowledge of the fact that Random Unreal method is not applicable into our case study we used its results as the comparision between the unrealistic method and realistics ones.
 In this regard, the aformentioned approaches are propossed and tried to lessen the gaps between the best results from random-unreal and the applied one.
@@
 \subsection{ALS without biases}
-Results show that in all condition pairs Complete Column method has 
+Results show that in all condition pairs Complete Columns method has 
 almost a constant accuracy even if the training ratio increased and it 
-is almost two times less than dummy accuracy in more differentiated 
+is almost two times less than dummy classifier in more differentiated 
 condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the 
-best case which it means in similar conditions the Complete column 
-accuracy is as much accurate as the Dummy accuracy is, $0.65$ 
-percent. In general the accuracy pattern of the two complete Rows and 
-Uniform-s methods show similar decline and grow behavior over the 
+best case which it means in similar conditions the Complete Columns 
+accuracy is as much accurate as the Dummy classifier which is $0.65$ 
+percent. In general the accuracy pattern of the two Complete Rows and 
+RS methods show similar decline and grow behavior over the 
 training ratio axis however it can be subject to considerable 
 fluctuations in differentiated condition pairs. Dispite of their 
-seemingly irrational behaviour, they always perform a better accuracy 
+likely irrational behaviour, they always have better accuracy 
 for the training size with less than $0.3$ in comparison to other 
@@
 similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$. 
-All the other random methods, Uniform-SF and both Triangular approaches 
-are performing a continues groth. Although some considerable variation 
+All the other random methods, RS and both RFNT approaches 
+are performing a continues growth. Although some considerable variation 
 for both triangular approches have been observed (CentOS5 vs CentOS6) 

### 2018-04-19 paper.tex
Added figures to Result section

@@
 \paragraph{Random File Numbers (Uniform)- RFNU}
-The 
-number of files selected in every subject is randomly selected in a 
-uniform distribution with parameters a and b where a and b are set as follows: \ldots{}
+The number of files selected for every subject is randomly selected in a 
+uniform distribution with parameters \textit{\textbf{a}} and \textit{\textbf{b}} where \textit{\textbf{a}} and \textit{\textbf{b}} are set as follows:\\
+\textit{\textbf{a}} : The minimume random of file index that could be selected for a subject\\ 
+\textit{\textbf{b}} : The highest possibility of file index that could be selected for a subject\\
+$\mathbf{\alpha}$ : Training ratio\\
+\textit{\textbf{Nf}} : Index file which means all files with lower and equal to this number should be sampled into the training set.
 This method is realistic as files are sampled according to their production timestamps.
@@
 accuracy is as much accurate as the Dummy classifier which is $0.65$ 
-percent. In general the accuracy pattern of the two Complete Rows and 
+percent Figure~\ref{fig:columns method} represents
+the ROC curves of Complete Columns method with comparision to dummy 
+classifier over the increasement of the training ratio.
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.3\linewidth}
+                \includegraphics[width=\columnwidth]{figures/columns_5vs6}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.3\linewidth}
+                \includegraphics[width=\columnwidth]{figures/columns_5vs7}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.3\linewidth}
+                \includegraphics[width=\columnwidth]{figures/columns_6vs7}
+        \end{subfigure}
+        \caption{Average performance of Complete Columns methods in three different condition pairs}
+        \label{fig:columns method}
+\end{figure}
+In general the accuracy pattern of the two Complete Rows and 
 RS methods show similar decline and grow behavior over the 
@@
 similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$.
+Figure~\ref{fig:RS_Rows} represents
+the ROC curves of these two methods with comparision to dummy
+classifier over the increasement of the training ratio.
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.4\linewidth}
+                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs6}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.4\linewidth}
+                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs7}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.4\linewidth}
+                \includegraphics[width=\columnwidth]{figures/RS_Rows_6vs7}
+        \end{subfigure}
+        \caption{Average performance of RS and Complete Rows methods in three different condition pairs}
+        \label{fig:RS_RowS}
+\end{figure}
+
 All the other random methods, RS and both RFNT approaches 
-are performing a continues growth. Although some considerable variation 
+are performing a continues growth Figure~\ref{fig:simple-methods} represents
+the ROC curves of all random methods with comparision to dummy
+classifier over the increasement of the training ratio.. Although some considerable variation 
 for both triangular approches have been observed (CentOS5 vs CentOS6) 
@@
 adding up bias into the current ALS technique. 
+The training set suffers from lacking the files which are almost generated towareds the end of pipeline.
 
-The training set suffers from lacking the files which are almost generated towareds the end of pipeline.
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.4\linewidth}
+                \includegraphics[width=\columnwidth]{figures/simple-methods-5vs6}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.4\linewidth}
+		\includegraphics[width=\columnwidth]{figures/simple-methods-5vs7}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.4\linewidth}
+                \includegraphics[width=\columnwidth]{figures/simple-methods-6vs7}
+        \end{subfigure}
+	\caption{Average performance of Complete Columns methods in three different condition pairs}
+	\label{fig:simple-methods}
+\end{figure}
 

### 2018-04-19 paper.tex
Added the parameters to RFNU method
Removed Nf parameter for the RFNU

@@
 \textit{\textbf{a}} : The minimume random of file index that could be selected for a subject\\ 
-\textit{\textbf{b}} : The highest possibility of file index that could be selected for a subject\\
+\textit{\textbf{b}} : The highest possibility of file index that could be selected for a subject which is equal to the maximum index file (total number of subject's files,Nf)\\
 $\mathbf{\alpha}$ : Training ratio\\
-\textit{\textbf{Nf}} : Index file which means all files with lower and equal to this number should be sampled into the training set.
+\[
+  f(\alpha;p) =
+  \begin{cases}
+	  R(0,Nf)      & \text{if $\alpha \leq 0.5$ }, \\
+	  R(\alpha,Nf),  
+	  a = (2\alpha - 1) Nf & \text{if $\alpha > 0.5$}.
+  \end{cases}
+\]
 This method is realistic as files are sampled according to their production timestamps.

### 2018-04-19 paper.tex
Updates following meeting with Soudabeh

--- 2018-04-19 paper.tex
@@
 
-\subsection{Sampling the Training Set}
+\subsection{Sampling the training set}
 
@@
 	\centering
-	\begin{subfigure}[b]{0.6\linewidth}
+	\begin{subfigure}[b]{0.4\linewidth}
 		\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
@@
 
-\paragraph{Random Subjects- RS} This method builds the 
-training set by selecting the next generated file of a random subject 
-until the training ratio is reached. The next generated file of a 
+\paragraph{Random Subjects -- RS} This method builds the 
+training set by selecting the files from random subjects 
+until the training ratio is reached. The file selected in a 
 subject is the file with the lowest index in this subject that has not 
@@
 
-\paragraph{Random File Numbers (Uniform)- RFNU}
-The number of files selected for every subject is randomly selected in a 
-uniform distribution with parameters \textit{\textbf{a}} and \textit{\textbf{b}} where \textit{\textbf{a}} and \textit{\textbf{b}} are set as follows:\\
-\textit{\textbf{a}} : The minimume random of file index that could be selected for a subject\\ 
-\textit{\textbf{b}} : The highest possibility of file index that could be selected for a subject\\
-$\mathbf{\alpha}$ : Training ratio\\
-\textit{\textbf{Nf}} : Index file which means all files with lower and equal to this number should be sampled into the training set.
+\paragraph{Random File Numbers (Uniform) -- RFNU}
+
+The number of files selected for every subject is randomly selected in 
+a uniform distribution with parameters \textit{\textbf{a}} and 
+\textit{\textbf{b}} where \textit{\textbf{b}} is set to the total 
+number of files $N_{f}$ and \textit{\textbf{a}} is set such that the 
+distribution average equals to $\alpha N_{f}$ where $\alpha$ is the training ratio,  that is, 
+$\textit{\textbf{a}}=(2\alpha-1)N_{f}$. \todo{Explain what you do when alpha is lower than 0.5}
+
 This method is realistic as files are sampled according to their production timestamps.
@@
 
-\paragraph{Random File Numbers (Triangular)- RFNT}
+\paragraph{Random File Numbers (Triangular) -- RFNT}
 The number of files selected in every subject is randomly selected in a triangular distribution
 with parameters a, b and c where a, b and c are set as follows: \ldots{}
-This ununiform distribution aims at sampling files produced towards the end of the execution.
+This distribution aims at sampling files produced towards the end of the execution.
 Two approches are tried to apply this method:
@@
 \subsection{ALS without biases}
+
+\todo{1. Use the same ordering and paragraph headings as in the method 
+section. 2. Don't mix multiple ideas/results in the same paragraph. 3. 
+Mention and describe the figure before discussing it.}
+
 Results show that in all condition pairs Complete Columns method has 

### 2018-04-23 paper.tex
Removed the manual firstrow on random-unreal and column training plots
Added utility matrics of all condition pairs
Modified <ROC curve> to <accuracy graph>

@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{figures/original_matrix_CentOS5vsCentOS7.pdf}
-  \caption{Difference matrix, PreFreesurfer pipeline, CentOS~5 vs CentOS~7.}
-  \label{fig:pre-freesurfer-5-7}
+  \centering
+  \begin{subfigure}[b]{0.5\linewidth}
+	\includegraphics[width=\columnwidth]{figures/utility_5vs6_PFS}
+  \caption{Utility matrix of CentOS5 vs CentOS6}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.5\linewidth}
+	 \includegraphics[width=\columnwidth]{figures/utility_5vs7_PFS}
+  \caption{Utility matrix of CentOS5 vs CentOS7}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.5\linewidth}
+	\includegraphics[width=\columnwidth]{figures/utility_6vs7_PFS}
+  \caption{Utility matrix of CentOS6 vs CentOS7}
+  \label{fig:utility metrics}
+  \end{subfigure}
 \end{figure}
@@
 percent Figure~\ref{fig:columns method} represents
-the ROC curves of Complete Columns method with comparision to dummy 
+the accuracy graph of Complete Columns method with comparision to dummy 
 classifier over the increasement of the training ratio.
@@
         \centering
-        \begin{subfigure}[b]{0.3\linewidth}
+        \begin{subfigure}[b]{0.5\linewidth}
                 \includegraphics[width=\columnwidth]{figures/columns_5vs6}
         \end{subfigure}
-        \begin{subfigure}[b]{0.3\linewidth}
+        \begin{subfigure}[b]{0.5\linewidth}
                 \includegraphics[width=\columnwidth]{figures/columns_5vs7}
         \end{subfigure}
-        \begin{subfigure}[b]{0.3\linewidth}
+        \begin{subfigure}[b]{0.5\linewidth}
                 \includegraphics[width=\columnwidth]{figures/columns_6vs7}
@@
 Figure~\ref{fig:RS_Rows} represents
-the ROC curves of these two methods with comparision to dummy
+the accuracy graph of these two methods with comparision to dummy
 classifier over the increasement of the training ratio.
@@
 are performing a continues growth Figure~\ref{fig:simple-methods} represents
-the ROC curves of all random methods with comparision to dummy
+the accuracy graph of all random methods with comparision to dummy
 classifier over the increasement of the training ratio.. Although some considerable variation 

### 2018-04-25 paper.tex
Added figures about ALS of all methods and ALS+Bias of three methods

@@
 \usepackage{subcaption}
+\usepackage{nicefrac}
 \DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
@@
 The number of files selected for every subject is randomly selected in
-a uniform distribution with parameters \textit{\textbf{a}} and 
-\textit{\textbf{b}} where \textit{\textbf{b}} is set to the total 
-number of files $N_{f}$ and \textit{\textbf{a}} is set such that the 
-distribution average equals to $\alpha N_{f}$ where $\alpha$ is the training ratio,  that is, 
-$\textit{\textbf{a}}=(2\alpha-1)N_{f}$. \todo{Explain what you do when alpha is lower than 0.5}
+a uniform distribution $U(\textit{a},\textit{b})$, where \textit{\textbf{b}} is set to the total
+number of files $N_{f}$ and \textit{\textbf{a}} is set according to training ratio ($\alpha$) as follow:
+
+\[
+  \begin{cases}
+          \textit{\textbf{a}} = 0      & \text{if $\alpha \leq 0.5$ }\\
+
+          \textit{\textbf{a}} = (2\alpha - 1) N_{f} & \text{if $\alpha > 0.5$}
+  \end{cases}
+\]
 
@@
 does not match the target one. We check that the difference between the target and real training ratios
-was lower than 0.01.
+was lower than 0.01.\\
 
 \paragraph{Random File Numbers (Triangular) -- RFNT}
-The number of files selected in every subject is randomly selected in a triangular distribution
-with parameters a, b and c where a, b and c are set as follows: \ldots{}
+The number of files selected for every subject is randomly selected in
+a triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the other two parameters could be set according to two different approaches.
+By considering $\alpha$ as training ratio, the distribution average equals to $\alpha N_{f}$ which that means f  $\alpha$ less than $\nicefrac{1}{3}$ the lower limmit \textit{\textbf{a}} would get a negative value in this regard, therefore to avoid this issue the uniform distribution is applied for $\alpha < \nicefrac{1}{3}$.
+But for $\alpha \leq \nicefrac{1}{3}$ the following approaches are applicable.
+
+ \ldots{}
 This distribution aims at sampling files produced towards the end of the execution.
@@
 
-\item Smallest-a (RNFT-S): In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
+\item Smallest-a (RFNT-S): In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
 that some subjects be reperesented in the training set just by their first generated file and no more files. \todo{Reformulate, this is unclear.}
@@
 Mention and describe the figure before discussing it.}
-
+\subsubsection{Random Unreal}
+Figure~\ref{fig:unreal method} represents
+the accuracy graph of Complete Columns method with comparision to dummy
+classifier over the increasement of the training ratio.
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-5vs6-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-5vs7-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-6vs7-PFS}
+        \end{subfigure}
+        \caption{Average performance of Random Unreal methods in three different condition pairs}
+        \label{fig:unreal method}
+\end{figure}
+\subsubsection{Complete Columns}
+Figure~\ref{fig:columns method} represents
+the accuracy graph of Complete Columns method with comparision to dummy
+classifier over the increasement of the training ratio.
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-5vs6-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-5vs7-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-6vs7-PFS}
+        \end{subfigure}
+        \caption{Average performance of Complete Columns methods in three different condition pairs}
+        \label{fig:columns method}
+\end{figure}
+\subsubsection{Complete Rows}
+Figure~\ref{fig:rows method} represents
+the accuracy graph of Complete Rows method with comparision to dummy
+classifier over the increasement of the training ratio.
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/rows-ALS-5vs6-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/rows-ALS-5vs7-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/rows-ALS-6vs7-PFS}
+        \end{subfigure}
+        \caption{Average performance of Complete Rows methods in three different condition pairs}
+        \label{fig:rows method}
+\end{figure}
+\subsubsection{Random Subjects-RS}
+Figure~\ref{fig:RS method} represents
+the accuracy graph of RS method with comparision to dummy
+classifier over the increasement of the training ratio.
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/RS-ALS-5vs6-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/RS-ALS-5vs7-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/RS-ALS-6vs7-PFS}
+        \end{subfigure}
+        \caption{Average performance of Complete RS methods in three different condition pairs}
+        \label{fig:RS method}
+\end{figure}
+\subsubsection{RandomFile Numbers(Uniform) - RFNU}
+Figure~\ref{fig:RFNU method} represents
+the accuracy graph of RFNU method with comparision to dummy
+classifier over the increasement of the training ratio.
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/RFNU-ALS-5vs6-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/RFNU-ALS-5vs7-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/RFNU-ALS-6vs7-PFS}
+        \end{subfigure}
+        \caption{Average performance of RFNU methods in three different condition pairs}
+        \label{fig:RFNU method}
+\end{figure}
+\subsubsection{RNFT-L}
+Figure~\ref{fig:RFNT-L method} represents
+the accuracy graph of RFNT-L method with comparision to dummy
+classifier over the increasement of the training ratio.
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-L-ALS-5vs6-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-L-ALS-5vs7-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-L-ALS-6vs7-PFS}
+        \end{subfigure}
+        \caption{Average performance of RFNT-L methods in three different condition pairs}
+        \label{fig:RFNT-L method}
+\end{figure}
+\subsubsection{RFNT-S}
+Figure~\ref{fig:RFNT-S method} represents
+the accuracy graph of RFNTS method with comparision to dummy
+classifier over the increasement of the training ratio.
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-S-ALS-5vs6-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-S-ALS-5vs7-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-S-ALS-6vs7-PFS}
+        \end{subfigure}
+        \caption{Average performance of RFNT-S methods in three different condition pairs}
+        \label{fig:RFNT-S method}
+\end{figure}
+% General conclution on results of ALS without Bias 
 Results show that in all condition pairs Complete Columns method has 
@@
 the accuracy graph of Complete Columns method with comparision to dummy 
-classifier over the increasement of the training ratio.
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.5\linewidth}
-                \includegraphics[width=\columnwidth]{figures/columns_5vs6}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.5\linewidth}
-                \includegraphics[width=\columnwidth]{figures/columns_5vs7}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.5\linewidth}
-                \includegraphics[width=\columnwidth]{figures/columns_6vs7}
-        \end{subfigure}
-        \caption{Average performance of Complete Columns methods in three different condition pairs}
-        \label{fig:columns method}
-\end{figure}
+classifier over the increasement of the training ratio.\\
+
 In general the accuracy pattern of the two Complete Rows and 
@@
 \end{figure}
+%-----------------------------------------------------------
+\subsection{ALS with biases}
 
+\subsubsection{RandomFile Numbers(Uniform) - RFNU}
+Figure~\ref{fig:RFNU method} represents
+the accuracy graph of RFNU method with comparision to dummy
+classifier over the increasement of the training ratio.
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-5vs6-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-5vs7-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-6vs7-PFS}
+        \end{subfigure}
+        \caption{Average performance of RFNU methods in three different condition pairs}
+        \label{fig:RFNU method}
+\end{figure}
+\subsubsection{RNFT-L}
+Figure~\ref{fig:RFNT-L method} represents
+the accuracy graph of RFNT-L method with comparision to dummy
+classifier over the increasement of the training ratio.
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-5vs6-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-5vs7-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-6vs7-PFS}
+        \end{subfigure}
+        \caption{Average performance of RFNT-L methods in three different condition pairs}
+        \label{fig:RFNT-L method}
+\end{figure}
+\subsubsection{RFNT-S}
+Figure~\ref{fig:RFNT-S method} represents
+the accuracy graph of RFNTS method with comparision to dummy
+classifier over the increasement of the training ratio.
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-5vs6-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-5vs7-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-6vs7-PFS}
+        \end{subfigure}
+        \caption{Average performance of RFNT-S methods in three different condition pairs}
+        \label{fig:RFNT-S method}
+\end{figure}
+%-----------------------------------------------------------
 % Present your results: accuracy, ROC curves, transparency matrix, factors.

### 2018-04-25 paper.tex
Added positive ratio of the untility metrices

@@
 
-Figure~\ref{fig:pre-freesurfer-5-7} shows the difference matrix
-obtained for the PreFreesurfer pipeline\todo{Remove title from figure,
-  remove color scale, add axes labels.}. The computational
+Figure~\ref{fig:utility metrices} shows the difference matrices
+obtained for the PreFreesurfer pipeline. The computational
 reproducibility of the PreFreesurfer pipeline varies across subjects,
@@
 consistently across all subjects, leading to complete black or white
-lines. The ratio of positive elements in this matrix is
-\todo{x}\%. Similar matrices were obtained with this pipeline for
-CentOS~6 vs CentOS~7 and for CentOS~5 vs CentOS~6, see
-Figures~\ref{fig:pre-freesurfer-5-6} and~\ref{fig:pre-freesurfer-5-7}.
+lines. The ratio of positive elements in utility matrix of CentOS5 vs CentOS6(C5C6),  CentOS5 vs CentOS7(C5C7) and  CentOS6 vs CentOS7(C6C7) are
+$0.34$, $0.79$ and $0.79$ respectively.
 
@@
   \caption{Utility matrix of CentOS6 vs CentOS7}
-  \label{fig:utility metrics}
+  \label{fig:utility metrices}
   \end{subfigure}

### 2018-04-25 paper.tex
Added info for some methods in ALS phase

@@
 
-\todo{Revise intro to this section}
 The experimental results have been obtained from four different approaches:
-1. Applying ALS technique
-2. Employing Bias as well as ALS technique
-3. Using just Bias 
+1. Applying ALS technique (ALS)
+2. Employing Bias as well as ALS technique (ALS-Bias)
+3. Using just Bias (Bias)
 4. Results stemmed from ommiting the impact of predicted value of canstant files 
@@
 \subsection{ALS without biases}
-
-\todo{1. Use the same ordering and paragraph headings as in the method 
-section. 2. Don't mix multiple ideas/results in the same paragraph. 3. 
-Mention and describe the figure before discussing it.}
+In this phase of the experiment, the Alternating Least Squares techniq of Collaborative Filtering is applied for all provided methods. \todo{should I talk about ALS in here?}
 \subsubsection{Random Unreal}
 Figure~\ref{fig:unreal method} represents
-the accuracy graph of Complete Columns method with comparision to dummy
+The accuracy graph of Random Unreal method with comparision to dummy
 classifier over the increasement of the training ratio.
@@
 \end{figure}
+This method has a great performance with absolute accouracy of more than $0.95$ even by accessing to small taining size of 10 percent.
+As it mentioned earlier this method is not applicable in pipline due to timestamp cosideration but it is a good criteria to estmiate the performance of other methods and try to modify the proposed methods in order to their accuracy be as colsed as possible to the Random Unreal method ones.
+
 \subsubsection{Complete Columns}
+
 Figure~\ref{fig:columns method} represents
@@
 classifier over the increasement of the training ratio.
+As it can be seen Complete Columns method has
+almost a constant accuracy even if the training ratio increased and it
+is almost two times less than dummy classifier in more differentiated
+condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the
+best case which it means in similar conditions the Complete Columns
+accuracy is as much accurate as the Dummy classifier which is $0.65$
+percent.
+
 \begin{figure}[h!]
@@
 \end{figure}
+
 \subsubsection{Complete Rows}
@@
 classifier over the increasement of the training ratio.
+As it can be observed, This method has some flactuation over the gowth of training set size.
+These falactuations are more frequent in condition pairs which have higher difference positive ratio.
+Also by enlarging the training ratio specially between $0.3$ to $0.7$, we can see dummy classifier has better results than Complete Rows ones.
+In other words despite of better performance of Complete Rows than dummy classifier at the last 10 percent of the graph, its accuracies are less than dummy classifiers ones.
 \begin{figure}[h!]
@@
 classifier over the increasement of the training ratio.
+Same to the Complete Row method, RS method has some flactuation but not as frequent as Complete Rows method.
+Althogh there are some up and down trends specialy with training ratio range of $0.2$ to $0.6$ but its constant growth trend after training ratio $0.3$ in condition pairs with high difference positive ratio is considerable.
+The method can be $0.99$ percent accurate when it has over 70 percent of the data however this accuracy can be achived with higher training ratio (over 80 percent) for C5C6.
 \begin{figure}[h!]
@@
 % General conclution on results of ALS without Bias 
-Results show that in all condition pairs Complete Columns method has 
-almost a constant accuracy even if the training ratio increased and it 
-is almost two times less than dummy classifier in more differentiated 
-condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the 
-best case which it means in similar conditions the Complete Columns 
-accuracy is as much accurate as the Dummy classifier which is $0.65$ 
-percent Figure~\ref{fig:columns method} represents
-the accuracy graph of Complete Columns method with comparision to dummy 
-classifier over the increasement of the training ratio.\\
-
 In general the accuracy pattern of the two Complete Rows and 

### 2018-04-25 paper.tex
Added formula for the two Triangular distribution approaches

@@
 But for $\alpha \leq \nicefrac{1}{3}$ the following approaches are applicable.
-
- \ldots{}
-This distribution aims at sampling files produced towards the end of the execution.
+This distribution aims at sampling files produced towards the end of the pipeline execution.
 Two approches are tried to apply this method:
 \begin{enumerate}
-\item Largest-a (RFNT-L):  In this approach there is a concern to eliminate the possibility of having less \todo{Reformulate, this is unclear.}
+\item Largest-a (RFNT-L):  
+ This approach of triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the two other parameters are reperesent the limmited bond and mode of the distribution respectively.
+The \textit{\textbf{a}} equals to $\nicefrac {N_{f}(3\alpha-1)}{2}$ while \textit{\textbf{c}} is considered as equal as \textit{\textbf{a}}, $(\textit{\textbf{c}} = \textit{\textbf{a}})$.\\
+
+In this approach there is a concern to eliminate the possibility of having less 
 than the two first generated files of any subjects in the sampled training set. 
@@
 
-\item Smallest-a (RFNT-S): In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
-that some subjects be reperesented in the training set just by their first generated file and no more files. \todo{Reformulate, this is unclear.}
+\item Smallest-a (RFNT-S):
+This approach of triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the
+ two other parameters are reperesent the limmited bond and mode of the distribution respectively. The \textit{\textbf{a}} is set to $0$  while \textit{\textbf{c}} equals to $N_{f}(3\alpha-1)$.\\
+In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
+that some subjects be reperesented in the training set just by their first generated file and no more files.
 

### 2018-04-25 paper.tex
Added info for RFNU in ALS phase

@@
 generated file of each subject) and a random column (all files of a 
-random subject) to avoid cold start issues. \todo{Check why the first line is not in random unreal}
+random subject) to avoid cold start issues.
 
@@
 classifier over the increasement of the training ratio.
+The graphs show a continuous rise in the accuracy trend in all condition pairs however a 0.03 drop is recorder in C6C7 beteen training ratio size of $0.8$ to $0.9$.
+This metod takes over the dummy accuracy after having a training size over 40 percent in C5vsC7 and C6vsC7 but it always shows better acuracy than dummy classifier ($0.73$ percent with traininfg ratio of $0.1$)
 \begin{figure}[h!]

### 2018-04-25 paper.tex

@@
         \end{subfigure}
-	\caption{Average performance of Complete Columns methods in three different condition pairs}
+	\caption{Average performance of all methods in three different condition pairs}
 	\label{fig:simple-methods}
@@
         \end{subfigure}
-        \caption{Average performance of RFNU methods in three different condition pairs}
+        \caption{Average performance of RFNU methods with considering Bias in three different condition pairs}
         \label{fig:RFNU method}
@@
         \end{subfigure}
-        \caption{Average performance of RFNT-L methods in three different condition pairs}
+        \caption{Average performance of RFNT-L methods  with considering Bias in three different condition pairs}
         \label{fig:RFNT-L method}
@@
         \end{subfigure}
-        \caption{Average performance of RFNT-S methods in three different condition pairs}
+        \caption{Average performance of RFNT-S methods  with considering Bias in three different condition pairs}
         \label{fig:RFNT-S method}

### 2018-05-03 paper.tex
Added info about TP,TN,FP,FN, sensitivity and specificity

@@
 \section{Results}
+TP: The number of cases correctly predicted as occurance of difference \\
+FP: The number of cases incorrectly predicted as occurance of difference \\
+TN: The number of cases correctly predicted as no occurance of difference \\ 
+FN: The number of cases incorrectly predicted as no occurance of difference \\
+\[
+	    Accuracy = \frac{TP+TN}{TP+TN+FP+FN}
+\]
+Sensitivity: The ability to predict the differences cases correctly. The bellow formula can be used to calculate sensitivity of a test.
+\[
+            Sensitivity = \frac{TP}{TP+FN}
+\]
+Specificity: The ability to predict the non differences cases correctly. The following formula can be used to calculate specificity of a test. 
+\[
+            Specificity = \frac{TN}{TN+FP}
+\]
 

### 2018-05-03 paper.tex
Added figures according to categorize the methods into failure and succeed ones

@@
 
-The experimental results have been obtained from four different approaches:
-1. Applying ALS technique (ALS)
-2. Employing Bias as well as ALS technique (ALS-Bias)
-3. Using just Bias (Bias)
-4. Results stemmed from ommiting the impact of predicted value of canstant files 
+The experimental results have been obtained from four different approaches:\\
+1. Applying ALS technique (ALS)\\
+2. Employing Bias as well as ALS technique (ALS-Bias)\\
+3. Using just Bias (Bias)\\
+4. Results stemmed from ommiting the impact of predicted value of canstant files \\
 In all above approaches, dummy classifier which makes predictions using simple rules\cite{URL}has been used to indicate that how much predicted value would tend to be anticipate as the dominent value of the utility matrix.

### 2018-05-07 paper.tex
Uppdated the ALS-Failure figures

@@
 
-% Explain all sampling techniques (maybe rename 4, 5, and 6)
-% 1. random unreal (baseline)
+% 0. random unreal (baseline)
 \paragraph{Random Unreal}
@@
 The number of files selected for every subject is randomly selected in
-a triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the other two parameters could be set according to two different approaches.
-By considering $\alpha$ as training ratio, the distribution average equals to $\alpha N_{f}$ which that means f  $\alpha$ less than $\nicefrac{1}{3}$ the lower limmit \textit{\textbf{a}} would get a negative value in this regard, therefore to avoid this issue the uniform distribution is applied for $\alpha < \nicefrac{1}{3}$.
-But for $\alpha \leq \nicefrac{1}{3}$ the following approaches are applicable.
-This distribution aims at sampling files produced towards the end of the pipeline execution.
+a triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} 
+and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the other 
+two parameters could be set according to two different approaches. By considering $\alpha$ 
+as training ratio, the distribution average equals to $\alpha N_{f}$ which that means 
+for $\alpha$ less than $\nicefrac{1}{3}$ the lower limmit \textit{\textbf{a}} would 
+get a negative value in this regard, therefore to avoid this issue the uniform distribution 
+is applied for $\alpha < \nicefrac{1}{3}$. But for $\alpha \leq \nicefrac{1}{3}$ the following 
+approaches are applicable. This distribution aims at sampling files produced towards 
+the end of the pipeline execution.
+
 Two approches are tried to apply this method:
@@
 \item Largest-a (RFNT-L):  
- This approach of triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the two other parameters are reperesent the limmited bond and mode of the distribution respectively.
-The \textit{\textbf{a}} equals to $\nicefrac {N_{f}(3\alpha-1)}{2}$ while \textit{\textbf{c}} is considered as equal as \textit{\textbf{a}}, $(\textit{\textbf{c}} = \textit{\textbf{a}})$.\\
+This approach of triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} 
+and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the two other 
+parameters are reperesent the limmited bond and mode of the distribution respectively. 
+The \textit{\textbf{a}} equals to $\nicefrac {N_{f}(3\alpha-1)}{2}$ while \textit{\textbf{c}} 
+is considered as equal as \textit{\textbf{a}}, $(\textit{\textbf{c}} = \textit{\textbf{a}})$.\\
 
 In this approach there is a concern to eliminate the possibility of having less 
-than the two first generated files of any subjects in the sampled training set. 
+than the first two generated files of any subjects in the sampled training set. 
 The possibility of missing some subjects in training set can happen to some of them due to 
@@
 \item Smallest-a (RFNT-S):
-This approach of triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the
- two other parameters are reperesent the limmited bond and mode of the distribution respectively. The \textit{\textbf{a}} is set to $0$  while \textit{\textbf{c}} equals to $N_{f}(3\alpha-1)$.\\
+This approach of triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} 
+and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the
+two other parameters are reperesent the limmited bond and mode of the distribution respectively. 
+The \textit{\textbf{a}} is set to $0$  while \textit{\textbf{c}} equals to $N_{f}(3\alpha-1)$.\\
 In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
@@
 \section{Results}
+
 TP: The number of cases correctly predicted as occurance of difference \\
@@
 4. Results stemmed from ommiting the impact of predicted value of canstant files \\
-In all above approaches, dummy classifier which makes predictions using simple rules\cite{URL}has been used to indicate that how much predicted value would tend to be anticipate as the dominent value of the utility matrix.
-This classifier is considered as an accuracy evaluator since the binary utility matrix is consist of \{1,0\} which respectively represent whether a difference has been observed between the same files in two different conditions (by comapring their checksums) or not.
-With the knowledge of the fact that Random Unreal method is not applicable into our case study we used its results as the comparision between the unrealistic method and realistics ones.
-In this regard, the aformentioned approaches are propossed and tried to lessen the gaps between the best results from random-unreal and the applied one.
+In all above approaches, dummy classifier which makes prediction by using simple rules\cite{URL}
+has been used to indicate that how much the predicted value would tend to be anticipate 
+as the dominent value of the utility matrix. This classifier is considered as an 
+accuracy evaluator since the binary utility matrix is consist of \{1,0\} which  
+respectively represent whether a difference has been observed between the same files 
+in two different conditions (by comapring their checksums) or not.
+With the knowledge of the fact that Random Unreal method is not applicable into our 
+case study, we used its results as the comparision between the unrealistic method 
+and realistics ones. In this regard, the aformentioned approaches are propossed and 
+tried to lessen the gaps between the best results from random-unreal and the applied one.
 
@@
 In this phase of the experiment, the Alternating Least Squares techniq of Collaborative Filtering is applied for all provided methods. \todo{should I talk about ALS in here?}
-\subsubsection{Random Unreal}
-Figure~\ref{fig:unreal method} represents
-The accuracy graph of Random Unreal method with comparision to dummy
-classifier over the increasement of the training ratio.
+Figure~\ref{fig:ALS-Failure} represents
+The accuracy graph of four diferent Complete Columns, RS, Complete Rows and Random Unreal methods.The comparision to dummy
+classifier over the increasement of the training ratio can be seen in this figure.
 \begin{figure}[h!]
@@
         \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-5vs6-PFS}
+                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-5vs6}
         \end{subfigure}
         \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-5vs7-PFS}
+                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-5vs7}
         \end{subfigure}
         \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/unreal-ALS-6vs7-PFS}
+                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-6vs7}
         \end{subfigure}
-        \caption{Average performance of Random Unreal methods in three different condition pairs}
-        \label{fig:unreal method}
+        \caption{Average performance of Complete Columns, RS, Complete Rows and Random Unreal methods in three different condition pairs}
+        \label{fig:ALS-Failure}
 \end{figure}
-This method has a great performance with absolute accouracy of more than $0.95$ even by accessing to small taining size of 10 percent.
-As it mentioned earlier this method is not applicable in pipline due to timestamp cosideration but it is a good criteria to estmiate the performance of other methods and try to modify the proposed methods in order to their accuracy be as colsed as possible to the Random Unreal method ones.
+
+\subsubsection{Random Unreal}
+This method has a great performance with absolute accouracy of more than $0.95$ 
+even by accessing to small taining size of 10 percent. As it mentioned earlier 
+this method is not applicable in pipline due to timestamp cosideration but it 
+is a good criteria to estmiate the performance of other methods and try to modify 
+the proposed methods in order to their accuracy be as colsed as possible to the 
+Random Unreal method ones.
 
 \subsubsection{Complete Columns}
-
-Figure~\ref{fig:columns method} represents
-the accuracy graph of Complete Columns method with comparision to dummy
-classifier over the increasement of the training ratio.
-As it can be seen Complete Columns method has
+As it shown in Figure~\ref{fig:ALS-Failure} the Complete Columns method has
 almost a constant accuracy even if the training ratio increased and it
@@
 percent.
-
+\\
+\subsubsection{Complete Rows}
+As it can be observed, Figure~\ref{fig:ALS-Failure}, This method has some 
+flactuation over the gowth of training set size. These falactuations are more 
+frequent in condition pairs which have higher difference positive ratio. 
+Also by enlarging the training ratio specially between $0.3$ to $0.7$, 
+we can see dummy classifier has better results than Complete Rows ones. 
+In other words despite of better performance of Complete Rows than 
+dummy classifier at the last 10 percent of the graph, its accuracies 
+are less than dummy classifiers ones.  
+\\
+\subsubsection{Random Subjects-RS}
+The performance of RS method is represented in Figure~\ref{fig:ALS-Failure}.
+Same to the Complete Row method, RS method has some flactuation but not as frequent 
+as Complete Rows method. Althogh there are some up and down trends specialy with 
+training ratio range of $0.2$ to $0.6$ but its constant growth trend after 
+training ratio $0.3$ in condition pairs with high difference positive ratio is considerable.
+The method can be $0.99$ percent accurate when it has over 70 percent of the data however 
+this accuracy can be achived with higher training ratio (over 80 percent) for C5C6.  
+\\
+\\
+\noindent Figure~\ref{fig:ALS-Succeed} represents
+the accuracy graph of all Random kind methods with comparision to dummy
+classifier over the increasement of the training ratio.\\
 \begin{figure}[h!]
@@
         \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-5vs6-PFS}
+                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs6}
         \end{subfigure}
         \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-5vs7-PFS}
+                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs7}
         \end{subfigure}
         \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/columns-ALS-6vs7-PFS}
-        \end{subfigure}
-        \caption{Average performance of Complete Columns methods in three different condition pairs}
-        \label{fig:columns method}
-\end{figure}
-
-\subsubsection{Complete Rows}
-Figure~\ref{fig:rows method} represents
-the accuracy graph of Complete Rows method with comparision to dummy
-classifier over the increasement of the training ratio.
-As it can be observed, This method has some flactuation over the gowth of training set size.
-These falactuations are more frequent in condition pairs which have higher difference positive ratio.
-Also by enlarging the training ratio specially between $0.3$ to $0.7$, we can see dummy classifier has better results than Complete Rows ones.
-In other words despite of better performance of Complete Rows than dummy classifier at the last 10 percent of the graph, its accuracies are less than dummy classifiers ones.
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/rows-ALS-5vs6-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/rows-ALS-5vs7-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/rows-ALS-6vs7-PFS}
-        \end{subfigure}
-        \caption{Average performance of Complete Rows methods in three different condition pairs}
-        \label{fig:rows method}
-\end{figure}
-\subsubsection{Random Subjects-RS}
-Figure~\ref{fig:RS method} represents
-the accuracy graph of RS method with comparision to dummy
-classifier over the increasement of the training ratio.
-Same to the Complete Row method, RS method has some flactuation but not as frequent as Complete Rows method.
-Althogh there are some up and down trends specialy with training ratio range of $0.2$ to $0.6$ but its constant growth trend after training ratio $0.3$ in condition pairs with high difference positive ratio is considerable.
-The method can be $0.99$ percent accurate when it has over 70 percent of the data however this accuracy can be achived with higher training ratio (over 80 percent) for C5C6.
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/RS-ALS-5vs6-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/RS-ALS-5vs7-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/RS-ALS-6vs7-PFS}
-        \end{subfigure}
-        \caption{Average performance of Complete RS methods in three different condition pairs}
-        \label{fig:RS method}
-\end{figure}
-\subsubsection{RandomFile Numbers(Uniform) - RFNU}
-Figure~\ref{fig:RFNU method} represents
-the accuracy graph of RFNU method with comparision to dummy
-classifier over the increasement of the training ratio.
-The graphs show a continuous rise in the accuracy trend in all condition pairs however a 0.03 drop is recorder in C6C7 beteen training ratio size of $0.8$ to $0.9$.
-This metod takes over the dummy accuracy after having a training size over 40 percent in C5vsC7 and C6vsC7 but it always shows better acuracy than dummy classifier ($0.73$ percent with traininfg ratio of $0.1$)
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/RFNU-ALS-5vs6-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/RFNU-ALS-5vs7-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/RFNU-ALS-6vs7-PFS}
+                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-6vs7}
         \end{subfigure}
         \caption{Average performance of RFNU methods in three different condition pairs}
-        \label{fig:RFNU method}
+        \label{fig:ALS-Succeed}
 \end{figure}
-\subsubsection{RNFT-L}
-Figure~\ref{fig:RFNT-L method} represents
-the accuracy graph of RFNT-L method with comparision to dummy
-classifier over the increasement of the training ratio.
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-L-ALS-5vs6-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-L-ALS-5vs7-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-L-ALS-6vs7-PFS}
-        \end{subfigure}
-        \caption{Average performance of RFNT-L methods in three different condition pairs}
-        \label{fig:RFNT-L method}
-\end{figure}
+\subsubsection{Random File Numbers(Uniform) - RFNU}
+The continuous rise of RFNU accuracy trend can be observed in Figure~\ref{fig:ALS-Succeed}.
+However a 0.03 drop is recorded in C6C7 between training ratio size of $0.8$ to $0.9$. 
+This method takes over the dummy accuracy after having a training size more than 40 percent 
+in condition pairs of C5vsC7 and C6vsC7 but it always shows better acuracy than 
+dummy classifier ($0.73$ percent with traininfg ratio of $0.1$).
+
+As it mentioned earlier, for $\alpha < \nicefrac{1}{3}$ RFNT approaches are not applicable, 
+therefor for training ratio less than $0.4$ RFNU method is employed. As a result, in terms of 
+evaluating the performance of RFNT-L and RFNT-S approches, only those accuracy results are 
+considered which their training set are equal or geather than 0.4 percent of the whole utility matrix.
+
+\subsubsection{RFNT-L}
+Figure~\ref{fig:ALS-Succeed}
+
 \subsubsection{RFNT-S}
-Figure~\ref{fig:RFNT-S method} represents
-the accuracy graph of RFNTS method with comparision to dummy
-classifier over the increasement of the training ratio.
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-S-ALS-5vs6-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-S-ALS-5vs7-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/RFNT-S-ALS-6vs7-PFS}
-        \end{subfigure}
-        \caption{Average performance of RFNT-S methods in three different condition pairs}
-        \label{fig:RFNT-S method}
-\end{figure}
+Figure~\ref{fig:ALS-Succeed}
+
 % General conclution on results of ALS without Bias 
@@
 % Summary of the results and discussion. The take-home message.
-
+%%%%%% why there is a drop in ALS-RFNT-L with 60% ratio?  
 \section*{Acknowledgment}

### 2018-05-07 paper.tex
Just for Test
Added ALS-Bias figures

@@
 
+% ALS-RFNT approaches
 As it mentioned earlier, for $\alpha < \nicefrac{1}{3}$ RFNT approaches are not applicable, 
@@
 \subsubsection{RFNT-L}
-Figure~\ref{fig:ALS-Succeed}
+In Figure~\ref{fig:ALS-Succeed}, the results show that RFNT-L performance is always more accurate than
+dummy classifier even in its lowest accuracy value observed at training ratio of $0.6$ in C5C6 ($0.78$ percent).
+Dispite of this sudden mentioned drop to $78\%$ accuracy, RFNT-L method has slight growing trend throughout the 
+increment of training ratio and its accuracy is always more than $90\%$.
 
 \subsubsection{RFNT-S}
-Figure~\ref{fig:ALS-Succeed}
+Figure~\ref{fig:ALS-Succeed} shows the overall performance of RFNT-S methods in three different condition pairs.
+Similar to RFNT-L, this method also has constant accuracy increament with maximum less accuracy of 0.07 than 
+Random Unreal method throughout the experiment of C5C7 and C6C7.
+
+\subsection{Adding biases}
+In this phase of experiment, the variation in values of utility matrix which caused by subjects and files are also considered. 
+Figure~\ref{fig:ALS-Bias-PFS} presents the result of three methods of RFNU, RFNT-L and RFNT-S with having a comparison with
+Random Unreal method.
+
+\begin{figure}[h!]
+        \centering
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-5vs6-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-5vs7-PFS}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.8\linewidth}
+                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-6vs7-PFS}
+        \end{subfigure}
+        \caption{Average performance of random methods in three different condition pairs with cosidering Bias of both subjects and files}
+        \label{fig:ALS-Bias-PFS}
+\end{figure}
 

### 2018-05-07 paper.tex
Some fixes following meeting

@@
 
-TP: The number of cases correctly predicted as occurance of difference \\
-FP: The number of cases incorrectly predicted as occurance of difference \\
-TN: The number of cases correctly predicted as no occurance of difference \\ 
-FN: The number of cases incorrectly predicted as no occurance of difference \\
+Four experiments have been conducted to evaluate the performance of our 
+predictions using (1) ALS without biases, (2) ALS with biases, (3) Biases only. 
+Results will be evaluated on the complete datasets and specifically on the files that
+do not behave consistently across subjects (\todo{explain this in introduction}).
+
+We evaluate prediction methods using accuracy, sensitivity and specificity defined as follows:
 \[
@@
 \]
-Sensitivity: The ability to predict the differences cases correctly. The bellow formula can be used to calculate sensitivity of a test.
 \[
@@
 \]
-Specificity: The ability to predict the non differences cases correctly. The following formula can be used to calculate specificity of a test. 
 \[
@@
 \]
+Where TP is the number of True Positives (correctly predicted errors), 
+FP is the number of False Positives, TN is the number of true negatives 
+and FN is the number of false negatives.
 
-The experimental results have been obtained from four different approaches:\\
-1. Applying ALS technique (ALS)\\
-2. Employing Bias as well as ALS technique (ALS-Bias)\\
-3. Using just Bias (Bias)\\
-4. Results stemmed from ommiting the impact of predicted value of canstant files \\
-In all above approaches, dummy classifier which makes prediction by using simple rules\cite{URL}
-has been used to indicate that how much the predicted value would tend to be anticipate 
-as the dominent value of the utility matrix. This classifier is considered as an 
-accuracy evaluator since the binary utility matrix is consist of \{1,0\} which  
-respectively represent whether a difference has been observed between the same files 
-in two different conditions (by comapring their checksums) or not.
-With the knowledge of the fact that Random Unreal method is not applicable into our 
-case study, we used its results as the comparision between the unrealistic method 
-and realistics ones. In this regard, the aformentioned approaches are propossed and 
-tried to lessen the gaps between the best results from random-unreal and the applied one.
+We compare our methods to two references, (1) a dummy classifier that always predicts the dominant class.
+as the dominent value of the utility matrix (1 or 0), (2) the Random Unreal method, used as the baseline sampling technique.
 
 \subsection{ALS without biases}
-In this phase of the experiment, the Alternating Least Squares techniq of Collaborative Filtering is applied for all provided methods. \todo{should I talk about ALS in here?}
-Figure~\ref{fig:ALS-Failure} represents
-The accuracy graph of four diferent Complete Columns, RS, Complete Rows and Random Unreal methods.The comparision to dummy
-classifier over the increasement of the training ratio can be seen in this figure.
+In this phase of the experiment, the Alternating Least Squares 
+technique of Collaborative Filtering is applied for all provided 
+methods. Our four sampling techniques are compared in 
+Figure~\ref{fig:ALS-Failure} and the results are described in the next 
+sub-sections.
+
 \begin{figure}[h!]
@@
         \end{subfigure}
-        \caption{Average performance of Complete Columns, RS, Complete Rows and Random Unreal methods in three different condition pairs}
+        \caption{Average accuracy of Complete Columns, RS, Complete Rows and Random Unreal methods in three different condition pairs.}
         \label{fig:ALS-Failure}
@@
 \subsubsection{Random Unreal}
-This method has a great performance with absolute accouracy of more than $0.95$ 
-even by accessing to small taining size of 10 percent. As it mentioned earlier 
-this method is not applicable in pipline due to timestamp cosideration but it 
-is a good criteria to estmiate the performance of other methods and try to modify 
-the proposed methods in order to their accuracy be as colsed as possible to the 
+This method has a great performance with absolute accuracy of more than $0.95$ 
+even by accessing to small training size of 10 percent. As it mentioned earlier 
+this method is not applicable in pipline due to timestamp consideration but it 
+is a good criteria to estimate the performance of other methods and try to modify 
+the proposed methods in order to their accuracy be as closed as possible to the 
 Random Unreal method ones.
@@
 \subsubsection{Complete Columns}
-As it shown in Figure~\ref{fig:ALS-Failure} the Complete Columns method has
+The Complete Columns method has
 almost a constant accuracy even if the training ratio increased and it
@@
 \subsubsection{Complete Rows}
-As it can be observed, Figure~\ref{fig:ALS-Failure}, This method has some 
+This method has some 
 flactuation over the gowth of training set size. These falactuations are more 
@@
 \subsubsection{Random Subjects-RS}
-The performance of RS method is represented in Figure~\ref{fig:ALS-Failure}.
 Same to the Complete Row method, RS method has some flactuation but not as frequent 

### 2018-05-09 paper.tex

@@
 do not behave consistently across subjects (\todo{explain this in introduction}).
-
+\todo{the last sentence just applies for Traiangular-L and on the case that I called 
+pure accuracy, other results of ALS, ALS-biases are not applied in this case}
 We evaluate prediction methods using accuracy, sensitivity and specificity defined as follows:
@@
 this method is not applicable in pipline due to timestamp consideration but it 
-is a good criteria to estimate the performance of other methods and try to modify 
+is a good criterion to estimate the performance of other methods and try to modify 
 the proposed methods in order to their accuracy be as closed as possible to the 
@@
 \subsubsection{Complete Columns}
-The Complete Columns method has
-almost a constant accuracy even if the training ratio increased and it
+The Complete Columns method has almost a constant accuracy even if the training ratio increased and it
 is almost two times less than dummy classifier in more differentiated
@@
 best case which it means in similar conditions the Complete Columns
-accuracy is as much accurate as the Dummy classifier which is $0.65$
+accuracy is as much accurate as the Dummy classifier is, $0.65$
 percent.
@@
 \subsubsection{Complete Rows}
-This method has some 
-flactuation over the gowth of training set size. These falactuations are more 
+This method has some flactuation over the gowth of training set size. These falactuations are more 
 frequent in condition pairs which have higher difference positive ratio. 
@@
 in condition pairs of C5vsC7 and C6vsC7 but it always shows better acuracy than 
-dummy classifier ($0.73$ percent with traininfg ratio of $0.1$).
+dummy classifier ($0.73$ percent with traininfg ratio of $0.1$).\newline
 
 % ALS-RFNT approaches
-As it mentioned earlier, for $\alpha < \nicefrac{1}{3}$ RFNT approaches are not applicable, 
+\indent As it mentioned earlier, for $\alpha < \nicefrac{1}{3}$ RFNT approaches are not applicable, 
 therefor for training ratio less than $0.4$ RFNU method is employed. As a result, in terms of 
 evaluating the performance of RFNT-L and RFNT-S approches, only those accuracy results are 
-considered which their training set are equal or geather than 0.4 percent of the whole utility matrix.
+considered which their training set are equal or geather than 0.4 percent of the whole utility matrix.\newline
 
 \subsubsection{RFNT-L}
+
 In Figure~\ref{fig:ALS-Succeed}, the results show that RFNT-L performance is always more accurate than
 dummy classifier even in its lowest accuracy value observed at training ratio of $0.6$ in C5C6 ($0.78$ percent).
-Dispite of this sudden mentioned drop to $78\%$ accuracy, RFNT-L method has slight growing trend throughout the 
+Dispite of this sudden, RFNT-L method has slight growing trend throughout the 
 increment of training ratio and its accuracy is always more than $90\%$.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Adding biases}
-In this phase of experiment, the variation in values of utility matrix which caused by subjects and files are also considered. 
-Figure~\ref{fig:ALS-Bias-PFS} presents the result of three methods of RFNU, RFNT-L and RFNT-S with having a comparison with
-Random Unreal method.
+In this part of the experiment, the effect of both subjects' and files' biases are considered in the predicted value. 
+Our three random sampeling techniques are compered in Figure~\ref{fig:ALS-Bias-PFS} accross the accretion of training 
+ratio;$\alpha$; and the results are reported at the following subsections.
 
@@
 \end{figure}
+
+\subsubsection{RFNU}
+The obtained results show that by sampling at least half of the utility matrix, 
+the predicted accuracy would be as accurate as the baseline (Random Unreal technique) 
+but for the $\alpha$ of less than $50\%$ this is not true. Actually there is a 
+difference range of $0.2$ to $0.7$ between the accuracy of Random Unreal and RFNU techniques for
+$\alpha <0.5$ in C5C7 and C6C7 but this range chanhe to $(0.07,0.17)$ in C5C6.
+
+\subsubsection{RFNT-L}
+As it mentioned earlier RFNT-L technique is applicable for $\alpha \leq \nicefrac{1}{3}$, therefore its 
+accuracy description is summerized for $\alpha > 0.3$. This accuracy of this technique is always higher than 
+dummy classifier. Results show that this RFNT-L reaches to $100\%$ accuracy by $\alpha >0.8$ in condition pairs
+with more errors, however the baseline never reached this high accuracy throughout of whole experiment.
+
+\subsubsection{RFNT-S}
+This sampling technique is as precise as Random Unreal with maximum difference gap of 0.07 between them which that 
+happend in C5C7 at $\alpha = 0.7$ with accuracy of $0.91$.
 

### 2018-05-09 paper.tex
Updates following discussion with Soudabeh

@@
 The number of files selected for every subject is randomly selected in
-a uniform distribution $U(\textit{a},\textit{b})$, where \textit{\textbf{b}} is set to the total
-number of files $N_{f}$ and \textit{\textbf{a}} is set according to training ratio ($\alpha$) as follow:
+a uniform distribution $U(\textit{a},\textit{b})$, where \textit{b} is set to the total
+number of files $N_{f}$ and \textit{a} is set according to training ratio $\alpha$ as follows:
 
@@
   \begin{cases}
-          \textit{\textbf{a}} = 0      & \text{if $\alpha \leq 0.5$ }\\
+          \textit{a} = 0      & \text{if $\alpha \leq 0.5$ }\\
 
-          \textit{\textbf{a}} = (2\alpha - 1) N_{f} & \text{if $\alpha > 0.5$}
+          \textit{a} = (2\alpha - 1) N_{f} & \text{if $\alpha > 0.5$}
   \end{cases}
@@
 The number of files selected for every subject is randomly selected in
-a triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} 
-and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the other 
-two parameters could be set according to two different approaches. By considering $\alpha$ 
+a triangular distribution with parameters \textit{a}, \textit{b} and 
+\textit{c} (\todo{see Figure X}) where \textit{b} is set to $N_{f}$ and the other two 
+parameters can be set with two approaches meant to ensure that the 
+average of the distribution is $\alpha N_{f}$ ($\alpha$ is the training 
+ratio):
+\begin{enumerate}
+        \item Largest-a (RFNT-L): In this approach, a is set to the 
+        largest possible value, i.e., b. The average of the 
+        distribution is $\frac{a+N_{f}}{2}$, therefore, 
+        a=$(2\alpha-1)N_{f}$.
+\end{enumerate}
+
+By considering $\alpha$ 
 as training ratio, the distribution average equals to $\alpha N_{f}$ which that means 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Adding biases}
-In this part of the experiment, the effect of both subjects' and files' biases are considered in the predicted value. 
-Our three random sampeling techniques are compered in Figure~\ref{fig:ALS-Bias-PFS} accross the accretion of training 
-ratio;$\alpha$; and the results are reported at the following subsections.
+\subsection{ALS with biases}
+In this part of the experiment, the effect of both subject and file 
+biases are considered in the prediction. Our three random sampling 
+techniques (RFNU, RFNT-L and RFNT-S) are compared in 
+Figure~\ref{fig:ALS-Bias-PFS} as a function of the training 
+ratio $\alpha$.
 
@@
         \end{subfigure}
-        \caption{Average performance of random methods in three different condition pairs with cosidering Bias of both subjects and files}
+        \caption{Average performance of random methods for three different condition pairs (ALS with Bias).}
         \label{fig:ALS-Bias-PFS}
 \end{figure}
+\todo{Add $\alpha$ to the x labels in the Figure}
 
-\subsubsection{RFNU}
-The obtained results show that by sampling at least half of the utility matrix, 
-the predicted accuracy would be as accurate as the baseline (Random Unreal technique) 
-but for the $\alpha$ of less than $50\%$ this is not true. Actually there is a 
-difference range of $0.2$ to $0.7$ between the accuracy of Random Unreal and RFNU techniques for
-$\alpha <0.5$ in C5C7 and C6C7 but this range chanhe to $(0.07,0.17)$ in C5C6.
-
-\subsubsection{RFNT-L}
-As it mentioned earlier RFNT-L technique is applicable for $\alpha \leq \nicefrac{1}{3}$, therefore its 
-accuracy description is summerized for $\alpha > 0.3$. This accuracy of this technique is always higher than 
-dummy classifier. Results show that this RFNT-L reaches to $100\%$ accuracy by $\alpha >0.8$ in condition pairs
-with more errors, however the baseline never reached this high accuracy throughout of whole experiment.
-
-\subsubsection{RFNT-S}
-This sampling technique is as precise as Random Unreal with maximum difference gap of 0.07 between them which that 
-happend in C5C7 at $\alpha = 0.7$ with accuracy of $0.91$.
+All three methods reach the accuracy of the baseline Random Unreal 
+method from $\alpha$=0.5. RFNT methods reach this accuracy earlier than 
+RFNU, from $\alpha$=0.4. For lower training ratios, all methods 
+outperform the dummy classifier for one condition pair (CentOS5 vs 
+CentOS6) but this is not the case for the other conditions. It should 
+be noted that, as explained before, the three methods boil down to the 
+same one (RFNU) for $\alpha<$0.3.
 

### 2018-05-09 paper.tex
Updates in method

@@
 a triangular distribution with parameters \textit{a}, \textit{b} and 
-\textit{c} (\todo{see Figure X}) where \textit{b} is set to $N_{f}$ and the other two 
-parameters can be set with two approaches meant to ensure that the 
+\textit{c} (\todo{see Figure X}). The mean of the distribution is 
+$\frac{a+b+c}{3}$. In our case, we set \textit{c} to $N_{f}$ and we set 
+\textit{a} and \textit{b} with two approaches meant to ensure that the 
 average of the distribution is $\alpha N_{f}$ ($\alpha$ is the training 
@@
 \begin{enumerate}
-        \item Largest-a (RFNT-L): In this approach, a is set to the 
+        \item Largest a (RFNT-L): a is set to the 
         largest possible value, i.e., b. The average of the 
-        distribution is $\frac{a+N_{f}}{2}$, therefore, 
-        a=$(2\alpha-1)N_{f}$.
+        distribution is $\frac{2a+N_{f}}{3}$, therefore 
+        $a=\frac{3\alpha-1}{2}N_{f}$.
+                \item Smallest a (RFNT-S): a is 
+        set to the smallest possible value, i.e., 0. The average of the 
+        distribution is $\frac{b+N_{f}}{3}$, therefore 
+        $b=N_{f}(3\alpha-1)$. To ensure that $b<N_{f}$, we actually set 
+        $b=\min(N_{f}, N_{f}(3\alpha-1))$. 
 \end{enumerate}
+It should be noted that $\alpha$ must be larger than $\frac{1}{3}$ for 
+a and b to remain positive. For training ratios lower than $\frac{1}{3}$, we 
+define RFNT methods as the RFNU one presented previously.
 
-By considering $\alpha$ 
-as training ratio, the distribution average equals to $\alpha N_{f}$ which that means 
-for $\alpha$ less than $\nicefrac{1}{3}$ the lower limmit \textit{\textbf{a}} would 
-get a negative value in this regard, therefore to avoid this issue the uniform distribution 
-is applied for $\alpha < \nicefrac{1}{3}$. But for $\alpha \leq \nicefrac{1}{3}$ the following 
-approaches are applicable. This distribution aims at sampling files produced towards 
-the end of the pipeline execution.
-
-Two approches are tried to apply this method:
-\begin{enumerate}
-\item Largest-a (RFNT-L):  
-This approach of triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} 
-and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the two other 
-parameters are reperesent the limmited bond and mode of the distribution respectively. 
-The \textit{\textbf{a}} equals to $\nicefrac {N_{f}(3\alpha-1)}{2}$ while \textit{\textbf{c}} 
-is considered as equal as \textit{\textbf{a}}, $(\textit{\textbf{c}} = \textit{\textbf{a}})$.\\
-
-In this approach there is a concern to eliminate the possibility of having less 
-than the first two generated files of any subjects in the sampled training set. 
-The possibility of missing some subjects in training set can happen to some of them due to 
-random selection of subjects or even meeting the determined training ratio before 
-having the chance of being selected.
-
-\item Smallest-a (RFNT-S):
-This approach of triangular distribution with parameters \textit{\textbf{a}}, \textit{\textbf{c}} 
-and \textit{\textbf{b}} where \textit{\textbf{b}} is set to $N_{f}$ and the
-two other parameters are reperesent the limmited bond and mode of the distribution respectively. 
-The \textit{\textbf{a}} is set to $0$  while \textit{\textbf{c}} equals to $N_{f}(3\alpha-1)$.\\
-In this approach of utilizing triangular distribution,despite of Largest-a approch, there is a possibility 
-that some subjects be reperesented in the training set just by their first generated file and no more files.
-
-\end{enumerate}
+As illustrated in Figures~\ref{fig:triangular-L-Sample-Training-set} 
+and~\ref{fig:triangular-S-Sample-Training-set}, the motivation for the 
+RFNT-L method is to guarantee that, for large enough values of 
+$\alpha$, all subjects will have at least a few files in the training 
+set.
 

### 2018-05-22 paper.tex
Added info and figures for Bias without ALS

@@
 been already selected in the training set. This method is realistic as 
-files are sampled according to their production timestamps. 
+files are sampled according to their production time-stamps. 
 Figure~\ref{fig:Uniform-S-Sample-Training-set} represents a training 
@@
 
-This method is realistic as files are sampled according to their production timestamps.
+This method is realistic as files are sampled according to their production time-stamps.
 Due to sampling issues, it is possible that the actual training ratio obtained with this method
@@
 
-\begin{figure}
+\begin{figure}[h!]
   \centering
@@
 
+as it can be seen, some of the files are consistent cross the subjects 
+which means that there are some cases that a file has an error in whole subjects (complete white)or 
+in another case no checksum difference has been observed for a file among all subjects (complete black).
+These kind of consistent behaviour makes us to discard the prediction of these file-id's elements 
+from the calculated accuracy in some phases of our experiments.
+
 % Describe your dataset: pipeline(s) used, input data, operating systems (CentOS5, 6, 7), matrix.
@@
 predictions using (1) ALS without biases, (2) ALS with biases, (3) Biases only. 
-Results will be evaluated on the complete datasets and specifically on the files that
+Results will be evaluated on the complete datasets and also specifically on the files that
 do not behave consistently across subjects (\todo{explain this in introduction}).
-\todo{the last sentence just applies for Traiangular-L and on the case that I called 
-pure accuracy, other results of ALS, ALS-biases are not applied in this case}
+\todo{the last sentence (pure accuracy) is just applied for Triangular-L, other results of ALS, ALS-biases are not applied in this case}
 We evaluate prediction methods using accuracy, sensitivity and specificity defined as follows:
@@
 We compare our methods to two references, (1) a dummy classifier that always predicts the dominant class.
-as the dominent value of the utility matrix (1 or 0), (2) the Random Unreal method, used as the baseline sampling technique.
+as the dominant value of the utility matrix (1 or 0), (2) the Random Unreal method, used as the baseline sampling technique.
 
@@
 even by accessing to small training size of 10 percent. As it mentioned earlier 
-this method is not applicable in pipline due to timestamp consideration but it 
+this method is not applicable in pipeline due to time-stamp consideration but it 
 is a good criterion to estimate the performance of other methods and try to modify 
@@
 \subsubsection{Complete Rows}
-This method has some flactuation over the gowth of training set size. These falactuations are more 
+This method has some fluctuation over the gowth of training set size. These falactuations are more 
 frequent in condition pairs which have higher difference positive ratio. 
@@
 In other words despite of better performance of Complete Rows than 
-dummy classifier at the last 10 percent of the graph, its accuracies 
+dummy classifier at the last 10 percent of the graph, its accuracy 
 are less than dummy classifiers ones.  
@@
 \subsubsection{Random Subjects-RS}
-Same to the Complete Row method, RS method has some flactuation but not as frequent 
-as Complete Rows method. Althogh there are some up and down trends specialy with 
+Same to the Complete Row method, RS method has some fluctuation but not as frequent 
+as Complete Rows method. Although there are some up and down trends specially with 
 training ratio range of $0.2$ to $0.6$ but its constant growth trend after 
@@
 \noindent Figure~\ref{fig:ALS-Succeed} represents
-the accuracy graph of all Random kind methods with comparision to dummy
-classifier over the increasement of the training ratio.\\
+the accuracy graph of all Random kind methods with comparison to dummy
+classifier over the increment of the training ratio.\\
 \begin{figure}[h!]
@@
 This method takes over the dummy accuracy after having a training size more than 40 percent 
-in condition pairs of C5vsC7 and C6vsC7 but it always shows better acuracy than 
-dummy classifier ($0.73$ percent with traininfg ratio of $0.1$).\newline
+in condition pairs of C5vsC7 and C6vsC7 but it always shows better accuracy than 
+dummy classifier ($0.73$ percent with training ratio of $0.1$).\newline
 
@@
 evaluating the performance of RFNT-L and RFNT-S approches, only those accuracy results are 
-considered which their training set are equal or geather than 0.4 percent of the whole utility matrix.\newline
+considered which their training set are equal or greater than 0.4 percent of the whole utility matrix.\newline
 
@@
 dummy classifier even in its lowest accuracy value observed at training ratio of $0.6$ in C5C6 ($0.78$ percent).
-Dispite of this sudden, RFNT-L method has slight growing trend throughout the 
+Despite of this sudden, RFNT-L method has slight growing trend throughout the 
 increment of training ratio and its accuracy is always more than $90\%$.
@@
 Figure~\ref{fig:ALS-Succeed} shows the overall performance of RFNT-S methods in three different condition pairs.
-Similar to RFNT-L, this method also has constant accuracy increament with maximum less accuracy of 0.07 than 
+Similar to RFNT-L, this method also has constant accuracy increment with maximum less accuracy of 0.07 than 
 Random Unreal method throughout the experiment of C5C7 and C6C7.
@@
 be noted that, as explained before, the three methods boil down to the 
-same one (RFNU) for $\alpha<$0.3.
-
-% General conclution on results of ALS without Bias 
-In general the accuracy pattern of the two Complete Rows and 
-RS methods show similar decline and grow behavior over the 
-training ratio axis however it can be subject to considerable 
-fluctuations in differentiated condition pairs. Dispite of their 
-likely irrational behaviour, they always have better accuracy 
-for the training size with less than $0.3$ in comparison to other 
-methods. This better performance (around 75 percent)is almost three 
-times higher than other methods in condition pairs with more 
-differences but just 20 percent better when the conditions are more 
-similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$.
-Figure~\ref{fig:RS_Rows} represents
-the accuracy graph of these two methods with comparision to dummy
-classifier over the increasement of the training ratio.
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.4\linewidth}
-                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs6}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.4\linewidth}
-                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs7}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.4\linewidth}
-                \includegraphics[width=\columnwidth]{figures/RS_Rows_6vs7}
-        \end{subfigure}
-        \caption{Average performance of RS and Complete Rows methods in three different condition pairs}
-        \label{fig:RS_RowS}
-\end{figure}
-
-All the other random methods, RS and both RFNT approaches 
-are performing a continues growth Figure~\ref{fig:simple-methods} represents
-the accuracy graph of all random methods with comparision to dummy
-classifier over the increasement of the training ratio.. Although some considerable variation 
-for both triangular approches have been observed (CentOS5 vs CentOS6) 
-their constant rise leads us to the next phase of experiments which was 
-adding up bias into the current ALS technique. 
-The training set suffers from lacking the files which are almost generated towareds the end of pipeline.
-
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.4\linewidth}
-                \includegraphics[width=\columnwidth]{figures/simple-methods-5vs6}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.4\linewidth}
-		\includegraphics[width=\columnwidth]{figures/simple-methods-5vs7}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.4\linewidth}
-                \includegraphics[width=\columnwidth]{figures/simple-methods-6vs7}
-        \end{subfigure}
-	\caption{Average performance of all methods in three different condition pairs}
-	\label{fig:simple-methods}
-\end{figure}
-%-----------------------------------------------------------
-\subsection{ALS with biases}
-
-\subsubsection{RandomFile Numbers(Uniform) - RFNU}
-Figure~\ref{fig:RFNU method} represents
-the accuracy graph of RFNU method with comparision to dummy
-classifier over the increasement of the training ratio.
+same one (RFNU) for $\alpha<$0.3.{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Bias without ALS}
+In this part of our experiments we tried to eliminate the ALS prediction 
+impact on the results therefore, the elements of the matrix are going to 
+be predicted according to the biases of both their constitutive subject and file-id.
+Figure~\ref{fig:Bias-PFS} represents
+the accuracy graph of all methods as a function of the training ratio in Biases without ALS technique. 
 \begin{figure}[h!]
@@
         \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-5vs6-PFS}
+                \includegraphics[width=\columnwidth]{figures/Bias/Bias-5vs6-PFS}
         \end{subfigure}	
         \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-5vs7-PFS}
+                \includegraphics[width=\columnwidth]{figures/Bias/Bias-5vs7-PFS}
         \end{subfigure}
         \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNU-ALS-Bias-6vs7-PFS}
+                \includegraphics[width=\columnwidth]{figures/Bias/Bias-6vs7-PFS}
         \end{subfigure}
-        \caption{Average performance of RFNU methods with considering Bias in three different condition pairs}
-        \label{fig:RFNU method}
+        \caption{Average performance of all methods for three different condition pairs (Bias without ALS).}
+        \label{fig:Bias-PFS}
 \end{figure}
-\subsubsection{RNFT-L}
-Figure~\ref{fig:RFNT-L method} represents
-the accuracy graph of RFNT-L method with comparision to dummy
-classifier over the increasement of the training ratio.
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-5vs6-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-5vs7-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-L-ALS-Bias-6vs7-PFS}
-        \end{subfigure}
-        \caption{Average performance of RFNT-L methods  with considering Bias in three different condition pairs}
-        \label{fig:RFNT-L method}
-\end{figure}
-\subsubsection{RFNT-S}
-Figure~\ref{fig:RFNT-S method} represents
-the accuracy graph of RFNTS method with comparision to dummy
-classifier over the increasement of the training ratio.
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-5vs6-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-5vs7-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS-Bias/RFNT-S-ALS-Bias-6vs7-PFS}
-        \end{subfigure}
-        \caption{Average performance of RFNT-S methods  with considering Bias in three different condition pairs}
-        \label{fig:RFNT-S method}
-\end{figure}
+
+As it can be seen, Complete Columns method is less accurate than dummy classifier
+ with less than 25 percent accuracy but this is not the case for the CentOS5 vs CentOS6 
+ condition pair which it outperform dummy classifier (with accuracy of 75).
+Despite of inadequate accuracy of RS and Complete Rows sampling methods in ALS without Biases prediction technique,
+ they surpass other methods with the same accuracy of the baseline Random Unreal method.
+Triangular Distribution methods(RFNT-L, RFNT-S) reach to the baseline accuracy by $\alpha$=0.4, 
+which is earlier than the same happens for RFNU  by $\alpha$>0.5.{}
+In general, all methods except complete columns have high accuracy almost as accurat as the Random Unreal baseline method
+in this technique of prediction.As usual, three distributional methods perform equally by the only significant 
+difference at $\alpha$=0.4{}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% General conclution on results of ALS without Bias 
+%~ In general the accuracy pattern of the two Complete Rows and 
+%~ RS methods show similar decline and grow behaviour over the 
+%~ training ratio axis however it can be subject to considerable 
+%~ fluctuations in differentiated condition pairs. Despite of their 
+%~ likely irrational behaviour, they always have better accuracy 
+%~ for the training size with less than $0.3$ in comparison to other 
+%~ methods. This better performance (around 75 percent)is almost three 
+%~ times higher than other methods in condition pairs with more 
+%~ differences but just 20 percent better when the conditions are more 
+%~ similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$.
+%~ Figure~\ref{fig:RS_Rows} represents
+%~ the accuracy graph of these two methods with comparison to dummy
+%~ classifier over the increment of the training ratio.
+%~ \begin{figure}[h!]
+        %~ \centering
+        %~ \begin{subfigure}[b]{0.4\linewidth}
+                %~ \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs6}
+        %~ \end{subfigure}
+        %~ \begin{subfigure}[b]{0.4\linewidth}
+                %~ \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs7}
+        %~ \end{subfigure}
+        %~ \begin{subfigure}[b]{0.4\linewidth}
+                %~ \includegraphics[width=\columnwidth]{figures/RS_Rows_6vs7}
+        %~ \end{subfigure}
+        %~ \caption{Average performance of RS and Complete Rows methods in three different condition pairs}
+        %~ \label{fig:RS_RowS}
+%~ \end{figure}
+
+%~ All the other random methods, RS and both RFNT approaches 
+%~ are performing a continues growth Figure~\ref{fig:simple-methods} represents
+%~ the accuracy graph of all random methods with comparison to dummy
+%~ classifier over the increment of the training ratio.. Although some considerable variation 
+%~ for both triangular approaches have been observed (CentOS5 vs CentOS6) 
+%~ their constant rise leads us to the next phase of experiments which was 
+%~ adding up bias into the current ALS technique. 
+%~ The training set suffers from lacking the files which are almost generated towards the end of pipeline.
+
+%~ \begin{figure}[h!]
+        %~ \centering
+        %~ \begin{subfigure}[b]{0.4\linewidth}
+                %~ \includegraphics[width=\columnwidth]{figures/simple-methods-5vs6}
+        %~ \end{subfigure}
+        %~ \begin{subfigure}[b]{0.4\linewidth}
+		%~ \includegraphics[width=\columnwidth]{figures/simple-methods-5vs7}
+        %~ \end{subfigure}
+        %~ \begin{subfigure}[b]{0.4\linewidth}
+                %~ \includegraphics[width=\columnwidth]{figures/simple-methods-6vs7}
+        %~ \end{subfigure}
+	%~ \caption{Average performance of all methods in three different condition pairs}
+	%~ \label{fig:simple-methods}
+%~ \end{figure}
+
 %-----------------------------------------------------------
@@
 \section{Discussion}
+this is just a test of compiling
 
@@
 %%%%%% why there is a drop in ALS-RFNT-L with 60% ratio?  
-\section*{Acknowledgment}
+\section*{Acknowledgement}
 

### 2018-06-01 paper.tex

@@
 \section{Method}
+To evaluate the reproducibility of a pipeline, a retrieved matrix from 
+the subjects and file-ids is built. Subjects and file-ids are equivalent 
+to users and items, respectively, as they are known in Collaborative Filtering (CF) technique.
+Filling in the missing entries of this matrix encompasses some issues 
+which take some barriers for use of Collaborative filtering technique as it 
+has being used in e-commerce applications.
+For instance, files-ids (items) are produced in a specific order in the 
+pipeline however items are sequentially independent in general use of CF in e-commerce.
+This issue adds constraints on the selection of CF training set. Despite of random 
+selection strategy which does not taking care of item order, we had to come up with those 
+selection strategies that respect the pipeline fundamental fact about file order generation.  
+The aforementioned matrix (utility matrix), con be fully completed by processing all subjects 
+in pipeline however the whole processing can takes loads of time. This possibility of 
+having a potential complete populated matrix means despite of potential sparse matrices 
+in e-commerce case studies here the utility matrix is not sparse and 
+we can decide precisely which samples we need to select as our training set selection. 
+In this regard, to avoid the cold start issue we can take the first file-id of all 
+subjects in order to get sure that for all subjects there is at least one 
+selected element in training ratio and in the same way, all generated files 
+from the process of a random subject which can guarantee that all files 
+are presented in the selection set at least for once.
 
@@
  		\includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
-		\caption{Random Subjects method}
+		\caption{RS method}
   		\label{fig:Uniform-S-Sample-Training-set}
@@
   		\includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
-  		\caption{(Uniform) method }
+  		\caption{RFNU  method }
   		\label{fig:Diagonal-Sample-Training-set}
@@
   		\includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
-  		\caption{(Triangular-L) method}
+  		\caption{RFNT-L method}
   		\label{fig:triangular-L-Sample-Training-set}
@@
   		\includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
-  		\caption{(Triangular-S) method}
+  		\caption{RFNT-S method}
   		\label{fig:triangular-S-Sample-Training-set}

### 2018-07-11 paper.tex
Some text in the intro

@@
 
+We consider the problem of predicting the values of a variable 
+controlled by a hidden, parametrized, time dependent, deterministic 
+process over time. We assume that the variable values is observed only for 
+a limited number of time points, and we aim at predicting the values in the remaining time points.
+
+We approach the problem from the point of view of collaborative 
+filtering. The process is represented by a matrix where columns 
+represent different parametrizations (we do not assume an order on the 
+parametrizations) and rows represent the time points. The main difference with the traditional 
+collaborative filtering problem
+
+% This is just a working example
+
 Computational reproducibility, the property through which
@@
 pipeline and input data.
+
+% Other possible examples
+
+Seasonality of MS lesions.
+Thresholded stock values.
 

### 2018-07-12 paper.tex
Wrote II.A

@@
 \usepackage{nicefrac}
+\usepackage{amsmath}
 \DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
@@
 We consider the problem of predicting the values of a variable 
-controlled by a hidden, parametrized, time dependent, deterministic 
-process over time. We assume that the variable values is observed only for 
+controlled by a hidden, parameterized, time dependent, deterministic 
+process. We assume that the variable values are observed only for 
 a limited number of time points, and we aim at predicting the values in the remaining time points.
@@
 \section{Method}
+
 To evaluate the reproducibility of a pipeline, a retrieved matrix from 
@@
 
-\subsection{Collaborative filtering using ALS}
+\subsection{Collaborative filtering}
 
-We consider the collaborative filtering method as implemented in Spark's MLlb.
-% Summarize Koren, Bell and Volinsky: https://dl.acm.org/citation.cfm?id=1608614
+Collaborative filtering is a technique to predict unknown values of a 
+matrix called ``utility matrix" from the known ones. Traditionally, the 
+matrix represents the ratings of items, represented by columns, by 
+users, represented by rows. Ratings might be explicit, when users input 
+ratings through a dedicated system, or implicit, when users' behaviors 
+are analyzed to estimate their preference toward specific items. A 
+complete introduction to collaborative filtering is provided 
+in~\cite{mmdsbook}.
+
+Several methods have been proposed to implement collaborative 
+filtering. Item-item collaborative filtering~\ref{item-item} predicts 
+the rating of item $i$ by user $u$ from the ratings of items similar to 
+$i$ by user $u$. Likewise, user-user collaborative 
+filtering~\ref{user-user} predicts the rating of item $i$ by user $u$ 
+from the ratings of item $i$ by users similar to $u$. Both methods
+have been used extensively for e-commerce applications.
+
+A third class of methods, which we will apply to our problem, is based 
+on the factorization of the utility matrix to estimate latent factors 
+with which users and items are represented. This method is described 
+in~\cite{koren} and became famous as it allowed its authors to win the 
+Netflix prize in 2009. To summarize, the method aims at finding $q_i$ 
+and $p_u$ vectors of $\mathbb{R}^f$, where $f$ is the number of latent factors, such that:
+\begin{equation*}
+r_{ui} = q_i^Tp_u,
+\end{equation*}
+where $r_{ui}$ is the rating of item $i$ by user $u$. In practice, the optimization
+involves a regularization term to avoid overfiting particular users or items. The method
+finds $q_i$ and $p_u$ that minimize the following objective:
+\begin{equation*}
+\sum_{(i,u) \in \mathbb{T}}\left( r_{ui} - q_i^Tp_u\right)^2+\lambda \left( \|{q_i}\|^2 + \|{p_u}\|^2\right)
+,
+\end{equation*}
+where $\lambda$ is the regularization parameter and $\mathbb{T}$ is the training set.
+
+It is also common to include user biases $b_u$ and item biases $b_i$ in 
+the optimization, defined as the average deviation of user $u$ and item 
+$i$ to the global average $\mu$. The goal then becomes to find $q_i$ and $p_u$ that minimize the 
+following objective:
+\begin{equation*}
+\sum_{(i,u) \in \mathbb{T}}\left( r_{ui} - \mu - b_u - b_i - q_i^Tp_u\right)^2+\lambda \left( \|{q_i}\|^2 + \|{p_u}\|^2 + b_u^2 + b_i^2\right)
+\end{equation*}
+
+Two good techniques to perform the optimization are stochastic gradient descent and alternating least squares (ALS). 
+In the remainder of this paper, we use matrix factorization as implemented in 
+Apache Spark's MLLib version 2.~\todo{xxx.}, which uses ALS.
 

### 2018-07-20 paper.tex
Worked on Section II and III.A

@@
 
+\todo{Explain that columns represent subjects and rows represent files, and that these terms are used
+indifferently}
+
 \section{Method}
@@
 matrix called ``utility matrix" from the known ones. Traditionally, the 
-matrix represents the ratings of items, represented by columns, by 
-users, represented by rows. Ratings might be explicit, when users input 
-ratings through a dedicated system, or implicit, when users' behaviors 
-are analyzed to estimate their preference toward specific items. A 
-complete introduction to collaborative filtering is provided 
-in~\cite{mmdsbook}.
+matrix represents the ratings of items, represented in columns, by 
+users, represented in rows. Ratings might be explicit, when users 
+provide ratings through a dedicated system, or implicit, when users' 
+behaviors are tracked and analyzed to estimate their preferences. An 
+overview of collaborative filtering is provided 
+in~\cite{leskovec2014mining}.
 
 Several methods have been proposed to implement collaborative 
-filtering. Item-item collaborative filtering~\ref{item-item} predicts 
+filtering. Item-item collaborative filtering~\cite{breese1998empirical, linden2003amazon} predicts 
 the rating of item $i$ by user $u$ from the ratings of items similar to 
 $i$ by user $u$. Likewise, user-user collaborative 
-filtering~\ref{user-user} predicts the rating of item $i$ by user $u$ 
+filtering~\cite{breese1998empirical} predicts the rating of item $i$ by user $u$ 
 from the ratings of item $i$ by users similar to $u$. Both methods
@@
 
-A third class of methods, which we will apply to our problem, is based 
-on the factorization of the utility matrix to estimate latent factors 
-with which users and items are represented. This method is described 
-in~\cite{koren} and became famous as it allowed its authors to win the 
+A third class of methods, which is the one we will apply to our 
+problem, is based on the factorization of the utility matrix to 
+estimate latent factors along which users and items are represented. 
+This method is described 
+in~\cite{koren2009matrix} and became famous as it contributed to winning the 
 Netflix prize in 2009. To summarize, the method aims at finding $q_i$ 
@@
 
+% Explain our particular context.
+% What our matrix represents
 % Explain that you have binary classes (rounding)
-
-% Biases
+% Explain the sampling issue.
 
@@
 
-We investigated the following sampling techniques for the training set. 
-In each method, we included the first row of the matrix (first 
-generated file of each subject) and a random column (all files of a 
-random subject) to avoid cold start issues.
-
-% 0. random unreal (baseline)
-\paragraph{Random Unreal}
-The training set is sampled randomly with no restriction, that is,
-regardless of the file generation time. This method will be used as a
-baseline for comparison with other methods, although it is not
-realistic. Figure~\ref{fig:Random-Unreal-Sample-Training-set} represents 
-a training set sampled using this method.
+As explained before, the training set in our problem cannot be 
+constructed by unconstrained random sampling of the matrix.
+To address this issue, we investigated the following sampling techniques.
 
 % 2. columns
-\paragraph{Complete Columns}
+\paragraph{Complete Columns (Figure~\ref{fig:Columns-Sample-Training-set})}
 The training set is sampled by randomly selecting complete columns in
@@
 remaining subjects from the subjects in the training set.
-Figure~\ref{fig:Columns-Sample-Training-set} represents a training set 
-sampled using this method.
 
 % 3. rows
-\paragraph{Complete Rows} The training set is sampled by selecting complete 
+\paragraph{Complete Rows (Figure~\ref{fig:Rows-Sample-Training-set})} The training set is sampled by selecting complete 
 rows in the matrix, that is, the first files produced by
@@
 filtering method will then predict the reproducibility of the remaining 
-files. Figure~\ref{fig:Rows-Sample-Training-set} represents a training 
-set sampled using this method.
+files.
+
 \begin{figure}[h!]
         \centering
-	\begin{subfigure}[b]{0.4\linewidth}
-		\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
-  		\caption{Random Unreal method}
-  		\label{fig:Random-Unreal-Sample-Training-set}
-	\end{subfigure}
         \begin{subfigure}[b]{0.4\linewidth}
@@
         \end{subfigure}
+        \begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
+                  \caption{Random Unreal method}
+                  \label{fig:Random-Unreal-Sample-Training-set}
+        \end{subfigure}
         \caption{Sample training set for different methods with a training ratio of 0.4.}                
@@
 
-\paragraph{Random Subjects -- RS} This method builds the 
+\paragraph{Random Subjects -- RS (Figure~\ref{fig:Uniform-S-Sample-Training-set})} This method builds the 
 training set by selecting the files from random subjects 
@@
 files are sampled according to their production time-stamps.
-Figure~\ref{fig:Uniform-S-Sample-Training-set} represents a training 
-set sampled using this method.
 
-\paragraph{Random File Numbers (Uniform) -- RFNU}
-
+\paragraph{Random File Numbers (Uniform) -- RFNU (Figure~\ref{fig:Diagonal-Sample-Training-set})}
 The number of files selected for every subject is randomly selected in
@@
 number of files $N_{f}$ and \textit{a} is set according to training ratio $\alpha$ as follows:
-
 \[
@@
 \]
-
 This method is realistic as files are sampled according to their production time-stamps.
@@
 a triangular distribution with parameters \textit{a}, \textit{b} and 
-\textit{c} (\todo{see Figure X}). The mean of the distribution is 
-$\frac{a+b+c}{3}$. In our case, we set \textit{c} to $N_{f}$ and we set 
-\textit{a} and \textit{b} with two approaches meant to ensure that the 
+\textit{c} as in Figure~\ref{fig:triangular}. The mean of the distribution is 
+$\frac{a+b+c}{3}$. We set \textit{c} to $N_{f}$ and we set 
+\textit{a} and \textit{b} with two approaches that ensure that the 
 average of the distribution is $\alpha N_{f}$ ($\alpha$ is the training 
@@
 \begin{enumerate}
-        \item Largest a (RFNT-L): a is set to the 
+        \item Largest a (RFNT-L, Figure~\ref{fig:triangular-L-Sample-Training-set}): a is set to the 
         largest possible value, i.e., b. The average of the 
@@
         $a=\frac{3\alpha-1}{2}N_{f}$.
-                \item Smallest a (RFNT-S): a is 
+                \item Smallest a (RFNT-S, Figure~\ref{fig:triangular-S-Sample-Training-set}): a is 
         set to the smallest possible value, i.e., 0. The average of the 
@@
         $b=N_{f}(3\alpha-1)$. To ensure that $b<N_{f}$, we actually set 
-        $b=\min(N_{f}, N_{f}(3\alpha-1))$. 
+        $b$ to $\min(N_{f}, N_{f}(3\alpha-1))$. 
 \end{enumerate}
@@
 define RFNT methods as the RFNU one presented previously.
-
 As illustrated in Figures~\ref{fig:triangular-L-Sample-Training-set} 
@@
 $\alpha$, all subjects will have at least a few files in the training 
-set.
+set, which is not the case for RFNU.
+\begin{figure}
+\centering
+\includegraphics[width=0.5\columnwidth]{figures/triangular.pdf}
+\caption{Triangular distribution}
+\label{fig:triangular}
+\end{figure}
+
+% 0. random unreal (baseline)
+\paragraph{Random Unreal (Figure ~\ref{fig:Random-Unreal-Sample-Training-set})}
+The training set is sampled in a random uniform way, 
+regardless of the file generation times. This method will be used as a
+baseline for comparison with other methods, although it is not
+realistic.
+
+In each method, we also included the first row of the matrix (first 
+generated file of each subject) and a random column (all files of a 
+random subject) to avoid cold start issues.
 
 \section{Dataset}
+
+\subsection{Synthetic Data}
+
+We generated synthetic matrices as shown in 
+Figure~\ref{fig:synthetic-data}. Each matrix has 100 files and 100 
+subjects of different \emph{types}. Subjects of the same type behave 
+identically and all types contain the same number of subjects $\pm$ 1 
+\todo{Soudabeh: check that}. Such a decomposition by subject type 
+correspond to the case where different subjects may have data of 
+different nature, as it is for instance the case in the neuroimaging 
+dataset of the Human Connectome Project~\cite{hcp} where not all the 
+subjects have the same amount of images.
+
+For subjects of a given type, matrix elements vary in $log(n)$  blocks, 
+where $n$ is the number of types, with all the possible variation 
+patterns: some types do not vary at all, while other ones vary in every 
+block. Such variation patterns are meant to mimic the logic of data 
+processing pipelines: each block of files represents the files produced 
+at a given stage of the pipeline, which may or may not contain 
+reproducibility errors depending on the subject type.
+
+\begin{figure}
+\centering
+        %\begin{subfigure}[b]{0.4\linewidth}
+                  %\includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/1_SubjectType_utility_matrix.png}
+                  %\caption{1 type}
+        %\end{subfigure}
+        \begin{subfigure}[b]{0.4\linewidth}
+                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/2_SubjectType_utility_matrix.png}
+                  \caption{2 types}
+        \end{subfigure}
+        \begin{subfigure}[b]{0.4\linewidth}
+                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/4_SubjectType_utility_matrix.png}
+                  \caption{4 types}
+        \end{subfigure}
+                \begin{subfigure}[b]{0.4\linewidth}
+                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/8_SubjectType_utility_matrix.png}
+                  \caption{8 types}
+        \end{subfigure}
+                \begin{subfigure}[b]{0.4\linewidth}
+                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/16_SubjectType_utility_matrix.png}
+                  \caption{16 types}
+        \end{subfigure}
+                \begin{subfigure}[b]{0.4\linewidth}
+                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/32_SubjectType_utility_matrix.png}
+                  \caption{32 types}
+        \end{subfigure}
+                \begin{subfigure}[b]{0.4\linewidth}
+                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/64_SubjectType_utility_matrix.png}
+                  \caption{64 types}
+        \end{subfigure}
+\caption{Synthetic Data}
+\label{fig:synthetic-data}
+\end{figure}
+
+\subsection{Real Data}
 

### 2018-07-20 paper.tex
Added gnuplot scripts and result figures

@@
   Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada\\
-  {first.last}@concordia.ca\\
-  $^*$ These authors have contributed equally
-}
+  {first.last}@concordia.ca}
 
@@
 indifferently}
+
+\todo{Mention why this is Big Data}
+
+\todo{Cite Cecile's paper}
+
+\todo{Define reproducibility \emph{errors}}
 
@@
                   \includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
-                  \caption{Complete Columns method}
+                  \caption{Complete Columns}
                   \label{fig:Columns-Sample-Training-set}
@@
                   \includegraphics[width=\columnwidth]{figures/5vs7_rows_04_training}
-                  \caption{Complete Rows method}
+                  \caption{Complete Rows}
                   \label{fig:Rows-Sample-Training-set}
@@
                  \includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
-                \caption{RS method}
+                \caption{Random Subjects (RS)}
                   \label{fig:Uniform-S-Sample-Training-set}
@@
                   \includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
-                  \caption{RFNU  method }
+                  \caption{RFNU}
                   \label{fig:Diagonal-Sample-Training-set}
@@
                   \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
-                  \caption{RFNT-L method}
+                  \caption{RFNT-L}
                   \label{fig:triangular-L-Sample-Training-set}
@@
                   \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
-                  \caption{RFNT-S method}
+                  \caption{RFNT-S}
                   \label{fig:triangular-S-Sample-Training-set}
@@
         \includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
-                  \caption{Random Unreal method}
+                  \caption{Random Unreal}
                   \label{fig:Random-Unreal-Sample-Training-set}
@@
 
+\todo{Soudabeh, can you remove the caption on all matrices?}
+
 \subsection{Synthetic Data}
@@
 different nature, as it is for instance the case in the neuroimaging 
-dataset of the Human Connectome Project~\cite{hcp} where not all the 
+dataset of the Human Connectome Project~\cite{van2013wu} where not all the 
 subjects have the same amount of images.
@@
 We collected data to evaluate the computational reproducibility of analysis
-pipelines of the Human Connectome Project~\cite{general-hcp}. We
+pipelines of the Human Connectome Project~\cite{glasser2013minimal}. We
 processed a set S of 94 subjects randomly selected in the S500 HCP
@@
 versions of the CentOS operating system (5.?, 6.? and 7.?), using the
-PreFreesurfer, Freesurfer, PostFreesurfer and fMRIVolume pipelines
-described in~\cite{hcp-pipelines} and available at \todo{URL}. For
+PreFreesurfer and Freesurfer pipelines
+described in~\cite{glasser2013minimal} and available at \todo{URL}. For
 each pipeline, we identified the set F of files produced for all
@@
 
-Figure~\ref{fig:utility metrices} shows the difference matrices
-obtained for the PreFreesurfer pipeline. The computational
-reproducibility of the PreFreesurfer pipeline varies across subjects,
-which motivates our study. Nevertheless, some files behave
+Figure~\ref{fig:utility-matrices} shows the utility matrices
+obtained for the PreFreesurfer and Freesufer pipeline. The computational
+reproducibility of these pipelines varies across subjects,
+but some files behave
 consistently across all subjects, leading to complete black or white
-lines. The ratio of positive elements in utility matrix of CentOS5 vs CentOS6(C5C6),  CentOS5 vs CentOS7(C5C7) and  CentOS6 vs CentOS7(C6C7) are
-$0.34$, $0.79$ and $0.79$ respectively.
+lines.
+%The ratio of positive elements in utility matrix of CentOS5 vs CentOS6(C5C6),  CentOS5 vs CentOS7(C5C7) and  CentOS6 vs CentOS7(C6C7) are
+%$0.34$, $0.79$ and $0.79$ respectively.
 
@@
   \centering
-  \begin{subfigure}[b]{0.5\linewidth}
-        \includegraphics[width=\columnwidth]{figures/utility_5vs6_PFS}
-  \caption{Utility matrix of CentOS5 vs CentOS6}
+  \begin{subfigure}[b]{0.45\linewidth}
+        \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v6_utility_matrix.png}
+  \caption{PFS, C5 vs C6}
   \end{subfigure}
-  \begin{subfigure}[b]{0.5\linewidth}
-         \includegraphics[width=\columnwidth]{figures/utility_5vs7_PFS}
-  \caption{Utility matrix of CentOS5 vs CentOS7}
+  \begin{subfigure}[b]{0.45\linewidth}
+         \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v7_utility_matrix.png}
+  \caption{PFS, C5 vs C7}
   \end{subfigure}
-  \begin{subfigure}[b]{0.5\linewidth}
-        \includegraphics[width=\columnwidth]{figures/utility_6vs7_PFS}
-  \caption{Utility matrix of CentOS6 vs CentOS7}
-  \label{fig:utility metrices}
+  \begin{subfigure}[b]{0.45\linewidth}
+        \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_6v7_utility_matrix.png}
+  \caption{PFS, C6 vs C7}
   \end{subfigure}
+  \begin{subfigure}[b]{0.45\linewidth}
+        \includegraphics[width=\columnwidth]{data/Utility_Matrix/FS-100files/FS-First-bound-100files.png}
+  \caption{FS (first 100 files), C6 vs C7}
+  \end{subfigure}
+  \caption{Utility matrices, PreFreesurfer (PFS) and Freesurfer (FS) pipelines}
+    \label{fig:utility-matrices}
 \end{figure}
-
-as it can be seen, some of the files are consistent cross the subjects 
-which means that there are some cases that a file has an error in whole subjects (complete white)or 
-in another case no checksum difference has been observed for a file among all subjects (complete black).
-These kind of consistent behaviour makes us to discard the prediction of these file-id's elements 
-from the calculated accuracy in some phases of our experiments.
-
-% Describe your dataset: pipeline(s) used, input data, operating systems (CentOS5, 6, 7), matrix.
-
-% 1. Prefreesurfer (what you have)
-% 2. Freesurfer, with the same subjects as in Prefreesurfer.
-% 3. PostFreesurfer
-% 4. fmriVolume
 
@@
 
-Four experiments have been conducted to evaluate the performance of our 
+Three experiments have been conducted for each dataset to evaluate the performance of our 
 predictions using (1) ALS without biases, (2) ALS with biases, (3) Biases only. 
-Results will be evaluated on the complete datasets and also specifically on the files that
-do not behave consistently across subjects (\todo{explain this in introduction}).
-\todo{the last sentence (pure accuracy) is just applied for Triangular-L, other results of ALS, ALS-biases are not applied in this case}
-We evaluate prediction methods using accuracy, sensitivity and specificity defined as follows:
+Results will be evaluated using accuracy, sensitivity and specificity defined as follows:
 \[
@@
 \]
-Where TP is the number of True Positives (correctly predicted errors), 
+Where TP is the number of True Positives (correctly predicted reproducibility errors), 
 FP is the number of False Positives, TN is the number of true negatives 
-and FN is the number of false negatives.
+and FN is the number of false negatives. \todo{Check if we want to report sensitivity and specificity, otherwise remove.}
 
-We compare our methods to two references, (1) a dummy classifier that always predicts the dominant class.
-as the dominant value of the utility matrix (1 or 0), (2) the Random Unreal method, used as the baseline sampling technique.
+We compare our sampling methods to (1) a dummy classifier that always predicts the value in the majority class
+ and (2) the Random Unreal method, used as the baseline sampling technique.
 
-\subsection{ALS without biases}
-In this phase of the experiment, the Alternating Least Squares 
-technique of Collaborative Filtering is applied for all provided 
-methods. Our four sampling techniques are compared in 
-Figure~\ref{fig:ALS-Failure} and the results are described in the next 
-sub-sections.
+\subsection{Synthetic Data}
 
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-5vs6}
+\subsubsection{ALS without Bias}
+
+Accuracy results for the different numbers of subject types are 
+reported in Figure~\ref{fig:results-synthetic}. By construction, the 
+accuracy of the dummy classifier is 0.5 for all subject types. Random 
+Unreal performs very well for all subject types, which confirms that 
+ALS is working correctly. Unsurprisingly, all the other methods perform 
+better than the dummy classifier, and their accuracy decreases as the 
+number of subject types increases.
+
+However, only 3 methods are able to provide accuracy values above 0.85 
+for all subject types: Random Subjects (RS), RFNU and RFNTL. This is 
+due to the fact that these methods are the only ones that can sample 
+files produced toward the end of the execution while maintaining a 
+reduced number of empty columns. Surprisingly, RFNTS does not perform 
+well for more than 2 subject types \todo{Check that.}.
+
+RS, RFNU and RFNTL achieve a 90\% accuracy for a training ratio of 
+about 0.85. Therefore, 15\% of the computations could potentially be 
+saved in such reproducibility studies.
+
+\begin{figure*}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-2-types.pdf}
+        \caption{2 subject types}
 \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-5vs7}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-4-types.pdf}
+        \caption{4 subject types}
 \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/AlS-Failure-6vs7}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-8-types.pdf}
+        \caption{8 subject types}
 \end{subfigure}
-        \caption{Average accuracy of Complete Columns, RS, Complete Rows and Random Unreal methods in three different condition pairs.}
-        \label{fig:ALS-Failure}
-\end{figure}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-16-types.pdf}
+        \caption{16 subject types}
+\end{subfigure}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-32-types.pdf}
+        \caption{32 subject types}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-64-types.pdf}
+        \caption{64 subject types}
+\end{subfigure}
+\caption{Accuracy results on synthetic data, ALS \emph{without} bias.}
+\label{fig:results-synthetic}
+\end{figure*}
 
-\subsubsection{Random Unreal}
-This method has a great performance with absolute accuracy of more than $0.95$ 
-even by accessing to small training size of 10 percent. As it mentioned earlier 
-this method is not applicable in pipeline due to time-stamp consideration but it 
-is a good criterion to estimate the performance of other methods and try to modify 
-the proposed methods in order to their accuracy be as closed as possible to the 
-Random Unreal method ones.
+\subsubsection{ALS with Bias}
 
-\subsubsection{Complete Columns}
-The Complete Columns method has almost a constant accuracy even if the training ratio increased and it
-is almost two times less than dummy classifier in more differentiated
-condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the
-best case which it means in similar conditions the Complete Columns
-accuracy is as much accurate as the Dummy classifier is, $0.65$
-percent.
-\\
-\subsubsection{Complete Rows}
-This method has some fluctuation over the gowth of training set size. These falactuations are more 
-frequent in condition pairs which have higher difference positive ratio. 
-Also by enlarging the training ratio specially between $0.3$ to $0.7$, 
-we can see dummy classifier has better results than Complete Rows ones. 
-In other words despite of better performance of Complete Rows than 
-dummy classifier at the last 10 percent of the graph, its accuracy 
-are less than dummy classifiers ones.  
-\\
-\subsubsection{Random Subjects-RS}
-Same to the Complete Row method, RS method has some fluctuation but not as frequent 
-as Complete Rows method. Although there are some up and down trends specially with 
-training ratio range of $0.2$ to $0.6$ but its constant growth trend after 
-training ratio $0.3$ in condition pairs with high difference positive ratio is considerable.
-The method can be $0.99$ percent accurate when it has over 70 percent of the data however 
-this accuracy can be achived with higher training ratio (over 80 percent) for C5C6.  
-\\
-\\
-\noindent Figure~\ref{fig:ALS-Succeed} represents
-the accuracy graph of all Random kind methods with comparison to dummy
-classifier over the increment of the training ratio.\\
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs6}
+Results of ALS with Bias are reported in Figure~\ref{fig:results-synthetic-als-bias}.
+RS, RFNU and RFNTL remain the methods that best compare to Random Unreal, but the achieved
+accuracy is much lower than without Biases. This is due to the fact that biases \ldots \todo{finish that.}
+
+\begin{figure*}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-2-types.pdf}
+        \caption{2 subject types}
 \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs7}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-4-types.pdf}
+        \caption{4 subject types}
 \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-6vs7}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-8-types.pdf}
+        \caption{8 subject types}
 \end{subfigure}
-        \caption{Average performance of RFNU methods in three different condition pairs}
-        \label{fig:ALS-Succeed}
-\end{figure}
-\subsubsection{Random File Numbers(Uniform) - RFNU}
-The continuous rise of RFNU accuracy trend can be observed in Figure~\ref{fig:ALS-Succeed}.
-However a 0.03 drop is recorded in C6C7 between training ratio size of $0.8$ to $0.9$. 
-This method takes over the dummy accuracy after having a training size more than 40 percent 
-in condition pairs of C5vsC7 and C6vsC7 but it always shows better accuracy than 
-dummy classifier ($0.73$ percent with training ratio of $0.1$).\newline
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-16-types.pdf}
+        \caption{16 subject types}
+\end{subfigure}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-32-types.pdf}
+        \caption{32 subject types}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-64-types.pdf}
+        \caption{64 subject types}
+\end{subfigure}
+\caption{Accuracy results on synthetic data, ALS \emph{with} bias.}
+\label{fig:results-synthetic-als-bias}
+\end{figure*}
 
-% ALS-RFNT approaches
-\indent As it mentioned earlier, for $\alpha < \nicefrac{1}{3}$ RFNT approaches are not applicable, 
-therefor for training ratio less than $0.4$ RFNU method is employed. As a result, in terms of 
-evaluating the performance of RFNT-L and RFNT-S approches, only those accuracy results are 
-considered which their training set are equal or greater than 0.4 percent of the whole utility matrix.\newline
+\subsection{Real Data}
 
-\subsubsection{RFNT-L}
+\subsubsection{ALS without bias}
 
-In Figure~\ref{fig:ALS-Succeed}, the results show that RFNT-L performance is always more accurate than
-dummy classifier even in its lowest accuracy value observed at training ratio of $0.6$ in C5C6 ($0.78$ percent).
-Despite of this sudden, RFNT-L method has slight growing trend throughout the 
-increment of training ratio and its accuracy is always more than $90\%$.
+\begin{figure*}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v6.pdf}
+        \caption{PFS, CentOS5 vs CentOS6}
+\end{subfigure}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v7.pdf}
+        \caption{PFS, CentOS5 vs CentOS7}
+\end{subfigure}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-6v7.pdf}
+        \caption{PFS, CentOS6 vs CentOS7}
+\end{subfigure}\hfill
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/FS-100files/ALS-FS100files.pdf}
+        \caption{FS, CentOS6 vs CentOS7}
+\end{subfigure}
+\caption{Accuracy results on PreFresurfer (PFS) and Freesurfer (FS) data, ALS \emph{without} bias.}
+\label{fig:results-real-als}
+\end{figure*}
 
-\subsubsection{RFNT-S}
-Figure~\ref{fig:ALS-Succeed} shows the overall performance of RFNT-S methods in three different condition pairs.
-Similar to RFNT-L, this method also has constant accuracy increment with maximum less accuracy of 0.07 than 
-Random Unreal method throughout the experiment of C5C7 and C6C7.
+\subsubsection{ALS with bias}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{ALS with biases}
-In this part of the experiment, the effect of both subject and file 
-biases are considered in the prediction. Our three random sampling 
-techniques (RFNU, RFNT-L and RFNT-S) are compared in 
-Figure~\ref{fig:ALS-Bias-PFS} as a function of the training 
-ratio $\alpha$.
-
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-5vs6-PFS}
+\begin{figure*}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v6.pdf}
+        \caption{PFS, CentOS5 vs CentOS6}
 \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-5vs7-PFS}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v7.pdf}
+        \caption{PFS, CentOS5 vs CentOS7}
 \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-6vs7-PFS}
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-6v7.pdf}
+        \caption{PFS, CentOS6 vs CentOS7}
+\end{subfigure}\hfill
+\begin{subfigure}[b]{0.4\linewidth}
+        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/FS-100files/ALS-Bias-FS100files.pdf}
+        \caption{FS, CentOS6 vs CentOS7}
 \end{subfigure}
-        \caption{Average performance of random methods for three different condition pairs (ALS with Bias).}
-        \label{fig:ALS-Bias-PFS}
-\end{figure}
-\todo{Add $\alpha$ to the x labels in the Figure}
-
-All three methods reach the accuracy of the baseline Random Unreal 
-method from $\alpha$=0.5. RFNT methods reach this accuracy earlier than 
-RFNU, from $\alpha$=0.4. For lower training ratios, all methods 
-outperform the dummy classifier for one condition pair (CentOS5 vs 
-CentOS6) but this is not the case for the other conditions. It should 
-be noted that, as explained before, the three methods boil down to the 
-same one (RFNU) for $\alpha<$0.3.{}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Bias without ALS}
-In this part of our experiments we tried to eliminate the ALS prediction 
-impact on the results therefore, the elements of the matrix are going to 
-be predicted according to the biases of both their constitutive subject and file-id.
-Figure~\ref{fig:Bias-PFS} represents
-the accuracy graph of all methods as a function of the training ratio in Biases without ALS technique. 
-\begin{figure}[h!]
-        \centering
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/Bias/Bias-5vs6-PFS}
-        \end{subfigure}        
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/Bias/Bias-5vs7-PFS}
-        \end{subfigure}
-        \begin{subfigure}[b]{0.8\linewidth}
-                \includegraphics[width=\columnwidth]{figures/Bias/Bias-6vs7-PFS}
-        \end{subfigure}
-        \caption{Average performance of all methods for three different condition pairs (Bias without ALS).}
-        \label{fig:Bias-PFS}
-\end{figure}
-
-As it can be seen, Complete Columns method is less accurate than dummy classifier
- with less than 25 percent accuracy but this is not the case for the CentOS5 vs CentOS6 
- condition pair which it outperform dummy classifier (with accuracy of 75).
-Despite of inadequate accuracy of RS and Complete Rows sampling methods in ALS without Biases prediction technique,
- they surpass other methods with the same accuracy of the baseline Random Unreal method.
-Triangular Distribution methods(RFNT-L, RFNT-S) reach to the baseline accuracy by $\alpha$=0.4, 
-which is earlier than the same happens for RFNU  by $\alpha$>0.5.{}
-In general, all methods except complete columns have high accuracy almost as accurat as the Random Unreal baseline method
-in this technique of prediction.As usual, three distributional methods perform equally by the only significant 
-difference at $\alpha$=0.4{}.
+\caption{Accuracy results on PreFresurfer (PFS) and Freesurfer (FS) data, ALS \emph{with} bias.}
+\label{fig:results-real-als-bias}
+\end{figure*}
 
@@
 
+% Real values, we expect the best sampling method to remain the same.
+
 \section{Conclusion}
@@
 %%%%%% why there is a drop in ALS-RFNT-L with 60% ratio?
+
+\todo{Make sure the code is available and results are reproducible.}
+
 \section*{Acknowledgement}

### 2018-07-23 paper.tex
Fixed normalization in distributions. Worked on results. Started working on intro.

@@
 
+Computational reproducibility, the property through which
+computational results can be recomputed over time and
+space~\cite{peng2011reproducible}, has become a critical component of scientific
+methodology with the rise of the reproducibility crisis in several 
+domains~\cite{baker2016there}. Among the factors hampering 
+computational reproducibility, infrastructural characteristics such as 
+the operating system play an important role. In neurosciences, our 
+primary field of interest, several studies have shown the effect of the 
+operating system on computational 
+results~\cite{gronenschild2012effects, glatard2015reproducibility}. 
+However, conducting such reproducibility studies at scale is cumbersome 
+due to the execution time of data analysis pipelines, which easily 
+exceeds a few hours.
+
 We consider the problem of predicting the values of a variable 
-controlled by a hidden, parameterized, time dependent, deterministic 
-process. We assume that the variable values are observed only for 
-a limited number of time points, and we aim at predicting the values in the remaining time points.
+controlled by a hidden, parameterized, time-dependent, deterministic 
+process. We assume that the variable values are observed only for a 
+limited number of time points and process parameters, and we aim at 
+predicting the values for the remaining time points and parameters.
+
+This problem description maps directly to the evaluation of 
+computational reproducibility in scientific pipelines: the process is 
+the pipeline, it is hidden since we consider it as a black box (we 
+don't inspect its source code), it is parametrized as it behaves 
+differently on different input datasets and parameters, it is 
+time-dependent as the value of the variable of interest varies 
+throughout the course of the pipeline execution. The variable of 
+interest is whether the pipeline outputs, most likely the files it 
+produces, are identical between execution conditions.
 
 We approach the problem from the point of view of collaborative 
-filtering. The process is represented by a matrix where columns 
-represent different parametrizations (we do not assume an order on the 
-parametrizations) and rows represent the time points. The main difference with the traditional 
-collaborative filtering problem
-
-% This is just a working example
-
-Computational reproducibility, the property through which
-computational results can be recomputed over time and
-space~\cite{stodden}, has become a critical component of scientific
-methodology with the rise of the reproducibility crisis in several
-domains~\cite{xxx}. Among the factors hampering computational
-reproducibility, infrastructural characteristics such as the operating
-system play an important role. In neurosciences, our primary field of
-interest, several studies have shown the effect of the operating
-system on computational results. However, conducting such
-reproducibility studies at scale is cumbersome due to the execution
-time of data analysis pipelines, which easily exceeds a few hours.
+filtering, inspired by previous examples that applied this method 
+outside of its initial application domain~\cite{feng2013efficient}. The 
+process is represented by a matrix where columns represent different 
+parametrizations and rows represent the files produced by the 
+execution. Parmeterizations may represent different input data sets or 
+parameter values, on which we do not assume an order. On the contrary, 
+an order is defined on the files, from their last modification time in 
+a sequential execution. We assume that files are produced in the same 
+order regardless of the parametrization, which is not always true, in 
+particular when pipelines are multi-threaded, but in general 
+reasonable \todo{explain "local" truth of this assumption}. This order imposes a constraint on the construction of the
+training set since files
 
@@
 
-% Computational reproducibility is an issue, for instance among
-% different operating systems (refer to Glatard FINF 2015,
-% Gronenschild 2012).
-
 % Scientific data analysis pipeline executions are long (give examples
@@
 
-% Refer to Germain et al 2008.
-
 % Define subjects, pipelines.
-
-% Problem: predict the reproducibility of pipeline files from other
-% subjects and the first files produced by a pipeline. Restrict the
-% study to binary classification.
 
@@
 
-\todo{Cite Cecile's paper}
+\todo{Define reproducibility \emph{errors}}
 
-\todo{Define reproducibility \emph{errors}}
+\todo{talk about time-constrained processes}
+
+The paper makes the following contributions:
+\begin{enumerate}
+\item We model reproducibility evaluations in data processing pipelines as a collaborative filtering problem.
+\item We propose strategies to sample the training set under time constraints.
+\item We evaluate and compare our sampling strategies on synthetic and real datasets.
+\end{enumerate}
 
@@
 Therefore we can take the first row and first column to avoid cold start issues.
+
+\todo{Restrict to binary classification}
 
@@
 \]
-This method is realistic as files are sampled according to their production time-stamps.
+ For $\alpha > 0.5$, this ensures that the average number of files in 
+ the training set is $\alpha N_f$. For $\alpha \leq 0.5$, the number of 
+ files selected in every subject is sampled from $U(0,N_f)$ with 
+ probability $2\alpha$, and set to 0 otherwise.
+RFNU is realistic as files are sampled according to their production time-stamps.
 Due to sampling issues, it is possible that the actual training ratio obtained with this method
@@
 The number of files selected for every subject is randomly selected in
-a triangular distribution with parameters \textit{a}, \textit{b} and 
-\textit{c} as in Figure~\ref{fig:triangular}. The mean of the distribution is 
+a triangular distribution $T(a, b, c)$ as in Figure~\ref{fig:triangular}. The mean of the distribution is 
 $\frac{a+b+c}{3}$. We set \textit{c} to $N_{f}$ and we set 
@@
         distribution is $\frac{2a+N_{f}}{3}$, therefore 
-        $a=\frac{3\alpha-1}{2}N_{f}$.
+        $a=\frac{3\alpha-1}{2}N_{f}$. When $\alpha \leq 1/3$, the 
+        number of files in every subject is sampled from $T(0, 0, N_f)$ 
+        with probability $3\alpha$ and set to 0 otherwise, to ensure that the average number of files
+        in the training set is $\alpha N_f$.
         \item Smallest a (RFNT-S, Figure~\ref{fig:triangular-S-Sample-Training-set}): a is 
@@
         distribution is $\frac{b+N_{f}}{3}$, therefore 
-        $b=N_{f}(3\alpha-1)$. To ensure that $b<N_{f}$, we actually set 
-        $b$ to $\min(N_{f}, N_{f}(3\alpha-1))$. 
+        $b=N_{f}(3\alpha-1)$. This implies that $\alpha \geq 1/3$, so 
+        that $b \geq 0$, and $\alpha \leq 2/3$, so that $b \leq N_f$. 
+        When $\alpha < 1/3$, we set $b=0$ and the number of files 
+        selected in every subject is sampled from $T(0, 0, N_f)$ with 
+        probability $3\alpha$ and set to 0 otherwise, as in RFNT-L. 
+        When $\alpha \geq 2/3$, we set $b=N_f$ and the number of files 
+        selected in every subject is sampled from $T(0, N_f, N_f)$ with 
+        probability $3(1-\alpha)$ and set to $N_f$ otherwise, still to 
+        ensure that the average number of files in the training set is 
+        $\alpha N_f$.
 \end{enumerate}
-It should be noted that $\alpha$ must be larger than $\frac{1}{3}$ for 
-a and b to remain positive. For training ratios lower than $\frac{1}{3}$, we 
-define RFNT methods as the RFNU one presented previously.
 As illustrated in Figures~\ref{fig:triangular-L-Sample-Training-set} 
@@
 \includegraphics[width=0.5\columnwidth]{figures/triangular.pdf}
-\caption{Triangular distribution}
+\caption{Triangular distribution $T(a, b, c)$}
 \label{fig:triangular}
@@
 
-We compare our sampling methods to (1) a dummy classifier that always predicts the value in the majority class
- and (2) the Random Unreal method, used as the baseline sampling technique.
+We compare our sampling methods to (1) a dummy classifier that always 
+predicts the value in the majority class and (2) the Random Unreal 
+method, used as the baseline sampling technique. All reported values are averages
+over 5 repetitions. \todo{Report model parameters, including number of factors.}
 
@@
 
-Results of ALS with Bias are reported in Figure~\ref{fig:results-synthetic-als-bias}.
+Results of ALS with bias are reported in Figure~\ref{fig:results-synthetic-als-bias}.
 RS, RFNU and RFNTL remain the methods that best compare to Random Unreal, but the achieved
@@
 
+Results for ALS without bias are reported in 
+Figure~\ref{fig:results-real-als}. Among the methods that performed 
+well in the synthetic dataset, RFNU performs the best, with an accuracy
+higher than 0.95 \todo{check value} for all datasets, when the training ratio is larger than 0.5. RS and RFNTL
+are slightly underperforming compared to RFNU.
+Complete rows and complete columns do not even reach the accuracy of the 
+dummy classifier. The reference method, Random Unreal, has an accuracy close
+to 1, which shows that collaborative filtering works well on this dataset too.
+
 \begin{figure*}
@@
 
+Results for ALS with bias are reported in 
+Figure~\ref{fig:results-real-als-bias}. From a training ratio of 0.5, 
+all methods have a very good accuracy for all datasets, except complete 
+columns in Figure~\ref{fig:pfs-c5vsc7-bias}. All methods except RFNU, 
+RFNTL and RFNTS also perform well for a training ratio lower than 0.5. 
+Overall, the accuracy of the methods is much higher than without bias: 
+the file bias is very strong in this dataset, as illustrated by the large number
+of constant lines in the matrices in Figure~\ref{fig:utility-matrices}.
+
 \begin{figure*}
@@
         \caption{PFS, CentOS5 vs CentOS7}
+        \label{fig:pfs-c5vsc7-bias}
 \end{subfigure}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% General conclution on results of ALS without Bias 
-%~ In general the accuracy pattern of the two Complete Rows and 
-%~ RS methods show similar decline and grow behaviour over the 
-%~ training ratio axis however it can be subject to considerable 
-%~ fluctuations in differentiated condition pairs. Despite of their 
-%~ likely irrational behaviour, they always have better accuracy 
-%~ for the training size with less than $0.3$ in comparison to other 
-%~ methods. This better performance (around 75 percent)is almost three 
-%~ times higher than other methods in condition pairs with more 
-%~ differences but just 20 percent better when the conditions are more 
-%~ similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$.
-%~ Figure~\ref{fig:RS_Rows} represents
-%~ the accuracy graph of these two methods with comparison to dummy
-%~ classifier over the increment of the training ratio.
-%~ \begin{figure}[h!]
-        %~ \centering
-        %~ \begin{subfigure}[b]{0.4\linewidth}
-                %~ \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs6}
-        %~ \end{subfigure}
-        %~ \begin{subfigure}[b]{0.4\linewidth}
-                %~ \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs7}
-        %~ \end{subfigure}
-        %~ \begin{subfigure}[b]{0.4\linewidth}
-                %~ \includegraphics[width=\columnwidth]{figures/RS_Rows_6vs7}
-        %~ \end{subfigure}
-        %~ \caption{Average performance of RS and Complete Rows methods in three different condition pairs}
-        %~ \label{fig:RS_RowS}
-%~ \end{figure}
-
-%~ All the other random methods, RS and both RFNT approaches 
-%~ are performing a continues growth Figure~\ref{fig:simple-methods} represents
-%~ the accuracy graph of all random methods with comparison to dummy
-%~ classifier over the increment of the training ratio.. Although some considerable variation 
-%~ for both triangular approaches have been observed (CentOS5 vs CentOS6) 
-%~ their constant rise leads us to the next phase of experiments which was 
-%~ adding up bias into the current ALS technique. 
-%~ The training set suffers from lacking the files which are almost generated towards the end of pipeline.
-
-%~ \begin{figure}[h!]
-        %~ \centering
-        %~ \begin{subfigure}[b]{0.4\linewidth}
-                %~ \includegraphics[width=\columnwidth]{figures/simple-methods-5vs6}
-        %~ \end{subfigure}
-        %~ \begin{subfigure}[b]{0.4\linewidth}
-                %~ \includegraphics[width=\columnwidth]{figures/simple-methods-5vs7}
-        %~ \end{subfigure}
-        %~ \begin{subfigure}[b]{0.4\linewidth}
-                %~ \includegraphics[width=\columnwidth]{figures/simple-methods-6vs7}
-        %~ \end{subfigure}
-        %~ \caption{Average performance of all methods in three different condition pairs}
-        %~ \label{fig:simple-methods}
-%~ \end{figure}
-
-%-----------------------------------------------------------
-% Present your results: accuracy, ROC curves, transparency matrix, factors.
-
-% Try with different numbers of factors.
+\todo{Different number of factors.}
 
 \section{Discussion}
-this is just a test of compiling
 
-% Not all subjects behave the same, which motivates the Big Data approach.
+% Which method is the best
+While collaborative filtering, perhaps unsurprisingly, is able to 
+correctly predict the missing values in a matrix modeling the 
+reproducibility problem, the usual random sampling method cannot be 
+used in time-constrained processes. We proposed 6 sampling methods to 
+address this issue, and we found that one of them, RFNU, (\todo{check 
+that}) was consistently able to solve the problem. We explain that by 
+the fact that RFNU leads the training set to contain a balanced mix 
+between nearly complete and nearly empty columns, with a continuum of 
+intermediate configurations in between. On the contrary, other sampling 
+methods, including RFNT-L and RFNT-S, bias the sampling toward complete 
+or empty columns, which is sometimes detrimental to 
+accuracy.
 
-% Which sampling method is best
-
-% Interpreting the factors? Factors reflect the pipeline definition.
+% Training ratio
+On datasets that are strongly dependent on row bias, such as the real 
+datasets studied here, RFNU provides accuracy values that are 
+consistently higher than 0.95 for training ratios higher than 0.5, even 
+when biases are not included in the collaborative filtering 
+optimization. On the synthetic dataset, RFNU still performs very well 
+when biases are not included. However, the training ratio required to 
+reach a 0.95 accuracy increases with the number of subject types 
+present in the dataset. \todo{maybe find a relation between the 
+required training ratio and the number of subjects per subject type in 
+the entire dataset}.
 
 % How can this be used in practice
+From a practical standpoint, our study shows that reproducibility 
+evaluations can be conducted using only 50\% of the files produced by 
+the evaluated pipelines, with an accuracy above 95\%. Potentially, this 
+could reduce the computing time and storage required for such studies 
+by a factor of 2. However, such studies could not be conducted by 
+processing only half of the subjects entirely, which would correspond 
+to the Complete Columns sampling method. Instead, the processing of all 
+the subjects should be initiated, and it should be terminated in a random
+uniform way, assuming that files are uniformly produced throughout the 
+execution.
+
+% Generalizability
 
 % What are the limitations
+Our study could be extended by considering real-valued reproducibility 
+matrices instead of just binary ones. It is indeed common for file 
+differences to be quantified using specific similarity measures or 
+distances, such as Levenshtein distance between strings, or the sum of 
+squared distances between voxels of an image. Our sampling methods 
+could be directly applied to real-valued matrices, and we expect our 
+conclusions regarding the best-performing sampling method (RFNU) and 
+the inclusion of biases in the model to remain valid.
 
 % Real values, we expect the best sampling method to remain the same.
-
-\section{Conclusion}
-
-% Summary of the results and discussion. The take-home message.
-%%%%%% why there is a drop in ALS-RFNT-L with 60% ratio?
+We recommend not to include biases in the collaborative filtering optimization
+to solve this problem. Even though biases provide a slight accuracy improvement 
+when datasets are strongly biased (constant lines in the matrix), they can also
+be very detrimental for more complex datasets such as the syntetic one used here.
 

### 2018-07-23 paper.tex
A few corrections

@@
 
-\title{Predicting computational reproducibility of scientific pipelines using collaborative filtering}
+\title{Predicting computational reproducibility of scientific pipelines\\ using collaborative filtering}
 
@@
 computational reproducibility in scientific pipelines: the process is 
-the pipeline, it is hidden since we consider it as a black box (we 
+the evaluated pipeline, it is hidden since we consider the pipeline as a black box (we 
 don't inspect its source code), it is parametrized as it behaves 
@@
 filtering, inspired by previous examples that applied this method 
-outside of its initial application domain~\cite{feng2013efficient}. The 
-process is represented by a matrix where columns represent different 
-parametrizations and rows represent the files produced by the 
-execution. Parmeterizations may represent different input data sets or 
-parameter values, on which we do not assume an order. On the contrary, 
-an order is defined on the files, from their last modification time in 
-a sequential execution. We assume that files are produced in the same 
-order regardless of the parametrization, which is not always true, in 
-particular when pipelines are multi-threaded, but in general 
-reasonable \todo{explain "local" truth of this assumption}. This order imposes a constraint on the construction of the
-training set since files
-
-In this paper we investigate approximate methods to predict the
-reproducibility of a computational analysis from the first files that
-it produces. Our main intuition is that reproducibility errors are
-caused by a reduced number of factors that originate in the analysis
-pipeline and input data.
-
-% Other possible examples
-
-Seasonality of MS lesions.
-Thresholded stock values.
+outside of its initial application domain, for instance 
+~\cite{feng2013efficient}. The pipeline is represented by a matrix 
+where columns represent different parametrizations and rows represent 
+the files produced by the execution. Parmeterizations may represent 
+different input data sets or parameter values, on which we do not 
+assume an order. On the contrary, an order is defined on the files, 
+from their last modification time in a sequential execution. We assume 
+that files are produced in the same order regardless of the 
+parametrization, which is not always true, in particular when pipelines 
+are multi-threaded, but in general reasonable \todo{explain "local" 
+truth of this assumption}. This order imposes a constraint on the 
+construction of the training set since files
 
@@
 
-To evaluate the reproducibility of a pipeline, a retrieved matrix from 
-the subjects and file-ids is built. Subjects and file-ids are equivalent 
-to users and items, respectively, as they are known in Collaborative Filtering (CF) technique.
-Filling in the missing entries of this matrix encompasses some issues 
-which take some barriers for use of Collaborative filtering technique as it 
-has being used in e-commerce applications.
-For instance, files-ids (items) are produced in a specific order in the 
-pipeline however items are sequentially independent in general use of CF in e-commerce.
-This issue adds constraints on the selection of CF training set. Despite of random 
-selection strategy which does not taking care of item order, we had to come up with those 
-selection strategies that respect the pipeline fundamental fact about file order generation.  
-The aforementioned matrix (utility matrix), con be fully completed by processing all subjects 
-in pipeline however the whole processing can takes loads of time. This possibility of 
-having a potential complete populated matrix means despite of potential sparse matrices 
-in e-commerce case studies here the utility matrix is not sparse and 
-we can decide precisely which samples we need to select as our training set selection. 
-In this regard, to avoid the cold start issue we can take the first file-id of all 
-subjects in order to get sure that for all subjects there is at least one 
-selected element in training ratio and in the same way, all generated files 
-from the process of a random subject which can guarantee that all files 
-are presented in the selection set at least for once.
-
-what is specific to our problem compared to regular collaborative filtering:
+%~ To evaluate the reproducibility of a pipeline, a retrieved matrix from 
+%~ the subjects and file-ids is built. Subjects and file-ids are equivalent 
+%~ to users and items, respectively, as they are known in Collaborative Filtering (CF) technique.
+%~ Filling in the missing entries of this matrix encompasses some issues 
+%~ which take some barriers for use of Collaborative filtering technique as it 
+%~ has being used in e-commerce applications.
+%~ For instance, files-ids (items) are produced in a specific order in the 
+%~ pipeline however items are sequentially independent in general use of CF in e-commerce.
+%~ This issue adds constraints on the selection of CF training set. Despite of random 
+%~ selection strategy which does not taking care of item order, we had to come up with those 
+%~ selection strategies that respect the pipeline fundamental fact about file order generation.  
+%~ The aforementioned matrix (utility matrix), con be fully completed by processing all subjects 
+%~ in pipeline however the whole processing can takes loads of time. This possibility of 
+%~ having a potential complete populated matrix means despite of potential sparse matrices 
+%~ in e-commerce case studies here the utility matrix is not sparse and 
+%~ we can decide precisely which samples we need to select as our training set selection. 
+%~ In this regard, to avoid the cold start issue we can take the first file-id of all 
+%~ subjects in order to get sure that for all subjects there is at least one 
+%~ selected element in training ratio and in the same way, all generated files 
+%~ from the process of a random subject which can guarantee that all files 
+%~ are presented in the selection set at least for once. 
+%~ what is specific to our problem compared to regular collaborative filtering:
 %+ subjects are equivalent to users. Not all subjects have the same input data. Anatomical variability, acquisition variability (e.g., 1 subject may have multiple T1s).
@@
 Therefore we can take the first row and first column to avoid cold start issues.
+
+\subsection{Problem formulation}
 
@@
 
-\subsection{Sampling the training set}
+\subsection{Sampling of the training set}
 
@@
 when datasets are strongly biased (constant lines in the matrix), they can also
-be very detrimental for more complex datasets such as the syntetic one used here.
+be very detrimental for more complex datasets such as the synthetic one used here.
+
+% Other possible examples
+The method described in this paper and applied to reproducibility 
+studies could be used to predict the outcome of other deterministic, 
+hidden, parameterized, time-dependent processes, for instance markers 
+of chronicle disease activity.
+
+\todo{Discussion on points that are not part of constant lines.}
+
+\todo{Show an overlap to see where the error is located.}
+
+RFNTS and RFNTL could be used when the matrix is more  uncertain at the beginning or end of the pipeline.
+
+RS and RFNU tends to become the same for high training ratios.
 
@@
 
+We thank Compute Canada for providing the compute and storage resources
+required for this study.
+
 \bibliographystyle{IEEEtran}

### 2018-07-24 paper.tex
Worked on abstract, introduction, and problem formulation

@@
 
-\title{Predicting computational reproducibility of scientific pipelines\\ using collaborative filtering}
+\title{Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering}
 
@@
 \begin{abstract}
+With the rise of the reproducibility crisis in several scientific 
+domains, evaluating the computational reproducibility of data analysis 
+pipelines has become a critical issue. It is, however, a cumbersome 
+process for analyses that involve data from large populations of 
+subjects, due to the computational and storage requirements. 
+Nevertheless, executions of a given analysis pipeline are not 
+independent, as they are obtained from the same program. We leverage 
+this observation to propose a method to predict the computational 
+reproducibility of data analysis pipelines in large population studies. 
+We formulate the problem as a collaborative filtering problem with 
+constraints on the construction of the training set. We propose 6 
+different strategies to build the training set and evaluate them on 2 
+datasets, a synthetic one modeling a population with a growing number 
+of subject types, and a real one obtained on neuroinformatics 
+pipelines. Results show that one sampling method, ``Random File Numbers 
+(Uniform)" is able to predict computational reproducibility in 
+pipelines with a good accuracy. We also analyze the relevance of 
+including file and subject biases in the collaborative filtering model. 
+We conclude that the proposed method is able to speed-up reproducibility 
+evaluations substantially, with a reduced accuracy loss.
 \end{abstract}
@@
 computational reproducibility, infrastructural characteristics such as 
-the operating system play an important role. In neurosciences, our 
+the operating system or multithreading play an important role. In neuroinformatics, our 
 primary field of interest, several studies have shown the effect of the 
@@
 However, conducting such reproducibility studies at scale is cumbersome 
-due to the execution time of data analysis pipelines, which easily 
-exceeds a few hours.
+due to the computational and storage requirements of data analysis pipelines.
 
-We consider the problem of predicting the values of a variable 
-controlled by a hidden, parameterized, time-dependent, deterministic 
-process. We assume that the variable values are observed only for a 
-limited number of time points and process parameters, and we aim at 
-predicting the values for the remaining time points and parameters.
+Neuroinformatics pipelines are generally iterated on data coming from 10 to 
+1,000 subjects, possibly with subtle input parameter variations to 
+adjust specific data acquisition conditions. Subject data often capture 
+anatomical and functional characteristics of their brain, for instance through
+Magnetic Resonance Imaging (MRI) and Electroencephalography (EEG). The number of files 
+associated with a subject may vary, and these files may also be of 
+different sizes. Typical data processing times range from 15 minutes to 
+15 hours, with input ranging from 100~MB to 15~GB per subject, and 
+outputs ranging from 1~GB to 500~GB. Such variations impact the 
+reproducibility of a given pipeline across subjects.
 
-This problem description maps directly to the evaluation of 
-computational reproducibility in scientific pipelines: the process is 
-the evaluated pipeline, it is hidden since we consider the pipeline as a black box (we 
-don't inspect its source code), it is parametrized as it behaves 
-differently on different input datasets and parameters, it is 
-time-dependent as the value of the variable of interest varies 
-throughout the course of the pipeline execution. The variable of 
-interest is whether the pipeline outputs, most likely the files it 
-produces, are identical between execution conditions.
-
+Our goal is to predict the outcome of reproducibility evaluations in a 
+large population of subject from a reduced set of pipeline executions. 
+More precisely, we aim at predicting whether a particular file produced 
+by an analysis pipeline will be identical across execution conditions, or if it will contain reproducibility \emph{errors}. 
 We approach the problem from the point of view of collaborative 
@@
 outside of its initial application domain, for instance 
-~\cite{feng2013efficient}. The pipeline is represented by a matrix 
-where columns represent different parametrizations and rows represent 
-the files produced by the execution. Parmeterizations may represent 
-different input data sets or parameter values, on which we do not 
-assume an order. On the contrary, an order is defined on the files, 
-from their last modification time in a sequential execution. We assume 
-that files are produced in the same order regardless of the 
-parametrization, which is not always true, in particular when pipelines 
-are multi-threaded, but in general reasonable \todo{explain "local" 
-truth of this assumption}. This order imposes a constraint on the 
-construction of the training set since files
-
-% Scientific data analysis pipeline executions are long (give examples
-% from neuroimaging).
-
-% Define subjects, pipelines.
-
-\todo{Explain that columns represent subjects and rows represent files, and that these terms are used
-indifferently}
-
-\todo{Mention why this is Big Data}
-
-\todo{Define reproducibility \emph{errors}}
-
-\todo{talk about time-constrained processes}
+~\cite{feng2013efficient}.
 
@@
 \end{enumerate}
+The paper ends with a discussion about \todo{x} and a conclusion.
 
@@
 
-%~ To evaluate the reproducibility of a pipeline, a retrieved matrix from 
-%~ the subjects and file-ids is built. Subjects and file-ids are equivalent 
-%~ to users and items, respectively, as they are known in Collaborative Filtering (CF) technique.
-%~ Filling in the missing entries of this matrix encompasses some issues 
-%~ which take some barriers for use of Collaborative filtering technique as it 
-%~ has being used in e-commerce applications.
-%~ For instance, files-ids (items) are produced in a specific order in the 
-%~ pipeline however items are sequentially independent in general use of CF in e-commerce.
-%~ This issue adds constraints on the selection of CF training set. Despite of random 
-%~ selection strategy which does not taking care of item order, we had to come up with those 
-%~ selection strategies that respect the pipeline fundamental fact about file order generation.  
-%~ The aforementioned matrix (utility matrix), con be fully completed by processing all subjects 
-%~ in pipeline however the whole processing can takes loads of time. This possibility of 
-%~ having a potential complete populated matrix means despite of potential sparse matrices 
-%~ in e-commerce case studies here the utility matrix is not sparse and 
-%~ we can decide precisely which samples we need to select as our training set selection. 
-%~ In this regard, to avoid the cold start issue we can take the first file-id of all 
-%~ subjects in order to get sure that for all subjects there is at least one 
-%~ selected element in training ratio and in the same way, all generated files 
-%~ from the process of a random subject which can guarantee that all files 
-%~ are presented in the selection set at least for once. 
-%~ what is specific to our problem compared to regular collaborative filtering:
-%+ subjects are equivalent to users. Not all subjects have the same input data. Anatomical variability, acquisition variability (e.g., 1 subject may have multiple T1s).
-%+ files are produced in a specific order (movies aren't),
-% which add constraints on the training set (cannot sample late files and not early ones).
-%+ utility matrix is not sparse: we can potentially populate it completely.
-Which means that we can decide precisely which samples we need (active sampling).
-Therefore we can take the first row and first column to avoid cold start issues.
-
 \subsection{Problem formulation}
 
-\todo{Restrict to binary classification}
+The pipeline to be evaluated is represented by a matrix $U$ of size $N_f \times N_s$
+where columns represent data coming from different subjects and rows represent 
+the files produced by the pipeline execution. Subjects are unordered, 
+i.e., columns may be reordered arbitrarily, but files are ordered, for 
+instance from their last modification time in a sequential execution, 
+and we assume that this order is consistent across subjects. $U_{i, j}$ 
+represents the 
+reproducibility of file $i$ produced during the processing of subject 
+$j$ in two conditions, for instance two different operating systems. In our 
+experiments, we restrict $U_{i,j}$ to be boolean, but the same prediction method
+can be applied for real values.
+
+Our goal is to predict the test set $\mathbb{T'}$ of missing values of 
+$U$ from a training subset $\mathbb{T}$ of known ones. In contrast with the traditional collaborative filtering 
+problem, (1) we have control over the construction of the training set, and (2)
+the construction of the training set is constrained by the order on the matrix rows, which is formalized as follows: 
+\begin{equation}
+\begin{array}{l}
+\forall (i, j, k) \in \llbracket 1, N_f \rrbracket \times \llbracket 1, N_f \rrbracket \times \llbracket 1, N_s \rrbracket, \\
+ \left( U_{i,k} \in \mathbb{T} \quad \mathrm{and} \quad U_{j,k} \in \mathbb{T'} \right) \Rightarrow i < j. \label{eq:time}
+ \end{array}
+\end{equation}
+
+Our problem is the following:
+\begin{quote}
+Given a training ratio $\alpha$, find a subset $\mathbb{T}$ of 
+$\{U_{i,j}\}$ of size $\alpha N_f N_s$ such that (1) $\mathbb{T}$ and 
+$\mathbb{T'}$ respect Equation~\ref{eq:time}, and (2) $\mathbb{T'}$ can 
+be predicted from $\mathbb{T}$ with high accuracy.
+\end{quote}
+The sampling of the training set will be described in Section~\ref{sec:training}.
+The collaborative filtering techniques used for the predictions are reported hereafter.
 
@@
 Collaborative filtering is a technique to predict unknown values of a 
-matrix called ``utility matrix" from the known ones. Traditionally, the 
+matrix called "utility matrix" from the known ones. Traditionally, the 
 matrix represents the ratings of items, represented in columns, by 
@@
 overview of collaborative filtering is provided 
-in~\cite{leskovec2014mining}.
+in~\cite{leskovec2014mining}. In our context, the utility matrix is the
+pipeline matrix described previously.
 
@@
 In the remainder of this paper, we use matrix factorization as implemented in 
-Apache Spark's MLLib version 2.~\todo{xxx.}, which uses ALS.
+Apache Spark's MLLib version 2.3.0, which uses ALS.
 
@@
 \subsection{Sampling of the training set}
-
+\label{sec:training}
 As explained before, the training set in our problem cannot be 
@@
 
+We consider the problem of predicting the values of a variable 
+controlled by a hidden, parameterized, time-dependent, deterministic 
+process. We assume that the variable values are observed only for a 
+limited number of time points and process parameters, and we aim at 
+predicting the values for the remaining time points and parameters.
+
+This problem description maps directly to the evaluation of 
+computational reproducibility in scientific pipelines: the process is 
+the evaluated pipeline, it is hidden since we consider the pipeline as a black box (we 
+don't inspect its source code), it is parametrized as it behaves 
+differently on different input datasets and parameters, it is 
+time-dependent as the value of the variable of interest varies 
+throughout the course of the pipeline execution. The variable of 
+interest is whether the pipeline outputs, most likely the files it 
+produces, are identical between execution conditions.
+
 \todo{Discussion on points that are not part of constant lines.}

### 2018-07-24 paper.tex
Added missing files, generated figures from updated data, various corrections until section V

@@
 process for analyses that involve data from large populations of 
-subjects, due to the computational and storage requirements. 
-Nevertheless, executions of a given analysis pipeline are not 
-independent, as they are obtained from the same program. We leverage 
-this observation to propose a method to predict the computational 
+subjects, due to their computational and storage requirements. 
+We present a method to predict the computational 
 reproducibility of data analysis pipelines in large population studies. 
-We formulate the problem as a collaborative filtering problem with 
+We formulate the problem as collaborative filtering, with 
 constraints on the construction of the training set. We propose 6 
-different strategies to build the training set and evaluate them on 2 
+different strategies to build the training set, and we evaluate them on 2 
 datasets, a synthetic one modeling a population with a growing number 
-of subject types, and a real one obtained on neuroinformatics 
+of subject types, and a real one obtained with neuroinformatics 
 pipelines. Results show that one sampling method, ``Random File Numbers 
@@
 Our goal is to predict the outcome of reproducibility evaluations in a 
-large population of subject from a reduced set of pipeline executions. 
-More precisely, we aim at predicting whether a particular file produced 
-by an analysis pipeline will be identical across execution conditions, or if it will contain reproducibility \emph{errors}. 
-We approach the problem from the point of view of collaborative 
-filtering, inspired by previous examples that applied this method 
-outside of its initial application domain, for instance 
-~\cite{feng2013efficient}.
+large population of subjects, from a reduced set of pipeline 
+executions. More precisely, we aim at predicting whether a particular 
+file produced by an analysis pipeline will be identical across 
+execution conditions, or if it will contain reproducibility 
+\emph{errors}. We approach the problem from the point of view of 
+collaborative filtering, inspired by previous examples that applied 
+this method outside of its initial application domain, for instance 
+~\cite{feng2013efficient}. The main issue, and originality, of our 
+problem lies in the fact that the training set cannot be arbitrarily 
+sampled from the utility matrix. Instead, the training set has to 
+respect the time constraints that stem from the order in which files 
+are produced during pipeline executions.
 
-The paper makes the following contributions:
+This paper makes the following contributions:
 \begin{enumerate}
@@
 \end{enumerate}
+The problem formulation, collaborative filtering technique used, and 
+proposed sampling strategies for the training set are presented in 
+Section~\ref{sec:methods}. The datasets are described in 
+Section~\ref{sec:datasets}, and experimental results are reported in 
+Section~\ref{sec:results}.
 The paper ends with a discussion about \todo{x} and a conclusion.
 
+\todo{Complete the introduction and improve the writing}
+
+\newpage
+
 \section{Method}
-
+\label{sec:methods}
 \subsection{Problem formulation}
 
-The pipeline to be evaluated is represented by a matrix $U$ of size $N_f \times N_s$
-where columns represent data coming from different subjects and rows represent 
-the files produced by the pipeline execution. Subjects are unordered, 
-i.e., columns may be reordered arbitrarily, but files are ordered, for 
-instance from their last modification time in a sequential execution, 
-and we assume that this order is consistent across subjects. $U_{i, j}$ 
-represents the 
-reproducibility of file $i$ produced during the processing of subject 
-$j$ in two conditions, for instance two different operating systems. In our 
-experiments, we restrict $U_{i,j}$ to be boolean, but the same prediction method
-can be applied for real values.
+The pipeline to be evaluated is represented by a matrix $U$ of size 
+$N_f \times N_s$ where the $N_s$ columns represent data coming from 
+different subjects and the $N_f$ rows represent the files produced by 
+the pipeline execution. While subjects are not ordered, files are, for 
+instance from their last modification time in a sequential execution. 
+We assume that the order on files is consistent across subjects. $U_{i, 
+j}$ measures the reproducibility of file $i$ produced during the 
+processing of subject $j$ in two conditions, for instance two different 
+operating systems. In our experiments, we restrict $U_{i,j}$ to be 
+boolean, but our methods can be applied for real values as well.
 
 Our goal is to predict the test set $\mathbb{T'}$ of missing values of 
-$U$ from a training subset $\mathbb{T}$ of known ones. In contrast with the traditional collaborative filtering 
-problem, (1) we have control over the construction of the training set, and (2)
-the construction of the training set is constrained by the order on the matrix rows, which is formalized as follows: 
+$U$ from a training set $\mathbb{T}$ of known ones, where $\mathbb{T} 
+\cap \mathbb{T'} = \emptyset$ and $\mathbb{T} \cup \mathbb{T'} = 
+\{U_{i,j}\}$. In contrast with the traditional collaborative filtering 
+problem, (1) we have control over the construction of the training set, 
+for instance we can choose to include only files producde by specific 
+subjects, or the first files produced by the processing of every 
+subject, and (2) the construction of the training set is constrained by 
+the 
+order on the matrix rows, which is formalized as follows: 
 \begin{equation}
@@
 in~\cite{leskovec2014mining}. In our context, the utility matrix is the
-pipeline matrix described previously.
+pipeline matrix $U$ described previously.
 
@@
 
-A third class of methods, which is the one we will apply to our 
+A third class of methods, which is the one that we will apply to our 
 problem, is based on the factorization of the utility matrix to 
@@
 
-Two good techniques to perform the optimization are stochastic gradient descent and alternating least squares (ALS). 
-In the remainder of this paper, we use matrix factorization as implemented in 
-Apache Spark's MLLib version 2.3.0, which uses ALS.
-
-% Explain our particular context.
-% What our matrix represents
-% Explain that you have binary classes (rounding)
-% Explain the sampling issue.
+Two good techniques to perform the optimization are stochastic gradient 
+descent and alternating least squares (ALS). In the remainder of this 
+paper, we use matrix factorization as implemented in Apache Spark's 
+MLLib version 2.3.0, which uses ALS. We round predictions to the 
+nearest integer to obtain binary values.
 
 \subsection{Sampling of the training set}
+
 \label{sec:training}
+
 As explained before, the training set in our problem cannot be 
-constructed by unconstrained random sampling of the matrix.
-To address this issue, we investigated the following sampling techniques.
+constructed by unconstrained random sampling of the matrix. Instead, 
+the training and test sets have to comply to Equation~\ref{eq:time}. To 
+address this issue, we investigated the following sampling techniques, illustrated in
+Figure~\ref{fig:sampling}.
 
-% 2. columns
-\paragraph{Complete Columns (Figure~\ref{fig:Columns-Sample-Training-set})}
-The training set is sampled by randomly selecting complete columns in
-the matrix, that is, complete subject executions. The last selected
-column might be incomplete to meet the exact training ratio. This 
-method is realistic: it corresponds to a situation where the 
-collaborative filtering method will predict the reproducibility in the 
-remaining subjects from the subjects in the training set.
+\paragraph{Complete Columns 
+(Figure~\ref{fig:Columns-Sample-Training-set})} The training set is 
+sampled by randomly selecting complete columns in the utility matrix, 
+that is, complete subject executions. The last selected column might be 
+incomplete to meet the exact training ratio. This method respects the 
+time constraints. It corresponds to a situation where the collaborative 
+filtering method will predict the reproducibility of the subjects in 
+the test set from the subjects in the training set.
 
-% 3. rows
-\paragraph{Complete Rows (Figure~\ref{fig:Rows-Sample-Training-set})} The training set is sampled by selecting complete 
-rows in the matrix, that is, the first files produced by
-every execution. The last selected row might be incomplete to meet the
-exact training ratio. This method is realistic: it corresponds to a 
-situation where the processing of all the subjects is launched and 
-interrupted before the execution is complete. The collaborative 
-filtering method will then predict the reproducibility of the remaining 
-files.
+\paragraph{Complete Rows (Figure~\ref{fig:Rows-Sample-Training-set})} 
+The training set is sampled by selecting complete rows in the utility 
+matrix, that is, the first files produced by every execution. The last 
+selected row might be incomplete to meet the exact training ratio. This 
+method respects the time constraints. It corresponds to a situation 
+where the processing of all the subjects is launched and interrupted 
+before the execution is complete. The collaborative filtering method 
+will then predict the reproducibility of the remaining files.
 
@@
                   \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
-                  \caption{RFNT-L}
+                  \caption{RFNTL}
                   \label{fig:triangular-L-Sample-Training-set}
@@
                   \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
-                  \caption{RFNT-S}
+                  \caption{RFNTS}
                   \label{fig:triangular-S-Sample-Training-set}
@@
         \caption{Sample training set for different methods with a training ratio of 0.4.}
+        \label{fig:sampling}
 \end{figure}
 
-\paragraph{Random Subjects -- RS (Figure~\ref{fig:Uniform-S-Sample-Training-set})} This method builds the 
-training set by selecting the files from random subjects 
-until the training ratio is reached. The file selected in a 
-subject is the file with the lowest index in this subject that has not 
-been already selected in the training set. This method is realistic as 
-files are sampled according to their production time-stamps.
+\paragraph{Random Subjects -- RS 
+(Figure~\ref{fig:Uniform-S-Sample-Training-set})} This method builds 
+the training set by selecting the files from random subjects until the 
+training ratio is reached. The file selected in a subject is the file 
+with the lowest index in this subject that has not been already 
+selected in the training set. This respects the time constraints as files are 
+sampled according to their production time-stamps.
 
@@
 \]
- For $\alpha > 0.5$, this ensures that the average number of files in 
- the training set is $\alpha N_f$. For $\alpha \leq 0.5$, the number of 
- files selected in every subject is sampled from $U(0,N_f)$ with 
- probability $2\alpha$, and set to 0 otherwise.
-RFNU is realistic as files are sampled according to their production time-stamps.
-Due to sampling issues, it is possible that the actual training ratio obtained with this method
-does not match the target one. We check that the difference between the target and real training ratios
-was lower than 0.01.\\
+ For $\alpha \leq 0.5$, we ensure that the average number of selected 
+ files by subject is $\alpha N_f$ by sampling the number of 
+ files selected in every subject from $U(0,N_f)$ with 
+ probability $2\alpha$, and setting it to 0 otherwise. For $\alpha > 
+ 0.5$, this is ensured by the value used for $a$, which leads the 
+ average of U(a, b) to be $\alpha N_f$.
 
@@
 \textit{a} and \textit{b} with two approaches that ensure that the 
-average of the distribution is $\alpha N_{f}$ ($\alpha$ is the training 
-ratio):
+average of the distribution is $\alpha N_{f}$:
 \begin{enumerate}
-        \item Largest a (RFNT-L, Figure~\ref{fig:triangular-L-Sample-Training-set}): a is set to the 
+        \item Largest a (RFNTL, Figure~\ref{fig:triangular-L-Sample-Training-set}): a is set to the 
         largest possible value, i.e., b. The average of the 
@@
         number of files in every subject is sampled from $T(0, 0, N_f)$ 
-        with probability $3\alpha$ and set to 0 otherwise, to ensure that the average number of files
-        in the training set is $\alpha N_f$.
-        \item Smallest a (RFNT-S, Figure~\ref{fig:triangular-S-Sample-Training-set}): a is 
+        with probability $3\alpha$ and set to 0 otherwise, to ensure 
+        that the average number of files by subject in the training set 
+        is $\alpha N_f$.
+        \item Smallest a (RFNTS, Figure~\ref{fig:triangular-S-Sample-Training-set}): a is 
         set to the smallest possible value, i.e., 0. The average of the 
@@
         selected in every subject is sampled from $T(0, 0, N_f)$ with 
-        probability $3\alpha$ and set to 0 otherwise, as in RFNT-L. 
+        probability $3\alpha$ and set to 0 otherwise, as in RFNTL. 
         When $\alpha \geq 2/3$, we set $b=N_f$ and the number of files 
@@
         probability $3(1-\alpha)$ and set to $N_f$ otherwise, still to 
-        ensure that the average number of files in the training set is 
+        ensure that the average number of files by subject in the training set is 
         $\alpha N_f$.
@@
 and~\ref{fig:triangular-S-Sample-Training-set}, the motivation for the 
-RFNT-L method is to guarantee that, for large enough values of 
+RFNTL method is to guarantee that, for large enough values of 
 $\alpha$, all subjects will have at least a few files in the training 
-set, which is not the case for RFNU.
+set, which is not the case for RFNU or RFNTS.
 \begin{figure}
@@
 
-% 0. random unreal (baseline)
-\paragraph{Random Unreal (Figure ~\ref{fig:Random-Unreal-Sample-Training-set})}
-The training set is sampled in a random uniform way, 
-regardless of the file generation times. This method will be used as a
-baseline for comparison with other methods, although it is not
-realistic.
+\paragraph{Random Unreal (Figure 
+~\ref{fig:Random-Unreal-Sample-Training-set})} The training set is 
+sampled in a random uniform way, regardless of the file generation 
+times. This method does not respect the time constraints in 
+Equation~\ref{eq:time}, it will be used as a baseline for comparison 
+with other methods.
 
@@
 
-\section{Dataset}
+\section{Datasets}
+
+\label{sec:datasets}
 
@@
 subjects of different \emph{types}. Subjects of the same type behave 
-identically and all types contain the same number of subjects $\pm$ 1 
-\todo{Soudabeh: check that}. Such a decomposition by subject type 
-correspond to the case where different subjects may have data of 
-different nature, as it is for instance the case in the neuroimaging 
+identically and all types contain the same number of subjects $\pm$ 1. 
+Such a decomposition by subject type correspond to the case where 
+different subjects may have data of different nature, as it is for 
+instance the case in the neuroimaging 
 dataset of the Human Connectome Project~\cite{van2013wu} where not all the 
@@
 
-For subjects of a given type, matrix elements vary in $log(n)$  blocks,         
-where $n$ is the number of types, with all the possible variation 
-patterns: some types do not vary at all, while other ones vary in every 
-block. Such variation patterns are meant to mimic the logic of data 
+ For subjects of a given type, the reproducibility matrix consists of 
+ $log(n)$  blocks, where $n$ is the number of types. Blocks are 
+ arranged with all the possible variation patterns: some types do not 
+ vary at all, while other ones vary in every block. Such variation 
+ patterns are meant to mimic the logic of data 
 processing pipelines: each block of files represents the files produced 
@@
         \end{subfigure}
-\caption{Synthetic Data}
+\caption{Synthetic reproducibility matrices. White cells denote reproducibility errors.}
 \label{fig:synthetic-data}
@@
 processed a set S of 94 subjects randomly selected in the S500 HCP
-release~\todo{URL} in three execution conditions with different
-versions of the CentOS operating system (5.?, 6.? and 7.?), using the
-PreFreesurfer and Freesurfer pipelines
-described in~\cite{glasser2013minimal} and available at \todo{URL}. For
-each pipeline, we identified the set F of files produced for all
+release\footnote{\url{https://db.humanconnectome.org}} in three execution conditions with different
+versions of the CentOS operating system (5.\todo{?}, 6.8 and 7.2), using the
+PreFreesurfer and Freesurfer pipelines described 
+in~\cite{glasser2013minimal} and available on 
+GitHub\footnote{\url{https://github.com/Washington-University/Pipelines/releases/tag/v3.19.0}}. 
+For each pipeline, we identified the set F of files produced for all
 subjects in all conditions. For each condition pair and each pipeline, 
-we computed a binary difference matrix D of size $|F|\times|S|$, where $D_{i,j}$ is true
-if file $i$ of subject $j$ was different in each condition. Rows of
-$M$ are ordered by ascending file modification time in the pipeline.
+we computed a binary reproducibility matrix U of size $|F|\times|S|$, 
+where $U_{i,j}$ is true iif file $i$ of subject $j$ was different in 
+each condition. Rows of $U$ were ordered by ascending file modification 
+time in a random subject in S.
 
@@
 
-Three experiments have been conducted for each dataset to evaluate the performance of our 
-predictions using (1) ALS without biases, (2) ALS with biases, (3) Biases only. 
-Results will be evaluated using accuracy, sensitivity and specificity defined as follows:
-\[
-        Accuracy = \frac{TP+TN}{TP+TN+FP+FN}
-\]
-\[
-        Sensitivity = \frac{TP}{TP+FN}
-\]
-\[
-        Specificity = \frac{TN}{TN+FP}
-\]
-Where TP is the number of True Positives (correctly predicted reproducibility errors), 
-FP is the number of False Positives, TN is the number of true negatives 
-and FN is the number of false negatives. \todo{Check if we want to report sensitivity and specificity, otherwise remove.}
+\label{sec:results}
 
-We compare our sampling methods to (1) a dummy classifier that always 
+Two experiments have been conducted for each reproducibility matrix, to evaluate the performance of our 
+predictions using (1) ALS without biases, and (2) ALS with biases. 
+Results will be evaluated using classification accuracy and compared to (1) a dummy classifier that always 
 predicts the value in the majority class and (2) the Random Unreal 
 method, used as the baseline sampling technique. All reported values are averages
-over 5 repetitions. \todo{Report model parameters, including number of factors.}
+over 5 repetitions. \todo{Report model parameters, including number of 
+factors.} Due to sampling issues, it is possible that the actual 
+training ratio obtained with some of the sampling methods does not 
+match the target one. We checked that the difference between the target 
+and real training ratios was lower than 0.01. We used Spark's ALS model 
+as available in package \texttt{pyspark.ml}, with 50 factors, a 
+regularization parameter of 0.01, a maximum of 5 iterations and non 
+negative constraints set to true.
+
+%~ , sensitivity and specificity defined as follows:
+%~ \[
+        %~ Accuracy = \frac{TP+TN}{TP+TN+FP+FN}
+%~ \]
+%~ \[
+        %~ Sensitivity = \frac{TP}{TP+FN}
+%~ \]
+%~ \[
+        %~ Specificity = \frac{TN}{TN+FP}
+%~ \]
+%~ Where TP is the number of True Positives (correctly predicted reproducibility errors), 
+%~ FP is the number of False Positives, TN is the number of true negatives 
+%~ and FN is the number of false negatives. \todo{Check if we want to report sensitivity and specificity, otherwise remove.}
 
@@
 reported in Figure~\ref{fig:results-synthetic}. By construction, the 
-accuracy of the dummy classifier is 0.5 for all subject types. Random 
+accuracy of the dummy classifier is close to 0.5 for all subject types. Random 
 Unreal performs very well for all subject types, which confirms that 
@@
 
-Results of ALS with bias are reported in Figure~\ref{fig:results-synthetic-als-bias}.
-RS, RFNU and RFNTL remain the methods that best compare to Random Unreal, but the achieved
-accuracy is much lower than without Biases. This is due to the fact that biases \ldots \todo{finish that.}
+Results of ALS with bias are reported in 
+Figure~\ref{fig:results-synthetic-als-bias}. RS, RFNU and RFNTL remain 
+the methods that best compare to Random Unreal, but the achieved 
+accuracy is much lower than without Biases. This is presumably due to 
+the fact that file biases are all close to 0.5 in the synthetic data. 
+In such a situation, biases are detrimental to the accuracy of the 
+collaborative filtering process and shouldn't be included.
 
@@
 RFNTL and RFNTS also perform well for a training ratio lower than 0.5. 
-Overall, the accuracy of the methods is much higher than without bias: 
-the file bias is very strong in this dataset, as illustrated by the large number
-of constant lines in the matrices in Figure~\ref{fig:utility-matrices}.
+Overall, the accuracy of the methods is much higher than without bias. 
+This is because the file bias is very strong in this dataset, as 
+illustrated by the large number of constant lines in the matrices in 
+Figure~\ref{fig:utility-matrices}.
 
@@
 used in time-constrained processes. We proposed 6 sampling methods to 
-address this issue, and we found that one of them, RFNU, (\todo{check 
-that}) was consistently able to solve the problem. We explain that by 
+address this issue, and we found that one of them, RFNU, \todo{check 
+that} is consistently able to solve the problem. We explain that by 
 the fact that RFNU leads the training set to contain a balanced mix 
@@
 intermediate configurations in between. On the contrary, other sampling 
-methods, including RFNT-L and RFNT-S, bias the sampling toward complete 
+methods, including RFNTL and RFNTS, bias the sampling toward complete 
 or empty columns, which is sometimes detrimental to 
@@
 required training ratio and the number of subjects per subject type in 
-the entire dataset}.
+the entire dataset}
 

### 2018-07-24 paper.tex
Minor fix

@@
 method, used as the baseline sampling technique. All reported values are averages
-over 5 repetitions. \todo{Report model parameters, including number of 
-factors.} Due to sampling issues, it is possible that the actual 
+over 5 repetitions. Due to sampling issues, it is possible that the actual 
 training ratio obtained with some of the sampling methods does not 

### 2018-07-25 paper.tex
Updates in introduction and II.A

@@
 \begin{abstract}
-With the rise of the reproducibility crisis in several scientific 
-domains, evaluating the computational reproducibility of data analysis 
-pipelines has become a critical issue. It is, however, a cumbersome 
+With the rise of the reproducibility crisis, evaluating the 
+computational reproducibility of data analysis pipelines has become a 
+critical issue. It is, however, a cumbersome 
 process for analyses that involve data from large populations of 
@@
 reproducibility of data analysis pipelines in large population studies. 
-We formulate the problem as collaborative filtering, with 
+We formulate the problem as a collaborative filtering process, with 
 constraints on the construction of the training set. We propose 6 
-different strategies to build the training set, and we evaluate them on 2 
+different strategies to build the training set, which we evaluate on 2 
 datasets, a synthetic one modeling a population with a growing number 
@@
 pipelines. Results show that one sampling method, ``Random File Numbers 
-(Uniform)" is able to predict computational reproducibility in 
-pipelines with a good accuracy. We also analyze the relevance of 
-including file and subject biases in the collaborative filtering model. 
-We conclude that the proposed method is able to speed-up reproducibility 
+(Uniform)" is able to predict computational reproducibility with a good 
+accuracy. We also analyze the relevance of including file and subject 
+biases in the collaborative filtering model. We conclude that the 
+proposed method is able to speed-up reproducibility 
 evaluations substantially, with a reduced accuracy loss.
@@
 
-Computational reproducibility, the property through which
-computational results can be recomputed over time and
-space~\cite{peng2011reproducible}, has become a critical component of scientific
-methodology with the rise of the reproducibility crisis in several 
-domains~\cite{baker2016there}. Among the factors hampering 
-computational reproducibility, infrastructural characteristics such as 
-the operating system or multithreading play an important role. In neuroinformatics, our 
-primary field of interest, several studies have shown the effect of the 
+Computational reproducibility, the ability to recompute data analyses 
+over time and 
+space~\cite{peng2011reproducible}, has become a critical component of 
+scientific methodology as many researchers acknowledge the existence of 
+a reproducibility crisis~\cite{baker2016there}. Among other factors, 
+such as data and code sharing, infrastructural characteristics 
+play an important role in making experiments reproducible. For instance, in 
+neuroinformatics, our primary field of interest, several studies have 
+shown the effect of the 
 operating system on computational 
@@
 However, conducting such reproducibility studies at scale is cumbersome 
-due to the computational and storage requirements of data analysis pipelines.
+due to the computational and storage requirements of data analysis 
+pipelines.
 
@@
 anatomical and functional characteristics of their brain, for instance through
-Magnetic Resonance Imaging (MRI) and Electroencephalography (EEG). The number of files 
+Magnetic Resonance Imaging (MRI) or Electroencephalography (EEG). The number of files 
 associated with a subject may vary, and these files may also be of 
 different sizes. Typical data processing times range from 15 minutes to 
-15 hours, with input ranging from 100~MB to 15~GB per subject, and 
-outputs ranging from 1~GB to 500~GB. Such variations impact the 
-reproducibility of a given pipeline across subjects.
+15 hours per subject, with input ranging from 100~MB to 15~GB per subject, and 
+outputs ranging from 1~GB to 500~GB.
+
+The reproducibility of a given pipeline may vary across subjects, for 
+instance due to different pipeline branches being executed depending on 
+the nature, cardinality or content of the input data. For instance, in 
+the public database released by the Human Connectome 
+Project~\cite{van2013wu}, subjects may have one or two anatomical images of 
+each modality; when two images are 
+present, they are aligned together and averaged. The presence of 
+artifacts, for instance due to high motion during the acquisition, may 
+also trigger corrections that are not otherwise required. Some branches 
+of the pipeline may also be executed only for specific acquisition 
+parameters, for instance the intensity of the magnetic field. To 
+capture all these variations, reproducibility evaluations need to be 
+conducted on many subjects, which is unwieldy.
 
@@
 sampled from the utility matrix. Instead, the training set has to 
-respect the time constraints that stem from the order in which files 
+respect the time constraints imposed by the order in which files 
 are produced during pipeline executions.
@@
 Section~\ref{sec:results}.
-The paper ends with a discussion about \todo{x} and a conclusion.
-
-\todo{Complete the introduction and improve the writing}
-
-\newpage
+The paper ends with a discussion about the impact, limitations and 
+generalizability of our results.
 
@@
 The pipeline to be evaluated is represented by a matrix $U$ of size 
-$N_f \times N_s$ where the $N_s$ columns represent data coming from 
-different subjects and the $N_f$ rows represent the files produced by 
+$N_f \times N_s$, where the $N_s$ columns represent data coming from 
+different subjects, and the $N_f$ rows represent the files produced by 
 the pipeline execution. While subjects are not ordered, files are, for 
-instance from their last modification time in a sequential execution. 
-We assume that the order on files is consistent across subjects. $U_{i, 
-j}$ measures the reproducibility of file $i$ produced during the 
-processing of subject $j$ in two conditions, for instance two different 
+instance from their last modification time in a sequential execution, 
+and we assume that this order is consistent across subjects. $U_{i, j}$ 
+measures the reproducibility of file $i$ produced during the processing 
+of subject $j$ in two conditions, for instance two different 
 operating systems. In our experiments, we restrict $U_{i,j}$ to be 
@@
 Collaborative filtering is a technique to predict unknown values of a 
-matrix called "utility matrix" from the known ones. Traditionally, the 
+matrix called ``utility matrix" from the known ones. Traditionally, the 
 matrix represents the ratings of items, represented in columns, by 
@@
 
+In any case, we recommend not to include biases in the collaborative filtering 
+optimization to solve this problem. Even though biases provide a slight 
+accuracy improvement when datasets are strongly biased (constant lines 
+in the matrix), they can also be very detrimental for more complex 
+datasets such as the synthetic one used here.
+
 % How can this be used in practice
@@
 
-% Generalizability
-
 % What are the limitations
@@
 
-% Real values, we expect the best sampling method to remain the same.
-We recommend not to include biases in the collaborative filtering optimization
-to solve this problem. Even though biases provide a slight accuracy improvement 
-when datasets are strongly biased (constant lines in the matrix), they can also
-be very detrimental for more complex datasets such as the synthetic one used here.
-
 % Other possible examples
 The method described in this paper and applied to reproducibility 
-studies could be used to predict the outcome of other deterministic, 
-hidden, parameterized, time-dependent processes, for instance markers 
-of chronicle disease activity.
-
-We consider the problem of predicting the values of a variable 
-controlled by a hidden, parameterized, time-dependent, deterministic 
-process. We assume that the variable values are observed only for a 
-limited number of time points and process parameters, and we aim at 
-predicting the values for the remaining time points and parameters.
-
-This problem description maps directly to the evaluation of 
-computational reproducibility in scientific pipelines: the process is 
-the evaluated pipeline, it is hidden since we consider the pipeline as a black box (we 
-don't inspect its source code), it is parametrized as it behaves 
-differently on different input datasets and parameters, it is 
-time-dependent as the value of the variable of interest varies 
-throughout the course of the pipeline execution. The variable of 
-interest is whether the pipeline outputs, most likely the files it 
-produces, are identical between execution conditions.
+studies could be used to predict the other variables controlled by 
+hidden, deterministic, hidden, parameterized, time-dependent processes, 
+for instance markers of chronicle disease activity. In the 
+reproducibility example studied in this paper, the variable of interest 
+is the reproducibility of files produced by the processing of a given 
+subjects, the process is the evaluated pipeline, it is hidden since we 
+consider the pipeline as a black box (we don't inspect its source 
+code), it is parametrized as it behaves differently on different input 
+datasets and parameters, it is time-dependent as the value of the 
+variable of interest varies throughout the course of the pipeline 
+execution.
 
@@
 \todo{Show an overlap to see where the error is located.}
-
-RFNTS and RFNTL could be used when the matrix is more  uncertain at the beginning or end of the pipeline.
-
-RS and RFNU tends to become the same for high training ratios.
 

### 2018-07-26 paper.tex
Added a figure generation script, updated README, now generate all figures in pdf directly, fixed typos

@@
         \centering
-        \begin{subfigure}[b]{0.4\linewidth}
+        \begin{subfigure}[b]{0.45\columnwidth}
                   \includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
@@
         \end{subfigure}
-        \begin{subfigure}[b]{0.4\linewidth}
+        \begin{subfigure}[b]{0.45\columnwidth}
                   \includegraphics[width=\columnwidth]{figures/5vs7_rows_04_training}
@@
         \end{subfigure}
-        \begin{subfigure}[b]{0.4\linewidth}
+        \begin{subfigure}[b]{0.45\columnwidth}
                  \includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
@@
         \end{subfigure}
-        \begin{subfigure}[b]{0.4\linewidth}
+        \begin{subfigure}[b]{0.45\columnwidth}
                   \includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
@@
         \end{subfigure}
-        \begin{subfigure}[b]{0.4\linewidth}
+        \begin{subfigure}[b]{0.45\columnwidth}
                   \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
@@
         \end{subfigure}
-        \begin{subfigure}[b]{0.4\linewidth}
+        \begin{subfigure}[b]{0.45\columnwidth}
                   \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
@@
         \end{subfigure}
-        \begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
+        \begin{subfigure}[b]{\columnwidth}
+        \centering
+        \includegraphics[width=0.45\columnwidth]{figures/5vs7_random-unreal_04_training}
                   \caption{Random Unreal}
@@
 \centering
-        %\begin{subfigure}[b]{0.4\linewidth}
+        %\begin{subfigure}[b]{\columnwidth}
                   %\includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/1_SubjectType_utility_matrix.png}
@@
         %\end{subfigure}
-        \begin{subfigure}[b]{0.4\linewidth}
+        \begin{subfigure}[b]{0.45\columnwidth}
                   \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/2_SubjectType_utility_matrix.png}
@@
         \end{subfigure}
-        \begin{subfigure}[b]{0.4\linewidth}
+        \begin{subfigure}[b]{0.45\columnwidth}
                   \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/4_SubjectType_utility_matrix.png}
@@
         \end{subfigure}
-                \begin{subfigure}[b]{0.4\linewidth}
+                \begin{subfigure}[b]{0.45\columnwidth}
                   \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/8_SubjectType_utility_matrix.png}
@@
         \end{subfigure}
-                \begin{subfigure}[b]{0.4\linewidth}
+                \begin{subfigure}[b]{0.45\columnwidth}
                   \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/16_SubjectType_utility_matrix.png}
@@
         \end{subfigure}
-                \begin{subfigure}[b]{0.4\linewidth}
+                \begin{subfigure}[b]{0.45\columnwidth}
                   \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/32_SubjectType_utility_matrix.png}
@@
         \end{subfigure}
-                \begin{subfigure}[b]{0.4\linewidth}
+                \begin{subfigure}[b]{0.45\columnwidth}
                   \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/64_SubjectType_utility_matrix.png}
@@
 release\footnote{\url{https://db.humanconnectome.org}} in three execution conditions with different
-versions of the CentOS operating system (5.\todo{?}, 6.8 and 7.2), using the
+versions of the CentOS operating system (5.11, 6.8 and 7.2), using the
 PreFreesurfer and Freesurfer pipelines described 
@@
   \centering
-  \begin{subfigure}[b]{0.45\linewidth}
+  \begin{subfigure}[b]{0.45\columnwidth}
         \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v6_utility_matrix.png}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.45\linewidth}
+  \begin{subfigure}[b]{0.45\columnwidth}
          \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v7_utility_matrix.png}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.45\linewidth}
+  \begin{subfigure}[b]{0.45\columnwidth}
         \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_6v7_utility_matrix.png}
@@
   \end{subfigure}
-  \begin{subfigure}[b]{0.45\linewidth}
+  \begin{subfigure}[b]{0.45\columnwidth}
         \includegraphics[width=\columnwidth]{data/Utility_Matrix/FS-100files/FS-First-bound-100files.png}
-  \caption{FS (first 100 files), C6 vs C7}
+  \caption{FS (100 files), C6 vs C7}
   \end{subfigure}
@@
 reported in Figure~\ref{fig:results-synthetic}. By construction, the 
-accuracy of the dummy classifier is close to 0.5 for all subject types. Random 
+accuracy of the dummy classifier is close to 0.5 for all subject types \todo{Why such variations?}. Random 
 Unreal performs very well for all subject types, which confirms that 
@@
 reduced number of empty columns. Surprisingly, RFNTS does not perform 
-well for more than 2 subject types \todo{Check that.}.
+well for more than 2 subject types, even for a training ratio of 0.9. \todo{Check that.}
 
@@
 \begin{figure*}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-2-types.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-2-types.pdf}
         \caption{2 subject types}
 \end{subfigure}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-4-types.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-4-types.pdf}
         \caption{4 subject types}
 \end{subfigure}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-8-types.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-8-types.pdf}
         \caption{8 subject types}
 \end{subfigure}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-16-types.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-16-types.pdf}
         \caption{16 subject types}
 \end{subfigure}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-32-types.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-32-types.pdf}
         \caption{32 subject types}
@@
 \hfill
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-64-types.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-64-types.pdf}
         \caption{64 subject types}
@@
 \begin{figure*}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-2-types.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-2-types.pdf}
         \caption{2 subject types}
 \end{subfigure}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-4-types.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-4-types.pdf}
         \caption{4 subject types}
 \end{subfigure}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-8-types.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-8-types.pdf}
         \caption{8 subject types}
 \end{subfigure}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-16-types.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-16-types.pdf}
         \caption{16 subject types}
 \end{subfigure}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-32-types.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-32-types.pdf}
         \caption{32 subject types}
@@
 \hfill
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-64-types.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-64-types.pdf}
         \caption{64 subject types}
@@
 well in the synthetic dataset, RFNU performs the best, with an accuracy 
-higher than 0.95 \todo{check value} for all datasets, when the training ratio is larger than 0.5. RS and RFNTL
-are slightly underperforming compared to RFNU.
-Complete rows and complete columns do not even reach the accuracy of the 
-dummy classifier. The reference method, Random Unreal, has an accuracy close
-to 1, which shows that collaborative filtering works well on this dataset too.
+higher than 0.95 for all datasets, when the training ratio is larger 
+than 0.5. RS and RFNTL are slightly underperforming compared to RFNU. 
+Complete rows and complete columns do not even reach the accuracy of 
+the dummy classifier. The reference method, Random Unreal, has an 
+accuracy close to 1, which shows that collaborative filtering works 
+well on this dataset too.
+\todo{why is the performance of columns so variable?}
 
 \begin{figure*}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v6.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v6.pdf}
         \caption{PFS, CentOS5 vs CentOS6}
 \end{subfigure}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v7.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v7.pdf}
         \caption{PFS, CentOS5 vs CentOS7}
 \end{subfigure}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-6v7.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-6v7.pdf}
         \caption{PFS, CentOS6 vs CentOS7}
 \end{subfigure}\hfill
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS/FS-100files/ALS-FS100files.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/FS-100files/ALS-FS100files.pdf}
         \caption{FS, CentOS6 vs CentOS7}
@@
 \begin{figure*}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v6.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v6.pdf}
         \caption{PFS, CentOS5 vs CentOS6}
 \end{subfigure}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v7.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v7.pdf}
         \caption{PFS, CentOS5 vs CentOS7}
@@
 \end{subfigure}
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-6v7.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-6v7.pdf}
         \caption{PFS, CentOS6 vs CentOS7}
 \end{subfigure}\hfill
-\begin{subfigure}[b]{0.4\linewidth}
-        \includegraphics[width=0.8\columnwidth, angle=-90]{data/results/means_of_results/ALS-Bias/FS-100files/ALS-Bias-FS100files.pdf}
+\begin{subfigure}[b]{\columnwidth}
+        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/FS-100files/ALS-Bias-FS100files.pdf}
         \caption{FS, CentOS6 vs CentOS7}

### 2018-07-26 plot_figures.sh

@@ -1,0 +1,8 @@
+#!/usr/bin/env bash
+
+for file in ./data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS-Bias/FS-100files/plot.gnplt ./data/results/means_of_results/ALS-Bias/PreFreeSurfer/plot.gnplt ./data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS/FS-100files/plot.gnplt ./data/results/means_of_results/ALS/PreFreeSurfer/plot.gnplt
+do
+  dir=$(dirname $file)
+  base=$(basename $file)
+  (cd ${dir}; gnuplot $base)
+done

### 2018-07-26 paper.tex
A few fixes and comments

@@
 \textit{a} and \textit{b} with two approaches that ensure that the 
-average of the distribution is $\alpha N_{f}$:
+average of the distribution is $\alpha N_{f}$: \todo{clarify this part}
 \begin{enumerate}
@@
 regularization parameter of 0.01, a maximum of 5 iterations and non 
-negative constraints set to true.
+negative constraints set to true. \todo{Tristan: Add one plot with sensitivity and specificity for 0.9 training}
 
@@
 reported in Figure~\ref{fig:results-synthetic}. By construction, the 
-accuracy of the dummy classifier is close to 0.5 for all subject types \todo{Why such variations?}. Random 
+accuracy of the dummy classifier is close to 0.5 for all subject types \todo{Soudabeh: why such variations?}. Random 
 Unreal performs very well for all subject types, which confirms that 
@@
 RS, RFNU and RFNTL achieve a 90\% accuracy for a training ratio of 
-about 0.85. Therefore, 15\% of the computations could potentially be 
+about 0.85 \todo{precise that}. Therefore, 15\% of the computations could potentially be 
 saved in such reproducibility studies.
@@
 
-\todo{Different number of factors.}
+\todo{Soudabeh: Different number of factors: type 8, RFNU, 50, 100, 200, 400.}
 
@@
 methods, including RFNTL and RFNTS, bias the sampling toward complete 
-or empty columns, which is sometimes detrimental to 
-accuracy.
+or empty columns, which is sometimes detrimental to accuracy.
+
+Figure~\ref{fig:overlap} illustrates the comparison between RFNU, RFNTL 
+and RFNTS. The matrices in this Figure represent the union between the 
+training and the test set, where the training set is represented in 
+black (negatives) and white (positives), and the test set is 
+represented in green (true positives), yellow (false negatives), gray 
+(true negatives) and red (false positives). This representation 
+provides insights regarding where, and perhaps why, prediction errors 
+occur. At this training ratio, RFNU (Figure~\ref{fig:overlap-rfntu}) 
+uniformly samples the number of files per subject between 0.8$N_f$ and 
+$N_f$. It provides an opportunity for ALS to be trained on the last 
+files of the pipelines, while maintaining a low number of columns with 
+a low training ratio. On the contrary, RFNTL 
+(Figure~\ref{fig:overlap-rfntl}) samples the number of files per 
+subject from 0.85$N_f$, but the probability to have a complete column 
+is 0 (the one complete column in Figure~\ref{fig:overlap-rfntl} is the one included
+to prevent cold start issues).
+
+\begin{figure*}
+\begin{subfigure}[b]{0.6\columnwidth}
+        \includegraphics[width=\columnwidth]{figures/RFNU_Syn_8_ALS_09_test_data_matrix_run1.png}
+        \caption{RFNU: $U(0.8N_f, N_f)$}
+        \label{fig:overlap-rfnu}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.6\columnwidth}
+        \includegraphics[width=\columnwidth]{figures/RFNT-L_Syn_8_ALS_09_test_data_matrix_run2.png}
+        \caption{RFNTL: $T(0.85N_f, 0.85N_f, N_f)$}
+        \label{fig:overlap-rfntl}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.6\columnwidth}
+        \includegraphics[width=\columnwidth]{figures/RFNT-S_Syn_8_ALS_09_test_data_matrix_run1.png}
+        \caption{RFNTS: 0.3$T(0, N_f, N_f)$+0.7$N_f$}
+        \label{fig:overlap-rfnts}
+\end{subfigure}
+\caption{Comparison between RFNU, RFNTL and RFNTS on synthetic dataset with 8 types, $\alpha=0.9$.}
+\label{fig:overlap}
+\end{figure*}
 
@@
 
-\todo{Discussion on points that are not part of constant lines.}
+\todo{Discussion on points that are not part of constant lines. Soudabeh: add an overlap matrix for FS, RFNU, ALS, at 0.5 or 0.6.}
 
-\todo{Show an overlap to see where the error is located.}
-
-\todo{Make sure the code is available and results are reproducible.}
+\todo{Make sure the code is available and results are reproducible. Soudabeh: push your code to reprotools. Tristan: release and check.}
 

### 2018-07-26 paper.tex
Finished discussion on overlap matrix

@@
 subject from 0.85$N_f$, but the probability to have a complete column 
-is 0 (the one complete column in Figure~\ref{fig:overlap-rfntl} is the one included
-to prevent cold start issues).
+is 0 (the one complete column in Figure~\ref{fig:overlap-rfntl} is the 
+one included to prevent cold start issues), which leads to a "stripe" 
+of errors at the bottom of the matrix. RFNTS 
+(Figure~\ref{fig:overlap-rfnts}) doesn't have this issue, as it 
+includes many complete columns in the training set, but this comes at 
+the cost of several columns with a very low number of files, lower than 
+60\%. For such columns, the prediction may go somewhat wrong, which explains
+the reduced accuracy compared to RFNU.
 

### 2018-07-30 paper.tex
Added ROC analysis

@@
 
+\subsubsection{ROC analysis}
+
+Figure~\ref{fig:roc} compares the sampling methods in the ROC space, 
+for a training ratio of 0.9, on the synthetic and Freesurfer dataset. 
+The PreFreesurfer dataset is not included since specificity of RFNTL, 
+RFNU, RS and complete rows is undefined at this training ratio (the 
+test set only contains positive elements \todo{check matrix with 
+Soudabeh to confirm}). The average sensitivity and specificity values 
+are reported in Table~\ref{table:roc}. On average, RFNU is the best 
+performing method.
+
+\begin{figure*}
+\includegraphics[width=\columnwidth]{data/results/roc/roc.pdf}
+\includegraphics[width=\columnwidth]{data/results/roc/roc-closeup.pdf}
+\caption{Comparison of the sampling methods in the ROC space for the 6 synthetic datasets and Freesurfer. Right: entire dataset. Left: close-up on the top-left part.}
+\label{fig:roc}
+\end{figure*}
+
+\begin{table}
+\centering
+\begin{tabular}{ccc}
+& Sensitivity & Specificity \\
+\hline
+Complete Columns & 0.53 & 0.97\\
+Complete Rows & 0.43 & 0.89\\
+Random Subjects & 0.88 & 0.99\\
+RFNU & 0.92 & 0.99 \\
+RFNTL & 0.81 & 0.97\\
+RFNTS & 0.65 & 0.93 \\
+Random Unreal & 1 & 1
+\end{tabular}
+\caption{Average sensitivity and specificity values for the 6 synthetic datasets and Freesurfer.}
+\label{table:roc}
+\end{table}
+
+\subsection{Effect of the number of factors}
 \todo{Soudabeh: Different number of factors: type 8, RFNU, 50, 100, 200, 400.}

### 2018-07-30 data/results/roc/extract_roc.sh

@@ -1,0 +1,19 @@
+#!/usr/bin/env bash
+
+set -e
+set -u
+
+for i in RandomUnreal RFNT-L RFNT-S RFNU rows columns RS
+do
+    \rm -f roc_$i.csv
+    for file in ../means_of_results/ALS/FS-100files/ALS-*-$i-average.txt
+    do
+        echo -n $i" "$file" " >> roc_$i.csv
+        awk -F ';' '$1==0.9 {print $2" "$4" "$5}' $file >> roc_$i.csv
+    done
+    for file in ../means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-*-$i-average.txt
+    do
+        echo -n $i" "$file" " >> roc_$i.csv
+        awk -F ';' '$1==0.9 {print $2" "$4" "$5}' $file >> roc_$i.csv
+    done
+done

### 2018-07-30 plot_figures.sh

@@ -1,6 +1,6 @@
 #!/usr/bin/env bash
 
-for file in ./data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS-Bias/FS-100files/plot.gnplt ./data/results/means_of_results/ALS-Bias/PreFreeSurfer/plot.gnplt ./data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS/FS-100files/plot.gnplt ./data/results/means_of_results/ALS/PreFreeSurfer/plot.gnplt
+for file in ./data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS-Bias/FS-100files/plot.gnplt ./data/results/means_of_results/ALS-Bias/PreFreeSurfer/plot.gnplt ./data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS/FS-100files/plot.gnplt ./data/results/means_of_results/ALS/PreFreeSurfer/plot.gnplt ./data/results/roc/plot.gnplt
 do
   dir=$(dirname $file)
   base=$(basename $file)

### 2018-07-30 paper.tex
Added effect of number of factors

@@
 
-\todo{Soudabeh, can you remove the caption on all matrices?}
-
 \subsection{Synthetic Data}
@@
 regularization parameter of 0.01, a maximum of 5 iterations and non 
-negative constraints set to true. \todo{Tristan: Add one plot with sensitivity and specificity for 0.9 training}
+negative constraints set to true.
 
@@
 reported in Figure~\ref{fig:results-synthetic}. By construction, the 
-accuracy of the dummy classifier is close to 0.5 for all subject types \todo{Soudabeh: why such variations?}. Random 
-Unreal performs very well for all subject types, which confirms that 
-ALS is working correctly. Unsurprisingly, all the other methods perform 
-better than the dummy classifier, and their accuracy decreases as the 
-number of subject types increases.
+accuracy of the dummy classifier is close to 0.5 for all subject types. 
+Random Unreal performs very well for all subject types, which confirms 
+that ALS is working correctly. Unsurprisingly, all the other methods 
+perform better than the dummy classifier, and their accuracy decreases 
+as the number of subject types increases.
 
@@
 
-\subsubsection{ROC analysis}
+\subsection{ROC analysis}
 
@@
 
-\subsection{Effect of the number of factors}
-\todo{Soudabeh: Different number of factors: type 8, RFNU, 50, 100, 200, 400.}
+\subsection{Varying the number of factors}
+Figure~\ref{fig:factors} shows the effect of the number of factors used 
+in ALS, for the RFNU method and the synthetic dataset. We do not find a 
+clear effect of the number of factors on the accuracy.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
+\caption{Effect of the number of factors used in ALS, RFNU method, synthetic dataset.}
+\label{fig:factors}
+\end{figure}
 
@@
 provides insights regarding where, and perhaps why, prediction errors 
-occur. At this training ratio, RFNU (Figure~\ref{fig:overlap-rfntu}) 
+occur. At this training ratio, RFNU (Figure~\ref{fig:overlap-rfnu}) 
 uniformly samples the number of files per subject between 0.8$N_f$ and 

### 2018-07-30 plot_figures.sh

@@ -1,6 +1,6 @@
 #!/usr/bin/env bash
 
-for file in ./data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS-Bias/FS-100files/plot.gnplt ./data/results/means_of_results/ALS-Bias/PreFreeSurfer/plot.gnplt ./data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS/FS-100files/plot.gnplt ./data/results/means_of_results/ALS/PreFreeSurfer/plot.gnplt ./data/results/roc/plot.gnplt
+for file in ./data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS-Bias/FS-100files/plot.gnplt ./data/results/means_of_results/ALS-Bias/PreFreeSurfer/plot.gnplt ./data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS/FS-100files/plot.gnplt ./data/results/means_of_results/ALS/PreFreeSurfer/plot.gnplt ./data/results/roc/plot.gnplt ./data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/plot.gnplt
 do
   dir=$(dirname $file)
   base=$(basename $file)

### 2018-07-30 paper.tex
Added overlap FS matrix

@@
 
+Figure~\ref{fig:error-locality} shows the results obtained by RFNU on 
+the Freesurfer dataset for a training ratio of 0.6. The prediction 
+error is localized (1) at the bottom of the matrix, which corresponds 
+to the end of the execution, and (2) in the regions where file 
+reproducibility varies across subjects, i.e., lines are not entirely 
+black or entirely white.
+\begin{figure}
+\includegraphics[width=0.6\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
+\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
+\label{fig:error-locality}
+\end{figure}
+
 In any case, we recommend not to include biases in the collaborative filtering 
@@
 
-\todo{Discussion on points that are not part of constant lines. Soudabeh: add an overlap matrix for FS, RFNU, ALS, at 0.5 or 0.6.}
+The code and data used in this paper are available at 
+\url{https://github.com/big-data-lab-team/paper-reproducibility-collaborative-filtering}.
 
-\todo{Make sure the code is available and results are reproducible. Soudabeh: push your code to reprotools. Tristan: release and check.}
+\todo{Soudabeh: push your code to reprotools. Tristan: release and check.}
 

### 2018-07-30 paper.tex
Typos
Improved discussion

@@
       #1}}}
-\newcommand{\comment}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{blue}\textbf{Comment}:
-      #1}}}
-
 \newcommand{\note}[1]{
@@
 Section~\ref{sec:results}.
-The paper ends with a discussion about the impact, limitations and 
-generalizability of our results.
+We finally conclude on the best sampling method to use, and the 
+potential impacts of the results, and on their limitations and 
+generalizability.
 
@@
 reduced number of empty columns. Surprisingly, RFNTS does not perform 
-well for more than 2 subject types, even for a training ratio of 0.9. \todo{Check that.}
+well for more than 2 subject types, even for a training ratio of 0.9.
 
-RS, RFNU and RFNTL achieve a 90\% accuracy for a training ratio of 
-about 0.85 \todo{precise that}. Therefore, 15\% of the computations could potentially be 
-saved in such reproducibility studies.
+Up to 32 subject types, RFNU achieves a 90\% accuracy for a training 
+ratio of about 0.85. Therefore, 15\% of the computations could 
+potentially be saved in such reproducibility studies.
 
@@
 clear effect of the number of factors on the accuracy.
-
-\begin{figure}
+\begin{figure}[h]
 \includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
@@
 
-\section{Discussion}
-
-% Which method is the best
-While collaborative filtering, perhaps unsurprisingly, is able to 
-correctly predict the missing values in a matrix modeling the 
-reproducibility problem, the usual random sampling method cannot be 
-used in time-constrained processes. We proposed 6 sampling methods to 
-address this issue, and we found that one of them, RFNU, \todo{check 
-that} is consistently able to solve the problem. We explain that by 
-the fact that RFNU leads the training set to contain a balanced mix 
-between nearly complete and nearly empty columns, with a continuum of 
-intermediate configurations in between. On the contrary, other sampling 
-methods, including RFNTL and RFNTS, bias the sampling toward complete 
-or empty columns, which is sometimes detrimental to accuracy.
-
+\subsection{Error localization}
 Figure~\ref{fig:overlap} illustrates the comparison between RFNU, RFNTL 
@@
 uniformly samples the number of files per subject between 0.8$N_f$ and 
-$N_f$. It provides an opportunity for ALS to be trained on the last 
-files of the pipelines, while maintaining a low number of columns with 
+$N_f$, which enables the training on the last 
+files of the pipeline, while maintaining a low number of columns with 
 a low training ratio. On the contrary, RFNTL 
@@
 is 0 (the one complete column in Figure~\ref{fig:overlap-rfntl} is the 
-one included to prevent cold start issues), which leads to a "stripe" 
+one included to prevent cold start issues), which leads to a ``stripe" 
 of errors at the bottom of the matrix. RFNTS 
 (Figure~\ref{fig:overlap-rfnts}) doesn't have this issue, as it 
-includes many complete columns in the training set, but this comes at 
-the cost of several columns with a very low number of files, lower than 
-60\%. For such columns, the prediction may go somewhat wrong, which explains
+includes many complete columns in the training set. However, it comes at 
+the cost of several columns with a number of files lower than 
+60\%: in such columns, the prediction is often entirely wrong, which explains
 the reduced accuracy compared to RFNU.
@@
 
-% Training ratio
-On datasets that are strongly dependent on row bias, such as the real 
-datasets studied here, RFNU provides accuracy values that are 
-consistently higher than 0.95 for training ratios higher than 0.5, even 
-when biases are not included in the collaborative filtering 
-optimization. On the synthetic dataset, RFNU still performs very well 
-when biases are not included. However, the training ratio required to 
-reach a 0.95 accuracy increases with the number of subject types 
-present in the dataset. \todo{maybe find a relation between the 
-required training ratio and the number of subjects per subject type in 
-the entire dataset}
-
 Figure~\ref{fig:error-locality} shows the results obtained by RFNU on 
@@
 
-In any case, we recommend not to include biases in the collaborative filtering 
+\section{Conclusion}
+
+% Which method is the best
+While collaborative filtering, perhaps unsurprisingly, is able to 
+correctly predict the missing values in a matrix modeling the 
+reproducibility problem, the usual random sampling method cannot be 
+used in time-constrained processes. We proposed 6 sampling methods to 
+address this issue, and we found that one of them, RFNU, performs 
+better than the other ones on average. We 
+explain that by the fact that RFNU builds the training set using a 
+balanced mix of nearly complete and nearly empty columns, with a 
+continuum of 
+intermediate configurations. On the contrary, other sampling 
+methods, including RFNTL and RFNTS, bias the sampling toward complete 
+or empty columns, which is sometimes detrimental to accuracy.
+
+For datasets that are strongly dependent on row bias, such as the 
+PreFreesurfer and Freesurfer datasets studied here, RFNU provides 
+accuracy values that are consistently higher than 0.95 for training 
+ratios higher than 0.5, even 
+when biases are not included in the collaborative filtering 
+optimization. For the synthetic dataset, RFNU still performs very well 
+when biases are not included, but it does very poorly when biases are included.
+For this reason, we recommend not to include biases in the collaborative filtering 
 optimization to solve this problem. Even though biases provide a slight 
@@
 
-% How can this be used in practice
 From a practical standpoint, our study shows that reproducibility 
-evaluations can be conducted using only 50\% of the files produced by 
-the evaluated pipelines, with an accuracy above 95\%. Potentially, this 
-could reduce the computing time and storage required for such studies 
-by a factor of 2. However, such studies could not be conducted by 
-processing only half of the subjects entirely, which would correspond 
-to the Complete Columns sampling method. Instead, the processing of all 
-the subjects should be initiated, and it should be terminated in a random
-uniform way, assuming that files are uniformly produced throughout the 
-execution.
+evaluations of the PreFreesurfer and Freesurfer pipelines can be 
+conducted using only 50\% of the files produced by the evaluated 
+pipelines, with an accuracy above 95\%. Potentially, this could reduce 
+the computing time and storage required for such studies by a factor of 
+2. However, such studies could not be conducted by processing only half 
+of the subjects entirely, which would correspond to the Complete 
+Columns sampling method. Instead, the processing of all the subjects 
+should be initiated, and it should be terminated in a random uniform 
+way, assuming that files are uniformly produced throughout the 
+execution. On more complex matrices, such as the synthetic dataset 
+studied here, the training ratio required to get a 95\% accuracy 
+increases to 0.85 to 0.9.
 
@@
 % Other possible examples
-The method described in this paper and applied to reproducibility 
-studies could be used to predict the other variables controlled by 
-hidden, deterministic, hidden, parameterized, time-dependent processes, 
-for instance markers of chronicle disease activity. In the 
-reproducibility example studied in this paper, the variable of interest 
-is the reproducibility of files produced by the processing of a given 
-subjects, the process is the evaluated pipeline, it is hidden since we 
-consider the pipeline as a black box (we don't inspect its source 
-code), it is parametrized as it behaves differently on different input 
-datasets and parameters, it is time-dependent as the value of the 
-variable of interest varies throughout the course of the pipeline 
-execution.
+The variable of interest in our study was the reproducibility of files 
+produced by the processing of a given subject, and it was controlled by 
+a process, the evaluated pipeline. This process was hidden, since we 
+considered the pipeline as a black box (we did not inspect its source 
+code), it was deterministic, since it was implemented as a program, it 
+was parametrized, as it behaved differently on different input datasets 
+and parameters, and it was time-dependent, as the value of the 
+variable of interest varied throughout the course of the pipeline 
+execution. The method described in this paper could possibly be used to 
+predict other variables controlled by such hidden, deterministic, 
+parametrized, and time-dependent processes, for instance markers of 
+chronic disease activity.
 

### 2018-07-30 paper.tex
Improved description of RFNTL

@@
 
-\paragraph{Complete Columns 
+\subsubsection{Complete Columns 
 (Figure~\ref{fig:Columns-Sample-Training-set})} The training set is 
@@
 
-\paragraph{Complete Rows (Figure~\ref{fig:Rows-Sample-Training-set})} 
+\subsubsection{Complete Rows (Figure~\ref{fig:Rows-Sample-Training-set})} 
 The training set is sampled by selecting complete rows in the utility 
@@
 
-\paragraph{Random Subjects -- RS 
+\subsubsection{Random Subjects -- RS 
 (Figure~\ref{fig:Uniform-S-Sample-Training-set})} This method builds 
@@
 
-\paragraph{Random File Numbers (Uniform) -- RFNU (Figure~\ref{fig:Diagonal-Sample-Training-set})}
+\subsubsection{Random File Numbers (Uniform) -- RFNU (Figure~\ref{fig:Diagonal-Sample-Training-set})}
 The number of files selected for every subject is randomly selected in
@@
 
-\paragraph{Random File Numbers (Triangular) -- RFNT}
+\subsubsection{Random File Numbers (Triangular) -- RFNT}
 The number of files selected for every subject is randomly selected in
@@
 $\frac{a+b+c}{3}$. We set \textit{c} to $N_{f}$ and we set 
-\textit{a} and \textit{b} with two approaches that ensure that the 
-average of the distribution is $\alpha N_{f}$: \todo{clarify this part}
-\begin{enumerate}
-        \item Largest a (RFNTL, Figure~\ref{fig:triangular-L-Sample-Training-set}): a is set to the 
-        largest possible value, i.e., b. The average of the 
-        distribution is $\frac{2a+N_{f}}{3}$, therefore 
-        $a=\frac{3\alpha-1}{2}N_{f}$. When $\alpha \leq 1/3$, the 
-        number of files in every subject is sampled from $T(0, 0, N_f)$ 
-        with probability $3\alpha$ and set to 0 otherwise, to ensure 
-        that the average number of files by subject in the training set 
-        is $\alpha N_f$.
-        \item Smallest a (RFNTS, Figure~\ref{fig:triangular-S-Sample-Training-set}): a is 
-        set to the smallest possible value, i.e., 0. The average of the 
-        distribution is $\frac{b+N_{f}}{3}$, therefore 
-        $b=N_{f}(3\alpha-1)$. This implies that $\alpha \geq 1/3$, so 
-        that $b \geq 0$, and $\alpha \leq 2/3$, so that $b \leq N_f$. 
-        When $\alpha < 1/3$, we set $b=0$ and the number of files 
+\textit{a} and \textit{b} with the following two approaches.
+
+\paragraph{Largest a (RFNTL, 
+Figure~\ref{fig:triangular-L-Sample-Training-set})} a is set to the 
+largest possible value, i.e., b, and b is set accordingly to ensure 
+that the average of the distribution is $\alpha N_{f}$. Two cases occur:
+\begin{itemize}
+\item When $\alpha > 1/3$:
+\[ \textit{a}=\textit{b}=\frac{3\alpha-1}{2}N_{f}
+\]
+\item When $\alpha \leq 1/3$: $a=b=0$, the number of files selected 
+in every subject is sampled from $T(0, 0, N_f)$ with probability 
+$3\alpha$ and set to 0 otherwise.
+\end{itemize}
+
+\paragraph{Smallest a (RFNTS, 
+Figure~\ref{fig:triangular-S-Sample-Training-set})} a is set to the 
+smallest possible value, i.e., 0, and b is set accordingly to ensure that the average of the
+distribution is $\alpha N_{f}$. Three cases occur:
+\begin{itemize}
+\item When $\alpha < 1/3$: $a=b=0$, the number of files 
 selected in every subject is sampled from $T(0, 0, N_f)$ with 
-        probability $3\alpha$ and set to 0 otherwise, as in RFNTL. 
-        When $\alpha \geq 2/3$, we set $b=N_f$ and the number of files 
-        selected in every subject is sampled from $T(0, N_f, N_f)$ with 
-        probability $3(1-\alpha)$ and set to $N_f$ otherwise, still to 
-        ensure that the average number of files by subject in the training set is 
-        $\alpha N_f$.
-\end{enumerate}
+probability $3\alpha$ and set to 0 otherwise.
+\item When $1/3 \leq \alpha \leq 2/3$:
+\[
+          \textit{a} = 0   \quad ; \quad
+          \textit{b}=N_{f}(3\alpha-1)
+\]
+\item When $\alpha \geq 2/3$: $b=N_f$, the number of files selected in 
+every subject is sampled from $T(0, N_f, N_f)$ with probability 
+$3(1-\alpha)$ 
+and set to $N_f$ otherwise.
+\end{itemize}
+
 As illustrated in Figures~\ref{fig:triangular-L-Sample-Training-set} 
@@
 $\alpha$, all subjects will have at least a few files in the training 
-set, which is not the case for RFNU or RFNTS.
+set (no empty column), which is not the case for RFNU or RFNTS.
 \begin{figure}
@@
 
-\paragraph{Random Unreal (Figure 
+\subsubsection{Random Unreal (Figure 
 ~\ref{fig:Random-Unreal-Sample-Training-set})} The training set is 
@@
 
-Two experiments have been conducted for each reproducibility matrix, to evaluate the performance of our 
-predictions using (1) ALS without biases, and (2) ALS with biases. 
-Results will be evaluated using classification accuracy and compared to (1) a dummy classifier that always 
-predicts the value in the majority class and (2) the Random Unreal 
-method, used as the baseline sampling technique. All reported values are averages
-over 5 repetitions. Due to sampling issues, it is possible that the actual 
-training ratio obtained with some of the sampling methods does not 
+We conducted two experiments for each reproducibility matrix, to evaluate the performance of our 
+predictions using (1) ALS without biases, and (2) ALS with biases. We 
+compare the performance of our sampling methods to (1) a dummy 
+classifier that always predicts the value in the majority class and (2) 
+the Random Unreal method, used as the baseline sampling technique. All 
+reported values are averages over 5 repetitions. Due to sampling 
+issues, it is possible that the actual training ratio obtained with 
+some of the sampling methods does not 
 match the target one. We checked that the difference between the target 
@@
 \subsubsection{ALS without Bias}
-
-Accuracy results for the different numbers of subject types are 
-reported in Figure~\ref{fig:results-synthetic}. By construction, the 
-accuracy of the dummy classifier is close to 0.5 for all subject types. 
-Random Unreal performs very well for all subject types, which confirms 
-that ALS is working correctly. Unsurprisingly, all the other methods 
+ Figure~\ref{fig:results-synthetic} shows accuracy results for ALS 
+ without bias. By construction, the accuracy of the dummy classifier is 
+ close to 0.5 for all subject types. Random Unreal performs very well 
+ for all subject types, which confirms that ALS is working correctly. 
+ Unsurprisingly, all the other methods 
 perform better than the dummy classifier, and their accuracy decreases 
@@
 well for more than 2 subject types, even for a training ratio of 0.9.
-
-Up to 32 subject types, RFNU achieves a 90\% accuracy for a training 
-ratio of about 0.85. Therefore, 15\% of the computations could 
-potentially be saved in such reproducibility studies.
 
@@
 
-Results of ALS with bias are reported in 
-Figure~\ref{fig:results-synthetic-als-bias}. RS, RFNU and RFNTL remain 
-the methods that best compare to Random Unreal, but the achieved 
-accuracy is much lower than without Biases. This is presumably due to 
+Figure~\ref{fig:results-synthetic-als-bias} shows accuracy results for 
+ALS with bias. RS, RFNU and RFNTL remain the methods that best compare 
+to Random Unreal, but the achieved accuracy is much lower than without 
+biases. This is presumably due to 
 the fact that file biases are all close to 0.5 in the synthetic data. 
@@
 
-Results for ALS without bias are reported in 
-Figure~\ref{fig:results-real-als}. Among the methods that performed 
+Figure~\ref{fig:results-real-als} shows the accuracy results for ALS without bias. Among the methods that performed 
 well in the synthetic dataset, RFNU performs the best, with an accuracy 
@@
 
-Results for ALS with bias are reported in 
-Figure~\ref{fig:results-real-als-bias}. From a training ratio of 0.5, 
-all methods have a very good accuracy for all datasets, except complete 
-columns in Figure~\ref{fig:pfs-c5vsc7-bias}. All methods except RFNU, 
-RFNTL and RFNTS also perform well for a training ratio lower than 0.5. 
-Overall, the accuracy of the methods is much higher than without bias. 
-This is because the file bias is very strong in this dataset, as 
-illustrated by the large number of constant lines in the matrices in 
-Figure~\ref{fig:utility-matrices}.
+Figure~\ref{fig:results-real-als-bias} shows the accuracy results for 
+ALS with bias. From a training ratio of 0.5, all methods have a very 
+good accuracy for all datasets, except complete columns in 
+Figure~\ref{fig:pfs-c5vsc7-bias}. All methods except RFNU, RFNTL and 
+RFNTS also perform well for a training ratio lower than 0.5. Overall, 
+the accuracy of the methods is much higher than without bias, due to 
+the fact that the file bias is very strong in this dataset, as 
+it can be seen in Figure~\ref{fig:utility-matrices}.
 
@@
 Soudabeh to confirm}). The average sensitivity and specificity values 
-are reported in Table~\ref{table:roc}. On average, RFNU is the best 
-performing method.
+are reported in Table~\ref{table:roc}, which confirms that RFNU is the best 
+performing method on average.
 
@@
 Figure~\ref{fig:factors} shows the effect of the number of factors used 
-in ALS, for the RFNU method and the synthetic dataset. We do not find a 
+in the ALS optimization for the RFNU method and the synthetic dataset. We do not find a 
 clear effect of the number of factors on the accuracy.
@@
 \subsection{Error localization}
-Figure~\ref{fig:overlap} illustrates the comparison between RFNU, RFNTL 
-and RFNTS. The matrices in this Figure represent the union between the 
-training and the test set, where the training set is represented in 
-black (negatives) and white (positives), and the test set is 
-represented in green (true positives), yellow (false negatives), gray 
-(true negatives) and red (false positives). This representation 
-provides insights regarding where, and perhaps why, prediction errors 
+
+Figure~\ref{fig:overlap} compares the prediction errors made by RFNU, 
+RFNTL and RFNTS. The matrices in this Figure represent the training set 
+in black (negatives) and white (positives), and the test set in green 
+(true positives), yellow (false negatives), gray (true negatives) and 
+red (false positives). This representation provides insights regarding 
+where, and perhaps why, prediction errors 
 occur. At this training ratio, RFNU (Figure~\ref{fig:overlap-rfnu}) 

### 2018-07-30 paper.tex

@@
 well on this dataset too.
-\todo{why is the performance of columns so variable?}
 
@@
 RFNU, RS and complete rows is undefined at this training ratio (the 
-test set only contains positive elements \todo{check matrix with 
-Soudabeh to confirm}). The average sensitivity and specificity values 
+test set only contains positive elements \todo{Soudabeh: check matrix to confirm}). The average sensitivity and specificity values 
 are reported in Table~\ref{table:roc}, which confirms that RFNU is the best 
@@
 in the ALS optimization for the RFNU method and the synthetic dataset. We do not find a 
-clear effect of the number of factors on the accuracy.
+clear effect of the number of factors on the accuracy. \todo{Soudabeh, add results for 50 and 800 factors}
 \begin{figure}[h]

### 2018-08-06 paper.tex
Added a section to describe iterations results

@@
 
+\subsection{Varying the number of iterations}
+Figure~\ref{fig:iterations} illustrates the impact of the number of iterations used to minimizing the error of matrix factorization for the RFNU method and synthetic dataset with 50 factors.
+As it shown, the increase in the number of iterations have slight effect on the accuracy except in the low training ratio of 10\% where maximum 20 iterations deteriorates the accuracy by 20\% .
+Also in the high training ratio such as 80\% and 90\% where 2 iterations leads to lower accuracy.
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Iterations-rank50/ALS-8-types-iteration.pdf}
+\caption{Effect of the number of iterations used in ALS, RFNU method, 50 factors, synthetic dataset.}
+\label{fig:iterations}
+\end{figure}
+
 \subsection{Error localization}
@@
 the computing time and storage required for such studies by a factor of 
-2. However, such studies could not be conducted by processing only half 
+3 and iteration of 4. However, such studies could not be conducted by processing only half 
 of the subjects entirely, which would correspond to the Complete 

### 2018-08-06 paper.tex

@@
 in the ALS optimization for the RFNU method and the synthetic dataset. We do not find a 
-clear effect of the number of factors on the accuracy. \todo{Soudabeh, add results for 50 and 800 factors}
+clear effect of the number of factors on the accuracy.
+As it shown, number of factors does not have effect on accuracy specially for the training ratios less than 50\% .However, for the training ratios  over than that having less than 3 factors can dramatically effect the accuracy.
+Notably at training ratio of 90\% the major accuracy gap is observed between the compute accuracy with 2 factors and the 3 factors; 2 factors accuracy is about 40\% lower than 3 factors accuracy.
+
 \begin{figure}[h]

### 2018-08-06 paper.tex
Minor corrections following Soudabeh's updates

--- 2018-07-30 paper.tex
@@
 Figure~\ref{fig:factors} shows the effect of the number of factors used 
-in the ALS optimization for the RFNU method and the synthetic dataset. We do not find a 
-clear effect of the number of factors on the accuracy. \todo{Soudabeh, add results for 50 and 800 factors}
+in the ALS optimization for the RFNU method, and the synthetic dataset with 8 types. 
+For training ratios greater or equal than 0.5, the accuracy obtained 
+with 3 factors is substantially higher than with 2 factors. Beyond 
+3, the number of factors does not have an effect on the accuracy. 
+This shows that the data is best explained by 3 factors. For training 
+ratios lower than 0.5, the number of factors does not have any effect 
+on the accuracy, presumably due to the low accuracy of the method.\todo{Soudabeh, check if the factors can be interpreted.}
+
 \begin{figure}[h]
-\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
+\includegraphics[width=0.9\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
 \caption{Effect of the number of factors used in ALS, RFNU method, synthetic dataset.}
 \label{fig:factors}
+\end{figure}
+
+\subsection{Varying the number of iterations}
+Figure~\ref{fig:iterations} illustrates the effect of the number of 
+iterations used in the ALS optimization, for the 
+RFNU method, the synthetic dataset with 8 types, and 50 factors.
+
+From a training ratio of 0.7, the number of iterations has a moderate 
+effect on the accuracy. Our previous experiments used 5 iterations, 
+which only degrades the accuracy slightly compared to 15 or 20 iterations.
+
+\begin{figure}[h]
+\includegraphics[width=0.9\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Iterations-rank50/ALS-8-types-iteration.pdf}
+\caption{Effect of the number of iterations used in ALS, RFNU method, 50 factors, synthetic dataset.}
+\label{fig:iterations}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=0.6\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
+\centering
+\includegraphics[width=0.55\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
 \caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}

### 2018-08-13 paper.tex
Added comment

@@
   Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada\\
-  {first.last}@concordia.ca}
+  {first.last}@concordia.ca \vspace*{-0.5cm}}
 
@@
 RFNU, RS and complete rows is undefined at this training ratio (the 
-test set only contains positive elements \todo{Soudabeh: check matrix to confirm}). The average sensitivity and specificity values 
+test set only contains positive elements). The average sensitivity and specificity values 
 are reported in Table~\ref{table:roc}, which confirms that RFNU is the best 
@@
 \end{figure}
+
+ \note{Soudabeh, add figure with two 3D plots showing the 3 factors of 
+ every item and subject. Comment: the method indeed separates files in 
+ 3 blocks (for 8 types) and subjects in 8 types.}
 
@@
 
+\todo{publish code on zenodo}
+
 \section*{Acknowledgement}

### 2018-08-15 paper.tex
Added comment and figures for figures for user/item factors

@@
 
- \note{Soudabeh, add figure with two 3D plots showing the 3 factors of 
- every item and subject. Comment: the method indeed separates files in 
- 3 blocks (for 8 types) and subjects in 8 types.}
+\begin{figure}[h]
+\includegraphics[width=0.9\columnwidth]{data/results/latent-factors/5i-3f-ALS-r1-08-userFactors.pdf}
+\caption{The three subject latent factor vectors from a matrix decomposition of the synthetic matrix of 8 subject types}
+\label{fig:userfactors}
+\end{figure}
+
+As in figures ~\ref{fig:userfactors} and  ~\ref{fig:itemfactors} shown by use of three latent factors the RFNU method indeed separates the files of synthetic matrix of 8 subject type into three blocks and also its subjects into eight types.
+
+\begin{figure}[h]
+\includegraphics[width=0.9\columnwidth]{data/results/latent-factors/5i-3f-ALS-r1-08-itemFactors.pdf}
+\caption{The three file latent factor vectors from a matrix decomposition of the synthetic matrix of 8 subject types}
+\label{fig:itemfactors}
+\end{figure}
 

### 2018-08-15 plot_figures.sh
Added the plot script of user/item factors figures

@@ -1,6 +1,6 @@
 #!/usr/bin/env bash
 
-for file in ./data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS-Bias/FS-100files/plot.gnplt ./data/results/means_of_results/ALS-Bias/PreFreeSurfer/plot.gnplt ./data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS/FS-100files/plot.gnplt ./data/results/means_of_results/ALS/PreFreeSurfer/plot.gnplt ./data/results/roc/plot.gnplt ./data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/plot.gnplt ./data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Iterations-rank50/plot-iteration.gnplt
+for file in ./data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS-Bias/FS-100files/plot.gnplt ./data/results/means_of_results/ALS-Bias/PreFreeSurfer/plot.gnplt ./data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/plot.gnplt ./data/results/means_of_results/ALS/FS-100files/plot.gnplt ./data/results/means_of_results/ALS/PreFreeSurfer/plot.gnplt ./data/results/roc/plot.gnplt ./data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/plot.gnplt ./data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Iterations-rank50/plot-iteration.gnplt ./data/results/latent-factors/itemFactor-plot-3d.gnplt  ./data/results/latent-factors/userFactor-plot-3d.gnplt
 do
   dir=$(dirname $file)
   base=$(basename $file)

### 2018-08-16 paper.tex
Small fix
Updated the file directory of figures user/item factors

@@
 anatomical and functional characteristics of their brain, for instance through
-Magnetic Resonance Imaging (MRI) or Electroencephalography (EEG). The number of files 
+Magnetic Resonance Imaging (MRI) or Electroencephalography (EEG). The number of input files 
 associated with a subject may vary, and these files may also be of 
@@
 \begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{data/results/latent-factors/5i-3f-ALS-r1-08-userFactors.pdf}
+\includegraphics[width=0.9\columnwidth]{figures/5i-3f-ALS-r1-08-userFactors.pdf}
 \caption{The three subject latent factor vectors from a matrix decomposition of the synthetic matrix of 8 subject types}
@@
 \begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{data/results/latent-factors/5i-3f-ALS-r1-08-itemFactors.pdf}
+\includegraphics[width=0.9\columnwidth]{figures/5i-3f-ALS-r1-08-itemFactors.pdf}
 \caption{The three file latent factor vectors from a matrix decomposition of the synthetic matrix of 8 subject types}

### 2018-08-16 paper.tex
Updates following discussion with Soudabeh

--- 2018-08-13 paper.tex
@@
 instance due to different pipeline branches being executed depending on 
-the nature, cardinality or content of the input data. For instance, in 
+the nature, cardinality or content of the input data. As an example, in 
 the public database released by the Human Connectome 
@@
 \emph{errors}. We approach the problem from the point of view of 
-collaborative filtering, inspired by previous examples that applied 
+collaborative filtering, inspired by works that applied 
 this method outside of its initial application domain, for instance 
@@
 sampled from the utility matrix. Instead, the training set has to 
-respect the time constraints imposed by the order in which files 
-are produced during pipeline executions.
+respect the time constraints imposed by the file creation order during 
+pipeline executions.
 
@@
 Section~\ref{sec:results}.
-We finally conclude on the best sampling method to use, and the 
-potential impacts of the results, and on their limitations and 
-generalizability.
+Finally, we conclude on the best sampling method to use, and on the 
+impact, limitations and generalizability of the results.
 
@@
 provide ratings through a dedicated system, or implicit, when users' 
-behaviors are tracked and analyzed to estimate their preferences. An 
+behaviors are analyzed to estimate their preferences. An 
 overview of collaborative filtering is provided 
 in~\cite{leskovec2014mining}. In our context, the utility matrix is the
-pipeline matrix $U$ described previously.
+matrix $U$ described previously.
 
@@
         \end{subfigure}
-        \caption{Sample training set for different methods with a training ratio of 0.4.}
+        \caption{Sample training set for different methods with a training ratio of 0.4 (dark elements are in the training set).}
         \label{fig:sampling}
@@
 selected in the training set. This respects the time constraints as files are 
-sampled according to their production time-stamps.
+sampled according to their modification time-stamps.
 
@@
 In each method, we also included the first row of the matrix (first 
-generated file of each subject) and a random column (all files of a 
+ file of each subject) and a random column (all files of a 
 random subject) to avoid cold start issues.
@@
 
-\subsection{Synthetic Data}
+\subsection{Synthetic Dataset}
 
@@
 
-\subsection{Real Data}
+\subsection{Real Dataset}
 
@@
 processed a set S of 94 subjects randomly selected in the S500 HCP 
-release\footnote{\url{https://db.humanconnectome.org}} in three execution conditions with different
-versions of the CentOS operating system (5.11, 6.8 and 7.2), using the
+release\footnote{\url{https://db.humanconnectome.org}} in three 
+execution conditions with different versions of the CentOS operating 
+system (5.11, 6.8 and 7.2 -- referred as C5, C6 and C7), using the 
 PreFreesurfer and Freesurfer pipelines described 
@@
 we computed a binary reproducibility matrix U of size $|F|\times|S|$, 
-where $U_{i,j}$ is true iif file $i$ of subject $j$ was different in 
+where $U_{i,j}$ is true if and only if file $i$ of subject $j$ was different in 
 each condition. Rows of $U$ were ordered by ascending file modification 
@@
   \end{subfigure}
-  \caption{Utility matrices, PreFreesurfer (PFS) and Freesurfer (FS) pipelines}
+  \caption{Utility matrices for PreFreesurfer (PFS) and Freesurfer (FS). White cells denote reproducibility errors.}
     \label{fig:utility-matrices}
@@
 We conducted two experiments for each reproducibility matrix, to evaluate the performance of our 
-predictions using (1) ALS without biases, and (2) ALS with biases. We 
+predictions using (1) ALS without biases, and (2) ALS with subject and file biases. We 
 compare the performance of our sampling methods to (1) a dummy 
@@
 
-\subsection{Synthetic Data}
+\subsection{Accuracy on Synthetic Data}
 
@@
 However, only 3 methods are able to provide accuracy values above 0.85 
-for all subject types: Random Subjects (RS), RFNU and RFNTL. This is 
-due to the fact that these methods are the only ones that can sample 
-files produced toward the end of the execution while maintaining a 
-reduced number of empty columns. Surprisingly, RFNTS does not perform 
-well for more than 2 subject types, even for a training ratio of 0.9.
+for all subject types: Random Subjects (RS), RFNU and RFNTL. 
+Surprisingly, RFNTS does not perform well for more than 2 subject 
+types, even for a training ratio of 0.9.
 
@@
 In such a situation, biases are detrimental to the accuracy of the 
-collaborative filtering process and shouldn't be included.
+collaborative filtering process and should not be included.
 
@@
 
-\subsection{Real Data}
+\subsection{Accuracy on  Real Data}
 
@@
 higher than 0.95 for all datasets, when the training ratio is larger 
-than 0.5. RS and RFNTL are slightly underperforming compared to RFNU. 
+than 0.5. RS and RFNTL are underperforming compared to RFNU. 
 Complete rows and complete columns do not even reach the accuracy of 
@@
 ALS with bias. From a training ratio of 0.5, all methods have a very 
-good accuracy for all datasets, except complete columns in 
+good accuracy for all real datasets, except complete columns in 
 Figure~\ref{fig:pfs-c5vsc7-bias}. All methods except RFNU, RFNTL and 
@@
 \end{tabular}
-\caption{Average sensitivity and specificity values for the 6 synthetic datasets and Freesurfer.}
+\caption{Average sensitivity and specificity values for the 6 synthetic datasets and Freesurfer ($\alpha=0.9$).}
 \label{table:roc}
@@
 
-\subsection{Varying the number of factors}
+\subsection{Effect of the number of factors}
 Figure~\ref{fig:factors} shows the effect of the number of factors used 
 in the ALS optimization for the RFNU method, and the synthetic dataset with 8 types. 
-For training ratios greater or equal than 0.5, the accuracy obtained 
+For training ratios greater than 0.5, the accuracy obtained 
 with 3 factors is substantially higher than with 2 factors. Beyond 
@@
 ratios lower than 0.5, the number of factors does not have any effect 
-on the accuracy, presumably due to the low accuracy of the method.\todo{Soudabeh, check if the factors can be interpreted.}
+on the accuracy.
 
@@
 \includegraphics[width=0.9\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
-\caption{Effect of the number of factors used in ALS, RFNU method, synthetic dataset.}
+\caption{Effect of the number of factors used in ALS, (RFNU, synthetic dataset, 8 types, 5 iterations).}
 \label{fig:factors}
@@
 
- \note{Soudabeh, add figure with two 3D plots showing the 3 factors of 
- every item and subject. Comment: the method indeed separates files in 
- 3 blocks (for 8 types) and subjects in 8 types.}
+Figure~\ref{fig:factors3d} confirms that 3 factors are indeed enough to 
+separate the files of the synthetic dataset with 8 subject types in 3 
+blocks, and the subjects in 8 types.
 
-\subsection{Varying the number of iterations}
+\begin{figure}[h]
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-userFactors.pdf}
+\caption{Subject factors}
+\end{subfigure}
+\begin{subfigure}{\columnwidth}
+\includegraphics[width=0.9\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-itemFactors.pdf}
+\caption{File factors}
+\end{subfigure}
+\caption{Subject and file factors produced by the collaborative filtering method (RFNU, synthetic dataset, 8 types, 3 factors, 5 iterations).}
+\label{fig:factors3d}
+\end{figure}
+
+\subsection{Effect of the number of iterations}
 Figure~\ref{fig:iterations} illustrates the effect of the number of 
@@
 \includegraphics[width=0.9\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Iterations-rank50/ALS-8-types-iteration.pdf}
-\caption{Effect of the number of iterations used in ALS, RFNU method, 50 factors, synthetic dataset.}
+\caption{Effect of the number of iterations used in ALS, (RFNU, synthetic dataset, 8 types, 50 factors).}
 \label{fig:iterations}
@@
 
-\subsection{Error localization}
+\subsection{Prediction error localization}
 
@@
 one included to prevent cold start issues), which leads to a ``stripe" 
-of errors at the bottom of the matrix. RFNTS 
+of prediction errors at the bottom of the matrix. RFNTS 
 (Figure~\ref{fig:overlap-rfnts}) doesn't have this issue, as it 
@@
 \begin{figure*}
-\begin{subfigure}[b]{0.6\columnwidth}
+\begin{subfigure}[b]{0.5\columnwidth}
         \includegraphics[width=\columnwidth]{figures/RFNU_Syn_8_ALS_09_test_data_matrix_run1.png}
@@
 \hfill
-\begin{subfigure}[b]{0.6\columnwidth}
+\begin{subfigure}[b]{0.5\columnwidth}
         \includegraphics[width=\columnwidth]{figures/RFNT-L_Syn_8_ALS_09_test_data_matrix_run2.png}
@@
 \hfill
-\begin{subfigure}[b]{0.6\columnwidth}
+\begin{subfigure}[b]{0.5\columnwidth}
         \includegraphics[width=\columnwidth]{figures/RFNT-S_Syn_8_ALS_09_test_data_matrix_run1.png}
@@
 studied here, the training ratio required to get a 95\% accuracy 
-increases to 0.85 to 0.9.
+increases to 0.85.
 
@@
 The variable of interest in our study was the reproducibility of files 
-produced by the processing of a given subject, and it was controlled by 
+produced by the processing of a given subject. This variable was controlled by 
 a process, the evaluated pipeline. This process was hidden, since we 
-considered the pipeline as a black box (we did not inspect its source 
-code), it was deterministic, since it was implemented as a program, it 
+we did not inspect the pipeline source 
+code, it was deterministic, since it was implemented as a program, it 
 was parametrized, as it behaved differently on different input datasets 

### 2018-08-17 paper.tex
A few fixes. Contracted to 10 pages

@@
 scientific methodology as many researchers acknowledge the existence of 
-a reproducibility crisis~\cite{baker2016there}. Among other factors, 
-such as data and code sharing, infrastructural characteristics 
-play an important role in making experiments reproducible. For instance, in 
+a reproducibility crisis~\cite{baker2016there}. Infrastructural 
+characteristics play an important role in making experiments 
+reproducible, among other factors, such as data and code sharing. For 
+instance, in 
 neuroinformatics, our primary field of interest, several studies have 
@@
 instance due to different pipeline branches being executed depending on 
-the nature, cardinality or content of the input data. As an example, in 
+the input data content. As an example, in 
 the public database released by the Human Connectome 
-Project~\cite{van2013wu}, subjects may have one or two anatomical images of 
-each modality; when two images are 
-present, they are aligned together and averaged. The presence of 
-artifacts, for instance due to high motion during the acquisition, may 
-also trigger corrections that are not otherwise required. Some branches 
-of the pipeline may also be executed only for specific acquisition 
-parameters, for instance the intensity of the magnetic field. To 
-capture all these variations, reproducibility evaluations need to be 
-conducted on many subjects, which is unwieldy.
+Project~\cite{van2013wu}, subjects may have one or two anatomical 
+images of each modality; when two images are present, they are
+aligned together and averaged. Acquisition artifacts, for instance due to motion,
+may also trigger corrections not otherwise required. Some 
+branches of the pipeline may also be executed only for specific 
+acquisition 
+parameters. These remarks are 
+consistent with recent findings that showed that variations in the 
+results of a functional MRI analysis are dependent on the dataset being 
+analyzed~\cite{bowring2018exploring}. To capture such variations, 
+reproducibility evaluations need to be conducted on many subjects, 
+which is unwieldy.
 
@@
 problem lies in the fact that the training set cannot be arbitrarily 
-sampled from the utility matrix. Instead, the training set has to 
-respect the time constraints imposed by the file creation order during 
+sampled from the utility matrix defining the collaborative filtering problem. Instead, the training set has to 
+respect time constraints imposed by the file creation order during 
 pipeline executions.
@@
 \end{enumerate}
-The problem formulation, collaborative filtering technique used, and 
+The problem formulation, collaborative filtering technique, and 
 proposed sampling strategies for the training set are presented in 
 Section~\ref{sec:methods}. The datasets are described in 
-Section~\ref{sec:datasets}, and experimental results are reported in 
+Section~\ref{sec:datasets}, and experimental results are in 
 Section~\ref{sec:results}.
@@
 different subjects, and the $N_f$ rows represent the files produced by 
-the pipeline execution. While subjects are not ordered, files are, for 
+the pipeline. While subjects are not ordered, files are, for 
 instance from their last modification time in a sequential execution, 
@@
 \{U_{i,j}\}$. In contrast with the traditional collaborative filtering 
-problem, (1) we have control over the construction of the training set, 
+problem, we have control over the construction of the training set, 
 for instance we can choose to include only files producde by specific 
 subjects, or the first files produced by the processing of every 
-subject, and (2) the construction of the training set is constrained by 
+subject. Moreover, the construction of the training set is constrained by 
 the 
@@
 
-A third class of methods, which is the one that we will apply to our 
-problem, is based on the factorization of the utility matrix to 
-estimate latent factors along which users and items are represented. 
-This method is described 
-in~\cite{koren2009matrix} and became famous as it contributed to winning the 
+A third class of methods, which is the one that we will use, is based 
+on the factorization of the utility matrix to estimate latent factors 
+along which users and items are represented. This method is described 
+in~\cite{koren2009matrix} and became famous as it contributed to 
+winning the 
 Netflix prize in 2009. To summarize, the method aims at finding $q_i$ 
@@
 involves a regularization term to avoid overfiting particular users or items. The method
-finds $q_i$ and $p_u$ that minimize the following objective:
+finds $q_i$ and $p_u$ that minimize the following objective, where $\lambda$ is the regularization parameter and $\mathbb{T}$ is the training set:
 \begin{equation*}
-\sum_{(i,u) \in \mathbb{T}}\left( r_{ui} - q_i^Tp_u\right)^2+\lambda \left( \|{q_i}\|^2 + \|{p_u}\|^2\right)
-,
+\sum_{(i,u) \in \mathbb{T}}\left( r_{ui} - q_i^Tp_u\right)^2+\lambda \left( \|{q_i}\|^2 + \|{p_u}\|^2\right).
 \end{equation*}
-where $\lambda$ is the regularization parameter and $\mathbb{T}$ is the training set.
 
@@
 the optimization, defined as the average deviation of user $u$ and item 
-$i$ to the global average $\mu$. The goal then becomes to find $q_i$ and $p_u$ that minimize the 
+$i$ to the global average $\mu$. The problem is then to find $q_i$ and $p_u$ that minimize the 
 following objective:
@@
 
-Two good techniques to perform the optimization are stochastic gradient 
-descent and alternating least squares (ALS). In the remainder of this 
-paper, we use matrix factorization as implemented in Apache Spark's 
-MLLib version 2.3.0, which uses ALS. We round predictions to the 
-nearest integer to obtain binary values.
+Stochastic gradient descent and alternating least squares (ALS) are 
+often used as optimization techniques. In the remainder, we use ALS as 
+implemented in Apache Spark's MLLib version 2.3.0. We also round predictions 
+to the nearest integer to obtain binary values.
 
@@
         \begin{subfigure}[b]{0.45\columnwidth}
-                 \includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
+                 \includegraphics[width=\columnwidth]{figures/5vs7_RS_04_training}
                 \caption{Random Subjects (RS)}
@@
         \begin{subfigure}[b]{0.45\columnwidth}
-                  \includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
+                  \includegraphics[width=\columnwidth]{figures/5vs7_RFNU_04_training}
                   \caption{RFNU}
@@
         \begin{subfigure}[b]{0.45\columnwidth}
-                  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
+                  \includegraphics[width=\columnwidth]{figures/5vs7_RFNT-L_04_training}
                   \caption{RFNTL}
@@
         \begin{subfigure}[b]{0.45\columnwidth}
-                  \includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
+                  \includegraphics[width=\columnwidth]{figures/5vs7_RFNT-S_04_training}
                   \caption{RFNTS}
@@
         \end{subfigure}
-        \caption{Sample training set for different methods with a training ratio of 0.4 (dark elements are in the training set).}
+        \caption{Training sets for different sampling methods; $\alpha=0.4$ (dark elements are in the training set).}
         \label{fig:sampling}
@@
  For $\alpha \leq 0.5$, we ensure that the average number of selected 
- files by subject is $\alpha N_f$ by sampling the number of 
- files selected in every subject from $U(0,N_f)$ with 
+ files by subject is $\alpha N_f$, by sampling the number of 
+ files in every subject from $U(0,N_f)$ with 
  probability $2\alpha$, and setting it to 0 otherwise. For $\alpha > 
- 0.5$, this is ensured by the value used for $a$, which leads the 
+ 0.5$, this is ensured by the value of $a$, which leads the 
  average of U(a, b) to be $\alpha N_f$.
@@
 times. This method does not respect the time constraints in 
-Equation~\ref{eq:time}, it will be used as a baseline for comparison 
+Equation~\ref{eq:time}: it will be used as a baseline for comparison 
 with other methods.
@@
 Such a decomposition by subject type correspond to the case where 
-different subjects may have data of different nature, as it is for 
-instance the case in the neuroimaging 
+different subjects may have data of different nature, as is the case in the
 dataset of the Human Connectome Project~\cite{van2013wu} where not all the 
@@
 
- For subjects of a given type, the reproducibility matrix consists of 
+ For subjects of a given type, the matrix consists of 
  $log(n)$  blocks, where $n$ is the number of types. Blocks are 
- arranged with all the possible variation patterns: some types do not 
- vary at all, while other ones vary in every block. Such variation 
+ defined with all the possible variation patterns: some types do not 
+ vary at all, while other ones vary in every block. Such 
  patterns are meant to mimic the logic of data 
-processing pipelines: each block of files represents the files produced 
+processing pipelines. Each block of files represents the files produced 
 at a given stage of the pipeline, which may or may not contain 
@@
 
-Figure~\ref{fig:utility-matrices} shows the utility matrices
-obtained for the PreFreesurfer and Freesufer pipeline. The computational
+Figure~\ref{fig:utility-matrices} shows the matrices
+for PreFreesurfer and Freesufer. The
 reproducibility of these pipelines varies across subjects,
-but some files behave
+but most files behave
 consistently across all subjects, leading to complete black or white
@@
 \section{Results}
-
 \label{sec:results}
-
 We conducted two experiments for each reproducibility matrix, to evaluate the performance of our 
@@
 regularization parameter of 0.01, a maximum of 5 iterations and non 
-negative constraints set to true.
+negative constraints set to true. The code and data used to obtain the results are available through GitHub at
+\url{https://github.com/big-data-lab-team/paper-reproducibility-collaborative-filtering}.
+\todo{Soudabeh: push your code to reprotools. Tristan: release and check.}
+\todo{publish code on zenodo}
 
@@
  without bias. By construction, the accuracy of the dummy classifier is 
- close to 0.5 for all subject types. Random Unreal performs very well 
+ close to 0.5 for all subject types. Random Unreal performs well 
  for all subject types, which confirms that ALS is working correctly. 
- Unsurprisingly, all the other methods 
+ All the other methods 
 perform better than the dummy classifier, and their accuracy decreases 
 as the number of subject types increases.
-
-However, only 3 methods are able to provide accuracy values above 0.85 
+However, only 3 methods provide accuracy values above 0.85 
 for all subject types: Random Subjects (RS), RFNU and RFNTL. 
 Surprisingly, RFNTS does not perform well for more than 2 subject 
-types, even for a training ratio of 0.9.
+types, even for $\alpha=0.9$.
 
@@
 ALS with bias. RS, RFNU and RFNTL remain the methods that best compare 
-to Random Unreal, but the achieved accuracy is much lower than without 
+to Random Unreal, but their accuracy is much lower than without 
 biases. This is presumably due to 
-the fact that file biases are all close to 0.5 in the synthetic data. 
-In such a situation, biases are detrimental to the accuracy of the 
-collaborative filtering process and should not be included.
+the fact that file biases are all close to 0.5. 
+In such a situation, biases are detrimental and should not be included.
 
@@
 
-Figure~\ref{fig:results-real-als} shows the accuracy results for ALS without bias. Among the methods that performed 
+Figure~\ref{fig:results-real-als} shows the accuracy for ALS without bias. Among the methods that performed 
 well in the synthetic dataset, RFNU performs the best, with an accuracy 
-higher than 0.95 for all datasets, when the training ratio is larger 
-than 0.5. RS and RFNTL are underperforming compared to RFNU. 
-Complete rows and complete columns do not even reach the accuracy of 
-the dummy classifier. The reference method, Random Unreal, has an 
+higher than 0.95 for all datasets when the training ratio is larger 
+than 0.5. Complete rows and complete columns do not reach the accuracy of 
+the dummy classifier. Random Unreal has an 
 accuracy close to 1, which shows that collaborative filtering works 
@@
 
-Figure~\ref{fig:results-real-als-bias} shows the accuracy results for 
-ALS with bias. From a training ratio of 0.5, all methods have a very 
-good accuracy for all real datasets, except complete columns in 
+Figure~\ref{fig:results-real-als-bias} shows the accuracy for ALS with 
+bias. From a training ratio of 0.5, all methods perform well for all 
+datasets, except complete columns in 
 Figure~\ref{fig:pfs-c5vsc7-bias}. All methods except RFNU, RFNTL and 
 RFNTS also perform well for a training ratio lower than 0.5. Overall, 
-the accuracy of the methods is much higher than without bias, due to 
-the fact that the file bias is very strong in this dataset, as 
-it can be seen in Figure~\ref{fig:utility-matrices}.
+the accuracy is much higher than without bias, due to the fact that the 
+file biases are very strong. In the remainder, all the 
+results are obtained using ALS without bias.
 
@@
 \includegraphics[width=\columnwidth]{data/results/roc/roc-closeup.pdf}
-\caption{Comparison of the sampling methods in the ROC space for the 6 synthetic datasets and Freesurfer. Right: entire dataset. Left: close-up on the top-left part.}
+\caption{Comparison of the sampling methods in the ROC space for the 6 synthetic datasets and Freesurfer (ALS without bias). Right: entire dataset. Left: close-up on the top-left part.}
 \label{fig:roc}
@@
 \end{tabular}
-\caption{Average sensitivity and specificity values for the 6 synthetic datasets and Freesurfer ($\alpha=0.9$).}
+\caption{Average sensitivity and specificity for the synthetic datasets and Freesurfer ($\alpha=0.9$, ALS without bias).}
 \label{table:roc}
@@
 
-\subsection{Effect of the number of factors}
-Figure~\ref{fig:factors} shows the effect of the number of factors used 
-in the ALS optimization for the RFNU method, and the synthetic dataset with 8 types. 
-For training ratios greater than 0.5, the accuracy obtained 
-with 3 factors is substantially higher than with 2 factors. Beyond 
-3, the number of factors does not have an effect on the accuracy. 
-This shows that the data is best explained by 3 factors. For training 
-ratios lower than 0.5, the number of factors does not have any effect 
-on the accuracy.
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
-\caption{Effect of the number of factors used in ALS, (RFNU, synthetic dataset, 8 types, 5 iterations).}
-\label{fig:factors}
-\end{figure}
-
-Figure~\ref{fig:factors3d} confirms that 3 factors are indeed enough to 
-separate the files of the synthetic dataset with 8 subject types in 3 
+\subsection{Effect of the number of factors} Figure~\ref{fig:factors} 
+shows the effect of the number of factors used in the ALS optimization 
+for the RFNU method and the synthetic dataset with 8 subject types (3 
+blocks of files). For training ratios greater than 0.5, the accuracy 
+with 3 factors is substantially higher than with 2 factors. Beyond 3, 
+the number of factors does not have any effect, which shows that the 
+data is best 
+explained by 3 factors. Figure~\ref{fig:factors3d} confirms that 3 
+factors are enough to separate the files of this dataset in 3 
 blocks, and the subjects in 8 types.
 
-\begin{figure}[h]
-\begin{subfigure}{\columnwidth}
-\includegraphics[width=0.9\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-userFactors.pdf}
-\caption{Subject factors}
-\end{subfigure}
-\begin{subfigure}{\columnwidth}
-\includegraphics[width=0.9\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-itemFactors.pdf}
-\caption{File factors}
-\end{subfigure}
-\caption{Subject and file factors produced by the collaborative filtering method (RFNU, synthetic dataset, 8 types, 3 factors, 5 iterations).}
-\label{fig:factors3d}
-\end{figure}
-
-\subsection{Effect of the number of iterations}
+\subsection{Effect of the maximum number of iterations}
 Figure~\ref{fig:iterations} illustrates the effect of the number of 
 iterations used in the ALS optimization, for the 
-RFNU method, the synthetic dataset with 8 types, and 50 factors.
-
+RFNU method and the synthetic dataset with 8 types. 
 From a training ratio of 0.7, the number of iterations has a moderate 
-effect on the accuracy. Our previous experiments used 5 iterations, 
-which only degrades the accuracy slightly compared to 15 or 20 iterations.
-
-\begin{figure}[h]
-\includegraphics[width=0.9\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Iterations-rank50/ALS-8-types-iteration.pdf}
-\caption{Effect of the number of iterations used in ALS, (RFNU, synthetic dataset, 8 types, 50 factors).}
-\label{fig:iterations}
-\end{figure}
+effect on the accuracy. We used 5 iterations in our experiments, 
+which slightly degrades the accuracy compared to 15 or 20.
 
@@
 Figure~\ref{fig:overlap} compares the prediction errors made by RFNU, 
-RFNTL and RFNTS. The matrices in this Figure represent the training set 
-in black (negatives) and white (positives), and the test set in green 
+RFNTL and RFNTS. The training set is represented
+in black (negatives) and white (positives), and the test set is in green 
 (true positives), yellow (false negatives), gray (true negatives) and 
@@
 
-\begin{figure*}
-\begin{subfigure}[b]{0.5\columnwidth}
-        \includegraphics[width=\columnwidth]{figures/RFNU_Syn_8_ALS_09_test_data_matrix_run1.png}
-        \caption{RFNU: $U(0.8N_f, N_f)$}
-        \label{fig:overlap-rfnu}
-\end{subfigure}
-\hfill
-\begin{subfigure}[b]{0.5\columnwidth}
-        \includegraphics[width=\columnwidth]{figures/RFNT-L_Syn_8_ALS_09_test_data_matrix_run2.png}
-        \caption{RFNTL: $T(0.85N_f, 0.85N_f, N_f)$}
-        \label{fig:overlap-rfntl}
-\end{subfigure}
-\hfill
-\begin{subfigure}[b]{0.5\columnwidth}
-        \includegraphics[width=\columnwidth]{figures/RFNT-S_Syn_8_ALS_09_test_data_matrix_run1.png}
-        \caption{RFNTS: 0.3$T(0, N_f, N_f)$+0.7$N_f$}
-        \label{fig:overlap-rfnts}
-\end{subfigure}
-\caption{Comparison between RFNU, RFNTL and RFNTS on synthetic dataset with 8 types, $\alpha=0.9$.}
-\label{fig:overlap}
-\end{figure*}
-
 Figure~\ref{fig:error-locality} shows the results obtained by RFNU on 
@@
 black or entirely white.
-\begin{figure}
-\centering
-\includegraphics[width=0.55\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
-\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
-\label{fig:error-locality}
-\end{figure}
 
@@
 % Which method is the best
-While collaborative filtering, perhaps unsurprisingly, is able to 
-correctly predict the missing values in a matrix modeling the 
-reproducibility problem, the usual random sampling method cannot be 
-used in time-constrained processes. We proposed 6 sampling methods to 
-address this issue, and we found that one of them, RFNU, performs 
+While collaborative filtering, perhaps unsurprisingly, correctly 
+predicts the missing values in a matrix modeling reproducibility 
+evaluations, the usual random sampling method cannot be used in 
+time-constrained processes. We proposed 6 sampling methods to address 
+this issue, and we found that one of them, RFNU, performs 
 better than the other ones on average. We 
@@
 continuum of 
-intermediate configurations. On the contrary, other sampling 
+intermediate configurations. On the contrary, other 
 methods, including RFNTL and RFNTS, bias the sampling toward complete 
@@
 For datasets that are strongly dependent on row bias, such as the 
-PreFreesurfer and Freesurfer datasets studied here, RFNU provides 
-accuracy values that are consistently higher than 0.95 for training 
+PreFreesurfer and Freesurfer ones, RFNU provides 
+accuracy values consistently higher than 0.95 for training 
 ratios higher than 0.5, even 
-when biases are not included in the collaborative filtering 
-optimization. For the synthetic dataset, RFNU still performs very well 
+when biases are not included. For the synthetic dataset, RFNU still performs very well 
 when biases are not included, but it does very poorly when biases are included.
-For this reason, we recommend not to include biases in the collaborative filtering 
+For this reason, we recommend to not include biases in the collaborative filtering 
 optimization to solve this problem. Even though biases provide a slight 
@@
 evaluations of the PreFreesurfer and Freesurfer pipelines can be 
-conducted using only 50\% of the files produced by the evaluated 
-pipelines, with an accuracy above 95\%. Potentially, this could reduce 
-the computing time and storage required for such studies by a factor of 
-2. However, such studies could not be conducted by processing only half 
-of the subjects entirely, which would correspond to the Complete 
-Columns sampling method. Instead, the processing of all the subjects 
-should be initiated, and it should be terminated in a random uniform 
-way, assuming that files are uniformly produced throughout the 
-execution. On more complex matrices, such as the synthetic dataset 
-studied here, the training ratio required to get a 95\% accuracy 
-increases to 0.85.
+conducted using only 50\% of the files produced, with an accuracy above 
+95\%. Potentially, this could reduce the computing time and storage 
+required for such studies by a factor of 2. However, such studies could 
+not be conducted by processing only half of the subjects entirely, 
+which would correspond to the Complete Columns sampling method. 
+Instead, the processing of all the subjects should be initiated, and it 
+should be terminated in a random uniform way, assuming that files are 
+uniformly produced throughout the execution. On more complex matrices, 
+such as the synthetic dataset studied here, the training ratio required 
+to get a 95\% accuracy increases to 0.85.
 
 % What are the limitations
-Our study could be extended by considering real-valued reproducibility 
+Our study could be extended to real-valued reproducibility 
 matrices instead of just binary ones. It is indeed common for file 
@@
 % Other possible examples
-The variable of interest in our study was the reproducibility of files 
-produced by the processing of a given subject. This variable was controlled by 
-a process, the evaluated pipeline. This process was hidden, since we 
-we did not inspect the pipeline source 
-code, it was deterministic, since it was implemented as a program, it 
-was parametrized, as it behaved differently on different input datasets 
-and parameters, and it was time-dependent, as the value of the 
-variable of interest varied throughout the course of the pipeline 
-execution. The method described in this paper could possibly be used to 
-predict other variables controlled by such hidden, deterministic, 
-parametrized, and time-dependent processes, for instance markers of 
-chronic disease activity.
+%~ In our study, the variable of interest was the reproducibility of files 
+%~ produced for a given subject. This variable was controlled by 
+%~ a process, the evaluated pipeline. This process was hidden, since we 
+%~ we did not inspect the pipeline source 
+%~ code, it was deterministic, since it was implemented as a program, it 
+%~ was parametrized, as it behaved differently on different input datasets 
+%~ and parameters, and it was time-dependent, as the value of the 
+%~ variable of interest varied throughout the course of the pipeline 
+%~ execution.
 
-The code and data used in this paper are available at 
-\url{https://github.com/big-data-lab-team/paper-reproducibility-collaborative-filtering}.
-
-\todo{Soudabeh: push your code to reprotools. Tristan: release and check.}
-
-\todo{publish code on zenodo}
+Finally, the method described in this paper could possibly be used to predict 
+the outcome of other time-constrained processes, for instance 
+markers of chronic disease activity.
 
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.6\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
+\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
+\label{fig:error-locality}
+\end{figure}
+
+\newpage
+
+\onecolumn
+
+\begin{figure}
+\begin{minipage}{0.45\textwidth}
+\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
+\caption{Effect of the number of factors used in ALS, (RFNU, synthetic dataset, 8 types, 5 iterations).}
+\label{fig:factors}
+\end{minipage}\hfill
+\begin{minipage}{0.45\textwidth}
+\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Iterations-rank50/ALS-8-types-iteration.pdf}
+\caption{Effect of the number of iterations used in ALS, (RFNU, synthetic dataset, 8 types, 50 factors).}
+\label{fig:iterations}
+\end{minipage}
+\end{figure}
+
+\begin{figure*}
+\begin{subfigure}{0.5\columnwidth}
+\includegraphics[width=\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-userFactors.pdf}
+\caption{Subject factors}
+\end{subfigure}
+\hfill
+\begin{subfigure}{0.5\columnwidth}
+\includegraphics[width=\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-itemFactors.pdf}
+\caption{File factors}
+\end{subfigure}
+\caption{Subject and file factors produced by collaborative filtering (RFNU, synthetic dataset, 8 types, 3 factors, 5 iterations).}
+\label{fig:factors3d}
+\end{figure*}
+
+\begin{figure*}
+\begin{subfigure}[b]{0.3\columnwidth}
+        \includegraphics[width=\columnwidth]{figures/RFNU_Syn_8_ALS_09_test_data_matrix_run1.png}
+        \caption{RFNU: $U(0.8N_f, N_f)$}
+        \label{fig:overlap-rfnu}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.3\columnwidth}
+        \includegraphics[width=\columnwidth]{figures/RFNT-L_Syn_8_ALS_09_test_data_matrix_run2.png}
+        \caption{RFNTL: $T(0.85N_f, 0.85N_f, N_f)$}
+        \label{fig:overlap-rfntl}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.3\columnwidth}
+        \includegraphics[width=\columnwidth]{figures/RFNT-S_Syn_8_ALS_09_test_data_matrix_run1.png}
+        \caption{RFNTS: 0.3$T(0, N_f, N_f)$+0.7$N_f$}
+        \label{fig:overlap-rfnts}
+\end{subfigure}
+\caption{Comparison between RFNU, RFNTL and RFNTS on synthetic dataset with 8 types, $\alpha=0.9$.}
+\label{fig:overlap}
+\end{figure*}
+
 \end{document}

### 2018-08-17 paper.tex
Minor fixes

@@
 \begin{abstract}
-With the rise of the reproducibility crisis, evaluating the 
+Evaluating the 
 computational reproducibility of data analysis pipelines has become a 
@@
 
-Computational reproducibility, the ability to recompute data analyses 
+Computational reproducibility, the ability to recompute analyses 
 over time and 
@@
 scientific methodology as many researchers acknowledge the existence of 
-a reproducibility crisis~\cite{baker2016there}. Infrastructural 
+a reproducibility crisis~\cite{baker2016there}. Among other factors, infrastructural 
 characteristics play an important role in making experiments 
-reproducible, among other factors, such as data and code sharing. For 
+reproducible. For 
 instance, in 
-neuroinformatics, our primary field of interest, several studies have 
+neuroinformatics, our primary field of interest, studies have 
 shown the effect of the 
@@
 However, conducting such reproducibility studies at scale is cumbersome 
-due to the computational and storage requirements of data analysis 
+due to the computational and storage requirements of analysis 
 pipelines.
@@
 associated with a subject may vary, and these files may also be of 
-different sizes. Typical data processing times range from 15 minutes to 
+different sizes. Typical processing times range from 15 minutes to 
 15 hours per subject, with input ranging from 100~MB to 15~GB per subject, and 
@@
 aligned together and averaged. Acquisition artifacts, for instance due to motion,
-may also trigger corrections not otherwise required. Some 
-branches of the pipeline may also be executed only for specific 
+may also trigger corrections not otherwise required, and some 
+branches of the pipeline may be executed only for specific 
 acquisition 
 parameters. These remarks are 
-consistent with recent findings that showed that variations in the 
+consistent with recent findings showing that variations in the 
 results of a functional MRI analysis are dependent on the dataset being 
@@
 \{U_{i,j}\}$. In contrast with the traditional collaborative filtering 
-problem, we have control over the construction of the training set, 
-for instance we can choose to include only files producde by specific 
+problem, we have control over the construction of the training set. 
+For instance, we can choose to include only files produced by specific 
 subjects, or the first files produced by the processing of every 
@@
 the 
-order on the matrix rows, which is formalized as follows: 
+order of the matrix rows, which is formalized as follows: 
 \begin{equation}
@@
         \end{subfigure}
-        \caption{Training sets for different sampling methods; $\alpha=0.4$ (dark elements are in the training set).}
+        \caption{Training sets for different sampling methods, $\alpha=0.4$ (dark elements are in the training set).}
         \label{fig:sampling}
@@
 with the lowest index in this subject that has not been already 
-selected in the training set. This respects the time constraints as files are 
-sampled according to their modification time-stamps.
+selected in the training set, which respects the time constraints.
 
@@
  For $\alpha \leq 0.5$, we ensure that the average number of selected 
- files by subject is $\alpha N_f$, by sampling the number of 
+ files by subject is $\alpha N_f$ by sampling the number of 
  files in every subject from $U(0,N_f)$ with 
@@
 As illustrated in Figures~\ref{fig:triangular-L-Sample-Training-set} 
-and~\ref{fig:triangular-S-Sample-Training-set}, the motivation for the 
+and~\ref{fig:triangular-S-Sample-Training-set}, the point of the 
 RFNTL method is to guarantee that, for large enough values of 
@@
 ~\ref{fig:Random-Unreal-Sample-Training-set})} The training set is 
-sampled in a random uniform way, regardless of the file generation 
+sampled in a random uniform way, regardless of the file creation 
 times. This method does not respect the time constraints in 
-Equation~\ref{eq:time}: it will be used as a baseline for comparison 
-with other methods.
+Equation~\ref{eq:time}: it will be used as a baseline for comparison.
 
@@
 identically and all types contain the same number of subjects $\pm$ 1. 
-Such a decomposition by subject type correspond to the case where 
+Such a decomposition by subject type corresponds to a situation where 
 different subjects may have data of different nature, as is the case in the
-dataset of the Human Connectome Project~\cite{van2013wu} where not all the 
+Human Connectome Project data~\cite{van2013wu} where not all the 
 subjects have the same amount of images.
@@
  defined with all the possible variation patterns: some types do not 
- vary at all, while other ones vary in every block. Such 
+ vary at all, while other ones vary between every block. Such 
  patterns are meant to mimic the logic of data 
-processing pipelines. Each block of files represents the files produced 
+processing pipelines: each block of files represents the files produced 
 at a given stage of the pipeline, which may or may not contain 
@@
 
-We collected data to evaluate the computational reproducibility of analysis
-pipelines of the Human Connectome Project~\cite{glasser2013minimal}. We
+We
 processed a set S of 94 subjects randomly selected in the S500 HCP 
-release\footnote{\url{https://db.humanconnectome.org}} in three 
-execution conditions with different versions of the CentOS operating 
-system (5.11, 6.8 and 7.2 -- referred as C5, C6 and C7), using the 
+release\footnote{\url{https://db.humanconnectome.org}} of the Human 
+Connectome Project~\cite{glasser2013minimal}, in three execution 
+conditions with different versions of the CentOS operating system 
+(5.11, 6.8 and 7.2 -- referred as C5, C6 and C7), using the 
 PreFreesurfer and Freesurfer pipelines described 
@@
 we computed a binary reproducibility matrix U of size $|F|\times|S|$, 
-where $U_{i,j}$ is true if and only if file $i$ of subject $j$ was different in 
-each condition. Rows of $U$ were ordered by ascending file modification 
-time in a random subject in S.
+where $U_{i,j}$ is true if and only if file $i$ of subject $j$ was 
+different in each condition. Rows of $U$ were ordered by ascending file 
+modification time in a random subject in S.
 
@@
 issues, it is possible that the actual training ratio obtained with 
-some of the sampling methods does not 
+some of the sampling methods does not exactly
 match the target one. We checked that the difference between the target 
 and real training ratios was lower than 0.01. We used Spark's ALS model 
-as available in package \texttt{pyspark.ml}, with 50 factors, a 
+as available in \texttt{pyspark.ml}, with 50 factors, a 
 regularization parameter of 0.01, a maximum of 5 iterations and non 
@@
 as the number of subject types increases.
-However, only 3 methods provide accuracy values above 0.85 
+However, only 3 methods can provide accuracy values above 0.85 
 for all subject types: Random Subjects (RS), RFNU and RFNTL. 
@@
 effect on the accuracy. We used 5 iterations in our experiments, 
-which slightly degrades the accuracy compared to 15 or 20.
+which only slightly degrades the accuracy compared to 15 or 20.
 
@@
 of prediction errors at the bottom of the matrix. RFNTS 
-(Figure~\ref{fig:overlap-rfnts}) doesn't have this issue, as it 
+(Figure~\ref{fig:overlap-rfnts}) does not have this issue, as it 
 includes many complete columns in the training set. However, it comes at 
@@
 
-Figure~\ref{fig:error-locality} shows the results obtained by RFNU on 
+Figure~\ref{fig:error-locality} shows the RFNU results on 
 the Freesurfer dataset for a training ratio of 0.6. The prediction 
@@
 reproducibility varies across subjects, i.e., lines are not entirely 
-black or entirely white.
+black or entirely white. This is consistent with our expectations and 
+confirms the validity of our results.
 
@@
 not be conducted by processing only half of the subjects entirely, 
-which would correspond to the Complete Columns sampling method. 
-Instead, the processing of all the subjects should be initiated, and it 
-should be terminated in a random uniform way, assuming that files are 
-uniformly produced throughout the execution. On more complex matrices, 
-such as the synthetic dataset studied here, the training ratio required 
+which would correspond to the complete columns sampling method. 
+Instead, the processing of all the subjects should be initiated and 
+terminated in a random uniform way, assuming that files are uniformly 
+produced throughout the execution. On more complex matrices, such as 
+the synthetic dataset studied here, the training ratio required 
 to get a 95\% accuracy increases to 0.85.
@@
 differences to be quantified using specific similarity measures or 
-distances, such as Levenshtein distance between strings, or the sum of 
-squared distances between voxels of an image. Our sampling methods 
+distances, such as the Levenshtein distance between strings, or the sum of 
+squared distances among voxels of an image. Our sampling methods 
 could be directly applied to real-valued matrices, and we expect our 
-conclusions regarding the best-performing sampling method (RFNU) and 
+conclusions on the best-performing sampling method (RFNU) and 
 the inclusion of biases in the model to remain valid.

### 2018-08-17 paper.tex
Release 0.1!
Added Ali as co-author as he helped produce the data

@@
 
-\author{Soudabeh Barghi, Lalet Scaria, Tristan Glatard\\
-  Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada\\
-  {first.last}@concordia.ca \vspace*{-0.5cm}}
+\author{Soudabeh Barghi, Lalet Scaria, Ali Salari, Tristan Glatard\\
+  Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada}
 
@@
 \url{https://github.com/big-data-lab-team/paper-reproducibility-collaborative-filtering}.
-\todo{Soudabeh: push your code to reprotools. Tristan: release and check.}
-\todo{publish code on zenodo}
 
@@
 %~ FP is the number of False Positives, TN is the number of true negatives 
-%~ and FN is the number of false negatives. \todo{Check if we want to report sensitivity and specificity, otherwise remove.}
+%~ and FN is the number of false negatives.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
+\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
+\label{fig:error-locality}
+\end{figure}
+
 \section*{Acknowledgement}
@@
 \bibliography{IEEEabrv,biblio.bib}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.6\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
-\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
-\label{fig:error-locality}
-\end{figure}
 

### 2018-11-11 paper.tex
Final version uploaded for IEEE BigData

@@
 }
+\newcommand{\english}[1]{\uwave{#1}}
 
@@
         %\end{subfigure}
-        \begin{subfigure}[b]{0.45\columnwidth}
+        \begin{subfigure}[b]{0.3\columnwidth}
                   \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/2_SubjectType_utility_matrix.png}
@@
         \end{subfigure}
-        \begin{subfigure}[b]{0.45\columnwidth}
-                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/4_SubjectType_utility_matrix.png}
-                  \caption{4 types}
-        \end{subfigure}
-                \begin{subfigure}[b]{0.45\columnwidth}
+                \begin{subfigure}[b]{0.3\columnwidth}
                   \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/8_SubjectType_utility_matrix.png}
@@
         \end{subfigure}
-                \begin{subfigure}[b]{0.45\columnwidth}
-                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/16_SubjectType_utility_matrix.png}
-                  \caption{16 types}
-        \end{subfigure}
-                \begin{subfigure}[b]{0.45\columnwidth}
-                  \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/32_SubjectType_utility_matrix.png}
-                  \caption{32 types}
-        \end{subfigure}
-                \begin{subfigure}[b]{0.45\columnwidth}
+                \begin{subfigure}[b]{0.3\columnwidth}
                   \includegraphics[width=\columnwidth]{data/Utility_Matrix/Synthetic/synthetic_subject_types/64_SubjectType_utility_matrix.png}
@@
 release\footnote{\url{https://db.humanconnectome.org}} of the Human 
-Connectome Project~\cite{glasser2013minimal}, in three execution 
+Connectome Project~\cite{glasser2013minimal}, in two execution 
 conditions with different versions of the CentOS operating system 
-(5.11, 6.8 and 7.2 -- referred as C5, C6 and C7), using the 
+(6.8 and 7.2 -- referred as C6 and C7), using the 
 PreFreesurfer and Freesurfer pipelines described 
@@
   \begin{subfigure}[b]{0.45\columnwidth}
-        \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v6_utility_matrix.png}
-  \caption{PFS, C5 vs C6}
+        \includegraphics[width=0.8\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_6v7_utility_matrix.png}
+  \caption{PFS}
   \end{subfigure}
   \begin{subfigure}[b]{0.45\columnwidth}
-         \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_5v7_utility_matrix.png}
-  \caption{PFS, C5 vs C7}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.45\columnwidth}
-        \includegraphics[width=\columnwidth]{data/Utility_Matrix/PreFreeSurfer/PFS_6v7_utility_matrix.png}
-  \caption{PFS, C6 vs C7}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.45\columnwidth}
-        \includegraphics[width=\columnwidth]{data/Utility_Matrix/FS-100files/FS-First-bound-100files.png}
-  \caption{FS (100 files), C6 vs C7}
+        \includegraphics[width=0.8\columnwidth]{data/Utility_Matrix/FS-100files/FS-First-bound-100files.png}
+  \caption{FS (100 files)}
   \end{subfigure}
@@
 \begin{figure*}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-2-types.pdf}
+\begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-2-types.pdf}
         \caption{2 subject types}
 \end{subfigure}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-4-types.pdf}
-        \caption{4 subject types}
-\end{subfigure}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-8-types.pdf}
+\hfill
+\begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-8-types.pdf}
         \caption{8 subject types}
 \end{subfigure}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-16-types.pdf}
-        \caption{16 subject types}
-\end{subfigure}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-32-types.pdf}
-        \caption{32 subject types}
-\end{subfigure}
 \hfill
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-64-types.pdf}
+\begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS/Synthetic/synthetic_subject_types/ALS-64-types.pdf}
         \caption{64 subject types}
@@
 \label{fig:results-synthetic}
+\end{figure*}
+\begin{figure*}
+\centering
+\begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-2-types.pdf}
+        \caption{2 subject types}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-8-types.pdf}
+        \caption{8 subject types}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-64-types.pdf}
+        \caption{64 subject types}
+\end{subfigure}
+\caption{Accuracy results on synthetic data, ALS \emph{with} bias.}
+\label{fig:results-synthetic-als-bias}
 \end{figure*}
@@
 In such a situation, biases are detrimental and should not be included.
-
-\begin{figure*}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-2-types.pdf}
-        \caption{2 subject types}
-\end{subfigure}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-4-types.pdf}
-        \caption{4 subject types}
-\end{subfigure}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-8-types.pdf}
-        \caption{8 subject types}
-\end{subfigure}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-16-types.pdf}
-        \caption{16 subject types}
-\end{subfigure}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-32-types.pdf}
-        \caption{32 subject types}
-\end{subfigure}
-\hfill
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/Synthetic/synthetic_subject_types/ALS-Bias-64-types.pdf}
-        \caption{64 subject types}
-\end{subfigure}
-\caption{Accuracy results on synthetic data, ALS \emph{with} bias.}
-\label{fig:results-synthetic-als-bias}
-\end{figure*}
 
@@
 
-\begin{figure*}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v6.pdf}
-        \caption{PFS, CentOS5 vs CentOS6}
-\end{subfigure}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-5v7.pdf}
-        \caption{PFS, CentOS5 vs CentOS7}
-\end{subfigure}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-6v7.pdf}
-        \caption{PFS, CentOS6 vs CentOS7}
+\begin{figure}
+\begin{subfigure}[b]{0.5\columnwidth}
+        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS/PreFreeSurfer/ALS-PFS-6v7.pdf}
+        \caption{PFS}
 \end{subfigure}\hfill
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS/FS-100files/ALS-FS100files.pdf}
-        \caption{FS, CentOS6 vs CentOS7}
+\begin{subfigure}[b]{0.5\columnwidth}
+        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS/FS-100files/ALS-FS100files.pdf}
+        \caption{FS}
 \end{subfigure}
@@
 \label{fig:results-real-als}
-\end{figure*}
+\end{figure}
 
@@
 bias. From a training ratio of 0.5, all methods perform well for all 
-datasets, except complete columns in 
-Figure~\ref{fig:pfs-c5vsc7-bias}. All methods except RFNU, RFNTL and 
+datasets. All methods except RFNU, RFNTL and 
 RFNTS also perform well for a training ratio lower than 0.5. Overall, 
@@
 
-\begin{figure*}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v6.pdf}
-        \caption{PFS, CentOS5 vs CentOS6}
-\end{subfigure}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-5v7.pdf}
-        \caption{PFS, CentOS5 vs CentOS7}
-        \label{fig:pfs-c5vsc7-bias}
-\end{subfigure}
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-6v7.pdf}
-        \caption{PFS, CentOS6 vs CentOS7}
+\begin{figure}
+\centering
+\begin{subfigure}[b]{0.5\columnwidth}
+        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS-Bias/PreFreeSurfer/ALS-Bias-PFS-6v7.pdf}
+        \caption{PFS}
 \end{subfigure}\hfill
-\begin{subfigure}[b]{\columnwidth}
-        \includegraphics[width=0.8\columnwidth]{data/results/means_of_results/ALS-Bias/FS-100files/ALS-Bias-FS100files.pdf}
-        \caption{FS, CentOS6 vs CentOS7}
+\begin{subfigure}[b]{0.5\columnwidth}
+        \includegraphics[width=\textwidth]{data/results/means_of_results/ALS-Bias/FS-100files/ALS-Bias-FS100files.pdf}
+        \caption{FS}
 \end{subfigure}
@@
 \label{fig:results-real-als-bias}
-\end{figure*}
+\end{figure}
 
@@
 performing method on average.
-
-\begin{figure*}
-\includegraphics[width=\columnwidth]{data/results/roc/roc.pdf}
-\includegraphics[width=\columnwidth]{data/results/roc/roc-closeup.pdf}
-\caption{Comparison of the sampling methods in the ROC space for the 6 synthetic datasets and Freesurfer (ALS without bias). Right: entire dataset. Left: close-up on the top-left part.}
+\begin{figure}
+\centering
+\includegraphics[width=0.5\columnwidth]{data/results/roc/roc.pdf}\hfill
+\includegraphics[width=0.5\columnwidth]{data/results/roc/roc-closeup.pdf}
+\caption{Comparison of the sampling methods in the ROC space for the 3 synthetic datasets and Freesurfer (ALS without bias). Right: entire dataset. Left: close-up on the top-left part.}
 \label{fig:roc}
-\end{figure*}
-
+\end{figure}
 \begin{table}
@@
 \hline
-Complete Columns & 0.53 & 0.97\\
-Complete Rows & 0.43 & 0.89\\
-Random Subjects & 0.88 & 0.99\\
-RFNU & 0.92 & 0.99 \\
-RFNTL & 0.81 & 0.97\\
-RFNTS & 0.65 & 0.93 \\
-Random Unreal & 1 & 1
+Complete Columns & 0.63 & 0.99\\
+Complete Rows & 0.50 & 0.91\\
+Random Subjects & 0.89 & 0.98\\
+RFNU & 0.90 & 0.98 \\
+RFNTL & 0.82 & 0.97\\
+RFNTS & 0.72 & 0.94 \\
+Random Unreal & 1.00 & 0.99
 \end{tabular}
@@
 \end{table}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.6\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
+\caption{Effect of the number of factors used in ALS, (RFNU, synthetic dataset, 8 types, 5 iterations).}
+\label{fig:factors}
+\end{figure}
+\begin{figure}
+\begin{subfigure}{0.5\columnwidth}
+\includegraphics[width=\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-userFactors.pdf}
+\caption{Subject factors}
+\end{subfigure}\hfill
+\begin{subfigure}{0.5\columnwidth}
+\includegraphics[width=\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-itemFactors.pdf}
+\caption{File factors}
+\end{subfigure}
+\caption{Subject and file factors produced by collaborative filtering (RFNU, synthetic dataset, 8 types, 3 factors, 5 iterations).}
+\label{fig:factors3d}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.6\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Iterations-rank50/ALS-8-types-iteration.pdf}
+\caption{Effect of the number of iterations used in ALS, (RFNU, synthetic dataset, 8 types, 50 factors).}
+\label{fig:iterations}
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}[b]{0.4\columnwidth}
+        \includegraphics[width=\columnwidth]{figures/RFNU_Syn_8_ALS_09_test_data_matrix_run1.png}
+        \caption{RFNU: $U(0.8N_f, N_f)$}
+        \label{fig:overlap-rfnu}
+\end{subfigure}\\
+\begin{subfigure}[b]{0.4\columnwidth}
+        \includegraphics[width=\columnwidth]{figures/RFNT-L_Syn_8_ALS_09_test_data_matrix_run2.png}
+        \caption{RFNTL: $T(0.85N_f, 0.85N_f, N_f)$}
+        \label{fig:overlap-rfntl}
+\end{subfigure}\\
+\begin{subfigure}[b]{0.4\columnwidth}
+        \includegraphics[width=\columnwidth]{figures/RFNT-S_Syn_8_ALS_09_test_data_matrix_run1.png}
+        \caption{RFNTS: 0.3$T(0, N_f, N_f)$+0.7$N_f$}
+        \label{fig:overlap-rfnts}
+\end{subfigure}
+\caption{Comparison between RFNU, RFNTL and RFNTS on synthetic dataset with 8 types, $\alpha=0.9$.}
+\label{fig:overlap}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.6\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
+\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
+\label{fig:error-locality}
+\end{figure}
 
@@
 factors are enough to separate the files of this dataset in 3 
-blocks, and the subjects in 8 types.
+blocks, and the subjects in 8 types. \enlargethispage{5mm}
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.6\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
-\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
-\label{fig:error-locality}
-\end{figure}
-
 \section*{Acknowledgement}
@@
 
-\newpage
-
-\onecolumn
-
-\begin{figure}
-\begin{minipage}{0.45\textwidth}
-\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Factors/ALS-8-types-ranks.pdf}
-\caption{Effect of the number of factors used in ALS, (RFNU, synthetic dataset, 8 types, 5 iterations).}
-\label{fig:factors}
-\end{minipage}\hfill
-\begin{minipage}{0.45\textwidth}
-\includegraphics[width=\columnwidth]{data/results/means_of_results/ALS/Synthetic/8type-RFNU-Differ-Num-Iterations-rank50/ALS-8-types-iteration.pdf}
-\caption{Effect of the number of iterations used in ALS, (RFNU, synthetic dataset, 8 types, 50 factors).}
-\label{fig:iterations}
-\end{minipage}
-\end{figure}
-
-\begin{figure*}
-\begin{subfigure}{0.5\columnwidth}
-\includegraphics[width=\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-userFactors.pdf}
-\caption{Subject factors}
-\end{subfigure}
-\hfill
-\begin{subfigure}{0.5\columnwidth}
-\includegraphics[width=\columnwidth]{./data/results/latent-factors/5i-3f-ALS-r1-08-itemFactors.pdf}
-\caption{File factors}
-\end{subfigure}
-\caption{Subject and file factors produced by collaborative filtering (RFNU, synthetic dataset, 8 types, 3 factors, 5 iterations).}
-\label{fig:factors3d}
-\end{figure*}
-
-\begin{figure*}
-\begin{subfigure}[b]{0.3\columnwidth}
-        \includegraphics[width=\columnwidth]{figures/RFNU_Syn_8_ALS_09_test_data_matrix_run1.png}
-        \caption{RFNU: $U(0.8N_f, N_f)$}
-        \label{fig:overlap-rfnu}
-\end{subfigure}
-\hfill
-\begin{subfigure}[b]{0.3\columnwidth}
-        \includegraphics[width=\columnwidth]{figures/RFNT-L_Syn_8_ALS_09_test_data_matrix_run2.png}
-        \caption{RFNTL: $T(0.85N_f, 0.85N_f, N_f)$}
-        \label{fig:overlap-rfntl}
-\end{subfigure}
-\hfill
-\begin{subfigure}[b]{0.3\columnwidth}
-        \includegraphics[width=\columnwidth]{figures/RFNT-S_Syn_8_ALS_09_test_data_matrix_run1.png}
-        \caption{RFNTS: 0.3$T(0, N_f, N_f)$+0.7$N_f$}
-        \label{fig:overlap-rfnts}
-\end{subfigure}
-\caption{Comparison between RFNU, RFNTL and RFNTS on synthetic dataset with 8 types, $\alpha=0.9$.}
-\label{fig:overlap}
-\end{figure*}
-
 \end{document}
